### 2017-08-24 tex/paper/paper.tex
Started the paper.

% !TEX TS-program = pdflatex
% !TEX encoding = UTF-8 Unicode

%\documentclass[12pt,a4paper]{memoir} % for a long document
\documentclass[12pt,a4paper,article]{memoir} % for a short document

\usepackage[utf8]{inputenc} % set input encoding to utf8

%%% PAGE DIMENSIONS
% Set up the paper to be as close as possible to both A4 & letter:
\settrimmedsize{11in}{210mm}{*} % letter = 11in tall; a4 = 210mm wide
\setlength{\trimtop}{0pt}
\setlength{\trimedge}{\stockwidth}
\addtolength{\trimedge}{-\paperwidth}
\settypeblocksize{*}{\lxvchars}{1.618} % we want to the text block to have golden proportionals
\setulmargins{50pt}{*}{*} % 50pt upper margins
\setlrmargins{*}{*}{1.618} % golden ratio again for left/right margins
\setheaderspaces{*}{*}{1.618}
\checkandfixthelayout 
\usepackage{enumitem}
\setitemize{noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt}
\usepackage{xcolor,listings}
\usepackage{textcomp}
\lstset{upquote=true}
\usepackage{graphicx}

%%% \maketitle CUSTOMISATION
% For more than trivial changes, you may as well do it yourself in a titlepage environment
\pretitle{\begin{center}\sffamily\huge\MakeUppercase}
\posttitle{\par\end{center}\vskip 0.5em}

%%% ToC (table of contents) APPEARANCE
\maxtocdepth{subsection} % include subsections
\renewcommand{\cftchapterpagefont}{}
\renewcommand{\cftchapterfont}{}     % no bold!

%%% HEADERS & FOOTERS
\pagestyle{ruled} % try also: empty , plain , headings , ruled , Ruled , companion

%%% CHAPTERS
\chapterstyle{hangnum} % try also: default , section , hangnum , companion , article, demo

\renewcommand{\chaptitlefont}{\Huge\sffamily\raggedright} % set sans serif chapter title font
\renewcommand{\chapnumfont}{\Huge\sffamily\raggedright} % set sans serif chapter number font

%%% SECTIONS
\hangsecnum % hang the section numbers into the margin to match \chapterstyle{hangnum}
\maxsecnumdepth{subsection} % number subsections

\setsecheadstyle{\Large\sffamily\raggedright} % set sans serif section font
\setsubsecheadstyle{\large\sffamily\raggedright} % set sans serif subsection font

\newlength\drop
\makeatletter
\newcommand*\titleM{\begingroup%
\setlength\drop{0.08\textheight}
\centering
\vspace*{\drop}
{\Huge\bfseries Technical Interview}\\[\baselineskip]
%{\scshape MAN-AHL}\\[\baselineskip]
\vfill
\includegraphics[width=0.5\textwidth]{img/logo.png}\par\vspace{1cm}
\vfill
{\large\scshape Fadil Mokhchane}\par
\vfill
{\scshape \@date}\par
\vspace*{2\drop}
\endgroup}
\makeatother
%% END Memoir customization

\title{Technical Interview}
\author{Fadil Mokhchane}
%\date{ August 2017} % Delete this line to display the current date
%%% BEGIN DOCUMENT
\begin{document}

\begin{titlingpage}
\titleM
\end{titlingpage}

\newpage
\tableofcontents* % the asterisk means that the contents itself isn't put into the ToC
%\clearpage %or \cleardoublepage
\phantomsection
%\listoffigures
%\listoftables
\newpage

\chapter{Algorithm}
\section{Question}
Implement the method nextNum() and a minimal but effective set of unit tests. 
Implement in the language of your choice, Python is preferred, but Java and 
other languages are completely fine. 
Make sure your code is exemplary, as if it was going to be shipped as part of a production system.

As a quick check, given Random Numbers are $[-1, 0, 1, 2, 3]$ and 
Probabilities are $[0.01, 0.3, 0.58, 0.1, 0.01]$ if we call nextNum() 100 times 
we may get the following results. As the results are random, these particular results are unlikely.
\begin{itemize}
	\item -1: 1 times 
	\item 0: 22 times
	\item 1: 57 times 
	\item 2: 20 times
	\item 3: 0 times 
\end{itemize}

\chapter{SQL}
\section{Question}
Given the following tables
\begin{lstlisting}[
           language=SQL,
           showspaces=false,
           basicstyle=\ttfamily,
           numbers=left,
           numberstyle=\tiny,
           commentstyle=\color{gray}
        ]
CREATE TABLE Product
(
product_id number primary key,
name varchar2(128 byte) not null,
rrp number not null,
available_from date not null
);
CREATE TABLE Orders
(
order_id number primary key,
product_id number not null,
quantity number not null,
order_price number not null,
dispatch_date date not null,
foreign key (product_id) references Product(product_id)
);
\end{lstlisting}
Write an sql query to find books that have sold fewer than 10 copies in the last year, 
excluding books that have been available for less than 1 month.

Some example data, intended to give an idea of the sort of data that might exist, 
can be found below. Note that the data is not complete, 
nor does it necessarily cover all the cases that might be encountered.

\begin{center}
    \begin{tabular}{| l | l | l | l |}
    \hline
	product\_id & name & rrp & available\_from \\
	\hline 
	101 & Bayesian Methods for ...& 94.95 & (last thursday) \\
	102 & (next year) in Review (preorder) & 21.95 & (next year) \\
	103 & Learn Python in Ten Minutes & 2.15 & (three months ago) \\
	104 & sports almanac (1999-2049) & 3.38 & (2 years ago) \\
	105 & finance for dummies & 84.99 & (1 year ago)  \\
	\hline
    \end{tabular}
\end{center}
\begin{center}
    \begin{tabular}{| l | l | l | l | l |}
    \hline
	order\_id & product\_id & quantity & order\_price & dispatch\_date \\
	\hline 
	1000 & 101 & 1 & 90.00 & (two months ago) \\
	1001 & 103 & 1 & 1.15 & (40 days ago) \\
	1002 & 101 & 10 & 90.00 & (11 months ago) \\
	1003 & 104 & 11 & 3.38 & (6 months ago) \\
	1004 & 105 & 11 & 501.33 & (two years ago) \\
	\hline
    \end{tabular}
\end{center}

%\newpage
%\appendix
%\addcontentsline{toc}{chapter}{Appendices}
%\chapter{Installing the App}

\end{document}

### 2017-08-25 tex/paper/paper.tex
paper: version 0.1 - added the first answers to the questions

@@
 \usepackage{graphicx}
+\usepackage{hyperref}
+\hypersetup{
+  colorlinks=true,
+  linkcolor=blue,
+  urlcolor=blue
+}
 
@@
 \vfill
-\includegraphics[width=0.5\textwidth]{img/logo.png}\par\vspace{1cm}
+\includegraphics[width=0.6\textwidth]{img/logo.png}\par\vspace{1cm}
 \vfill
-{\large\scshape Fadil Mokhchane}\par
+{\Huge\scshape Fadil Mokhchane \\ 
+\small \href{https://www.linkedin.com/in/fadil/}{LinkedIn} }\par
+\vspace{1cm}
+\includegraphics[width=0.2\textwidth]{img/harrington.jpg}\par
 \vfill
@@
 \vspace*{2\drop}
+{\scshape \small Version 0.1}\par
 \endgroup}
@@
 \phantomsection
-%\listoffigures
+\listoffigures
 %\listoftables
@@
 
+%-------------------------------------------------------------------------------
 \chapter{Algorithm}
@@
 
+\section{The Problem}
+We interpret the question as the following the mathematical problem. 
+We define a $X$ as a discrete random variable. 
+As input, we have a $k$ values, $x_i$, with their associated probabilities, $P_i$.
+
+A discrete probability density function is a probability distribution charaterised 
+by a probability mass function :
+\[
+	\forall i \in \left[1 ...  k\right], P\left[ X = x_i \right] = P_i  
+\]
+With
+\[ 
+	\sum_{i = 1}^k  P\left[ X = x_i \right]  = 1
+\]
+This probability mass function can be illustrated \autoref{fig:distribution} :
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.5\textwidth]{img/distribution.png}
+\caption{Probability Mass Function}
+\label{fig:distribution}
+\end{center}
+\end{figure}
+
+We would like to build a generator that picks $x_i$ given their probabilities
+$P_i$. 
+In order to make sure we generate $x_i$ with repesct to their original probabilities, 
+we need to add a no $x_i$ selected if the sum of the $x_i$ is less than $1$.
+
+This way we can build a discrete cumulative function for $X$, $F_x$, such as :
+\begin{equation}
+	F_x = P\left( X \leq x \right)
+	\label{eq:cdf}
+\end{equation}
+Which can be illustrated with \autoref{fig:cdf2} :
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.5\textwidth]{img/cdf.png}
+\caption{Discrete Cumulative Distribution Function}
+\label{fig:cdf2}
+\end{center}
+\end{figure}
+
+We then use a normal distribution to generate a number between $0$ and $1$.
+\[
+	f_x = \frac{1}{\sqrt{2 \pi}} e^{\frac{x^2}{2}}
+\]
+Using our discrete cumulative function, in \autoref{eq:cdf}, we can pick an $x_i$.
+The probability density of the normal distribution with mean $0$ and variance $1$ is:
+
+\section{Solution Proposed}
+\subsection{Overview}
+
+The key requirement is to deliver a production quality software.
+This means that the code has to be well designed, efficient, portable and well tested.
+
+The key features we would like to implement are:
+\begin{itemize}
+	\item Implement the generator,
+	\item Create an User Interface, via Command Line Input,
+	\item Compare various pseudo random number generator,
+	\item Target $100\%$ testing coverage.
+	\item Document the work.
+\end{itemize}
+
+\subsection{Design}
+Hence we target the following archictecture, c.f. \autoref{fig:architecture1}.
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.8\textwidth]{img/architecture1.png}
+\caption{Algorithm App Architecture}
+\label{fig:architecture1}
+\end{center}
+\end{figure}
+The various modules implement all the functionalities we need.
+\begin{description}
+	\item[Analytics] The mathematical functions required,
+	\item[Engine] 	The various random numbers generator,
+	\item[CLI] 		The command line input module,
+	\item[Testing] 	The testing module. 
+\end{description}
+
+\subsection{Testing}
+We need to test each module independtly, i.e. unit testing, and when they 
+are all used together, i.e. integration testing.
+
+Due to our limited testing environment, c.f. \autoref{apx:testing.env},
+we limit ourselves to the following tests.
+
+\emph{TBC}
+
+\subsection{UI}
+The UI is command line input allowing the user to run each feature.
+
+%-------------------------------------------------------------------------------
+\newpage
 \chapter{SQL}
@@
 
-%\newpage
-%\appendix
-%\addcontentsline{toc}{chapter}{Appendices}
-%\chapter{Installing the App}
+\section{Solution Proposed}
+We can solve the problem by running a query like:
+\begin{lstlisting}[
+           language=SQL,
+           showspaces=false,
+           basicstyle=\ttfamily,
+           numbers=left,
+           numberstyle=\tiny,
+           commentstyle=\color{gray}
+        ]
+SELECT p.name
+FROM  (
+   SELECT product_id, name FROM product 
+      WHERE available_from >=  (today - 1 month)
+) p
+INNER JOIN (
+   SELECT product_id, SUM(quantity) nb FROM orders
+      GROUP BY product_id
+      WHERE dispatch_date <= (today - 1 year)
+) o
+   ON p.product_id = o.product_id
+WHERE 
+   o.nb < 10
+\end{lstlisting}
+
+The key issue here in order to produce a production-like quality is 
+to test the query proposed.
+
+\subsection{Overview}
+We will extend our App by adding a database layer to create and query 
+the tables.
+We extend also our testing layer to create datasets in order to test
+the accuracy and efficiency of our query.
+
+\subsection{Design}
+Hence we target the following archictecture, c.f. \autoref{fig:architecture2}.
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.8\textwidth]{img/architecture2.png}
+\caption{SQL App Architecture}
+\label{fig:architecture2}
+\end{center}
+\end{figure}
+
+\subsection{Testing}
+We unfortunately lack the production tools to analyse the query execution.
+Without the access to the query plan of execution, we can only on our
+experience and empirical tests to create the best query possible.
+
+Therefore we have simple datasets to test the limiting cases and 
+large datasets to test the performance of our query.
+
+We have access to a limited hardware, c.f. \autoref{apx:testing.env}, 
+therefore the performance are slow.
+
+\subsection{UI}
+We extend the CLI to include the following command :
+\begin{description}
+	\item[TBC] ...
+\end{description}
+
+%-------------------------------------------------------------------------------
+\newpage
+\chapter{Discussion}
+\section{Implementation}
+In order to understand and share the creation process, 
+we share the Git log in \autoref{apx:git.log}. 
+Having a git log allows also rolling back changes, if needed.
+
+We tried to follow a Test Driven Development process as 
+demonstrated by the Git log.
+
+\section{Testing}
+The testing environment is described in \autoref{apx:testing.env}.
+
+\section{Extension}
+Here is a list of possible extension we could add.
+\begin{description}
+	\item [Testing]
+	Add some qualitative testing, by displaying the distribution generated 
+	by the random number generators.
+
+	Run the tests on different environments to ensure the portability of 
+	the code.
+	\item [UI] 
+	A nice extension would be to add a Graphic User Interface,
+	using the library 
+	\href{https://hackage.haskell.org/package/threepenny-gui}{threepenny-gui}
+	to create a portable Web application.
+
+	Also we could integrate a plot library to display the distribution of 
+	random numbers.
+	\item[Database]
+	We could add features to store and retrieve the results.
+	\item[Continuous Integration]
+	The fact that we tested only Mac OS, c.f. \autoref{apx:testing.env} is 
+	not production like.
+	We would like to run on various environment, a simple extension would 
+	be to run on Travis and AppVeyor website accessible via GitHub.
+\end{description}
+
+%-------------------------------------------------------------------------------
+\newpage
+\appendix
+\addcontentsline{toc}{chapter}{Appendices}
+\chapter{Installation} \label{apx:installation}
+
+Here are the steps to install the App.
+\begin{enumerate}
+	\item Download Haskell via this \href{https://www.haskell.org/platform/}{link}.
+	\item Install following the instructions given by the installer.
+	\item Use cabal to download the require packages :
+\begin{lstlisting}[
+           language=SQL,
+           showspaces=false,
+           basicstyle=\ttfamily,
+           numbers=left,
+           numberstyle=\tiny,
+           commentstyle=\color{gray}
+        ]
+	cabal install TBC
+\end{lstlisting}
+\end{enumerate}
+
+%-------------------------------------------------------------------------------
+\newpage
+\chapter{Testing Environment} \label{apx:testing.env}
+
+Given that I don't have access to my server this week, 
+we run the test on a MacBook Pro 2008 4GB DDR3 Intel Core Duo 2.53GHz.
+It has 250GB harddisk, not SSD.
+
+We are using Haskell version 8.2.1 on MacOS.
+
+%-------------------------------------------------------------------------------
+\newpage
+\chapter{Haskell Libraries} \label{apx:haskell.libraries}
+
+%-------------------------------------------------------------------------------
+\newpage
+\chapter{Git Log} \label{apx:git.log}
+We provide below the git log, as we are simulating a production environment.
+
+%-------------------------------------------------------------------------------
+\newpage
+\chapter{Code} \label{apx:code}
+We provide below the code.
 

### 2017-08-25 src/ManAhl/Core/Analytics.hs
First draft of the API without the Analytics

@@ -1,0 +1,5 @@
+module ManAhl.Core.Anaytics(
+
+) where
+
+

### 2017-08-25 src/ManAhl/Core/Engine.hs

@@ -1,0 +1,20 @@
+module ManAhl.Core.Engine(
+  -- * Creation
+  mkEngine,
+  -- * Generation
+  nextNum,
+  nextNums
+) where
+
+import ManAhl.Core.Types
+import ManAhl.Core.Random
+
+mkEngine :: [(Int, Double)] -> Maybe UniformRNGType -> IO Engine
+mkEngine xs typ = return . Engine xs =<< mkUniformRNG typ
+
+nextNum :: Engine -> (Double, Engine)
+nextNum = undefined
+
+nextNums :: Engine -> Int -> ([Double], Engine)
+nextNums = undefined
+

### 2017-08-25 src/ManAhl/Core/Random.hs

@@ -1,0 +1,20 @@
+module ManAhl.Core.Random(
+  -- * Creation
+  mkUniformRNG,
+  -- * Generation
+  next
+) where
+
+import ManAhl.Core.Types
+
+import System.Random hiding (next)
+import System.Random.Mersenne.Pure64
+
+mkUniformRNG :: Maybe UniformRNGType -> IO UniformRNG
+mkUniformRNG (Just Ecuyer)   = return . RandomEcuyer =<< newStdGen
+mkUniformRNG (Just Mersenne) = return . RandomMersenne =<< newPureMT
+mkUniformRNG Nothing         = mkUniformRNG $ Just Mersenne
+
+next :: UniformRNG -> (Double, UniformRNG)
+next (RandomEcuyer rng)   = let (x, r) = randomR (0, 1) rng in (x, RandomEcuyer r)
+next (RandomMersenne rng) = let (x, r) = randomR (0, 1) rng in (x, RandomMersenne r)

### 2017-08-25 src/ManAhl/Core/Types.hs

@@ -1,0 +1,19 @@
+module ManAhl.Core.Types(
+  Engine(..),
+  UniformRNGType(..),
+  UniformRNG(..)
+) where
+
+import qualified System.Random as Ecuyer
+import qualified System.Random.Mersenne.Pure64 as Mersenne
+
+data UniformRNG
+  = RandomEcuyer Ecuyer.StdGen
+  | RandomMersenne Mersenne.PureMT
+
+data UniformRNGType = Ecuyer | Mersenne
+
+data Engine = Engine{
+    pillars    :: [(Int, Double)]
+   ,uniformRng :: UniformRNG
+  }

### 2017-08-25 src/ManAhl/Run.hs

@@ -1,0 +1,14 @@
+module ManAhl.Run (
+  main
+) where
+
+import ManAhl.Core.Engine
+
+main :: IO()
+main = do
+  let datum = [(1 , 0.2), (3, 0.5), (7, 0.3)]
+  engine <- mkEngine datum Nothing
+  print $ fst $ nextNum engine
+  print $ fst $ nextNums engine 10
+
+

### 2017-08-25 src/Main.hs
Add the cabal files

@@ -1,4 +1,4 @@
-module ManAhl.Run (
+module Main (
   main
 ) where
 

### 2017-09-01 src/ManAhl/CLI.hs
Add count to Result in CLI

@@ -36,15 +36,16 @@ instance NFData Query where
   rnf (RunWeightedWith p n u) = rnf p `seq` rnf n
   rnf (RunUniformWith n u) = rnf n
 
--- The run type using either the weighted probability or
+-- | The run type using either the weighted probability or
 -- uniform probability engine
 data RunType = Weighted | Uniform
   deriving (Show, Read)
 
--- Encapsulated the Result of a run
+-- | Encapsulated the Result of a run
+-- its statistics and probabilities
 data Result =
-   ResultWeighted [(Maybe Int, Double)]
-  |ResultUniform  [(Double, Double)]
+   ResultWeighted (Stats (Maybe Int)) [(Maybe Int, Double)]
+  |ResultUniform  (Stats Double) [(Double, Double)]
   deriving Show
 
 -- | Parse the input argument into a query.
@@ -77,7 +78,7 @@ run (RunUniformWith nSims rngT) = do
   res <- runStatUni (Just rngT) $ allUStats nSims
   let stats = probaFromCount res
   return $
-    Right $ ResultUniform $ toList stats
+    Right $ ResultUniform res $ toList stats
 run (RunWeightedWith pdfPillars nSims rngT) = do
   let p = mkEngineParams pdfPillars $ Just rngT
   case p of
@@ -85,7 +86,7 @@ run (RunWeightedWith pdfPillars nSims rngT) = do
     Right e -> do
       res' <- runStatEngine e $ allStats nSims
       let res = probaFromCount res'
-      return $ Right $ ResultWeighted $ toList res
+      return $ Right $ ResultWeighted res' $ toList res
 
 -- | Give the CLI help
 help :: [(String, String)]

### 2017-09-01 src/Test/ManAhl/CLI.hs

@@ -39,14 +39,14 @@ testRun = do
       q2 = RunUniformWith 1000000 Mersenne
 
   r1' <- run q1
-  let r1 = either (const False) ( \ (ResultWeighted r) ->
+  let r1 = either (const False) ( \ (ResultWeighted _ r) ->
           foldl (\ acc (_, x) ->
             if not acc then False
               else round (x * 100) == 50) True r
           ) r1'
 
   r2' <- run q2
-  let r2 = either (const False) (\ (ResultUniform r) ->
+  let r2 = either (const False) (\ (ResultUniform _ r) ->
           foldl (\ acc (_, x) ->
             if not acc then False
               else round (x * 100) ==

### 2017-09-01 src/ManAhl/Core/Engine.hs
Fix totalCount

@@ -90,6 +90,6 @@ allStats 0 = error "You need at least one element"
 allStats n = allStats' (n-1) nextStat
   where
     allStats' :: Int -> StatWPEngine -> StatWPEngine
-    allStats' 1 acc = acc
+    allStats' 0 acc = acc
     allStats' !n acc = allStats' (n - 1) $ acc >> nextStat
 

### 2017-09-01 src/ManAhl/Core/Random.hs

@@ -83,7 +83,7 @@ allUStats 0 = error "You need at least one element"
 allUStats n = allStats' (n-1) nextUStat
   where
     allStats' :: Int -> StatUniEngine -> StatUniEngine
-    allStats' 1 acc = acc
+    allStats' 0 acc = acc
     allStats' !n acc = allStats' (n - 1) $ acc >> nextUStat
 
 -- | Range used to compute the statistics

### 2017-09-01 src/ManAhl/CLI.hs
Add Show instance to Result CLI

@@ -46,7 +46,25 @@ data RunType = Weighted | Uniform
 data Result =
    ResultWeighted (Stats (Maybe Int)) [(Maybe Int, Double)]
   |ResultUniform  (Stats Double) [(Double, Double)]
-  deriving Show
+
+showList' :: (Show a, Show b) => [(a, b)] -> [String]
+showList' = map (\(x, p) -> show x ++ ";" ++ show p )
+
+instance Show Result where
+  show (ResultWeighted (Stats count n) proba) = unlines $ [
+      "Result Weighted Random Number Engine, " ++ show n ++ " random numbers."
+     ,"Probabilities:"
+     ]
+     ++ showList' proba
+     ++ ["", "Distribution:"]
+     ++ showList' (toList count)
+  show (ResultUniform (Stats count n) proba) = unlines $ [
+      "Result Uniform Random Number Engine, " ++ show n ++ " random numbers."
+     ,"Probabilities:"
+     ]
+     ++ showList' proba
+     ++ ["", "Distribution:"]
+     ++ showList' (toList count)
 
 -- | Parse the input argument into a query.
 parse :: [String] -> Maybe Query

### 2017-09-01 src/Test/ManAhl/CLI.hs

@@ -11,7 +11,7 @@ import Control.Monad
 -- | Testsuite
 tests :: [(String, IO Bool)]
 tests = [
-    ("CLI Query creation", testQuery)
+    ("CLI Query", testQuery)
    ,("CLI Run",            testRun)
   ]
 

### 2017-09-01 src/Test/ManAhl/Core/Analytics.hs

@@ -67,10 +67,14 @@ propCdfFromPdfComplete pdf = fst (last pillarsCdf) == 1
 -- | Ensure that the PDF and CDF have the correct number of pillars
 propCdfPdfPillars :: PDF -> Bool
 propCdfPdfPillars pdf =
-    nCdfPillars == nPdfPillars || nCdfPillars == nPdfPillars + 1
+    (length cdfPillars == length pdfPillars ||
+    length cdfPillars == length pdfPillars + 1)
+    &&
+      (all (`elem` cdfPillars) pdfPillars &&
+     all (`elem` pdfPillars) cdfPillars)
   where
-    nCdfPillars = Map.size $ unCDF $ mkCdf pdf
-    nPdfPillars = Map.size $ unPDF pdf
+    cdfPillars = catMaybes $ Map.elems $ unCDF $ mkCdf pdf
+    pdfPillars = Map.keys $ unPDF pdf
 
 -- | Ensure that the pdf construction is stable
 propPdfStable :: PdfPillars -> Bool

### 2017-09-01 tex/paper/paper.tex
paper: updated all until the Automated testing

@@
 \vspace{1cm}
-\includegraphics[width=0.2\textwidth]{img/harrington.jpg}\par
+\includegraphics[width=0.3\textwidth]{img/harrington.jpg}\par
 \vfill
-{\scshape \@date}\par
 \vspace*{2\drop}
-{\scshape \small Version 0.1}\par
+{\scshape September 1, 2017}\par
+{\scshape \small Version 1.0}\par
 \endgroup}
@@
 We define a $X$ as a discrete random variable. 
-As input, we have a $k$ values, $x_i$, with their associated probabilities, $P_i$.
+As input, we have a $k$ values, $x_i$, with their associated probabilities, $p_i$.
 
 A discrete probability density function is a probability distribution charaterised 
-by a probability mass function :
-\[
-	\forall i \in \left[1 ...  k\right], P\left[ X = x_i \right] = P_i  
-\]
+by a probability mass function, c.f. \autoref{eq:pdf}, referenced as PDF.
+\begin{equation}
+	\forall i \in \left[1 ...  k\right], P\left[ X = x_i \right] = p_i  
+	\label{eq:pdf}
+\end{equation}
 With
@@
 \]
-This probability mass function can be illustrated \autoref{fig:distribution} :
+The values $\left(x_i, p_i\right)$ are called the PDF pillars.
+This probability mass function can be illustrated by \autoref{fig:distribution} :
 \begin{figure}[h!]
@@
 
-This way we can build a discrete cumulative function for $X$, $F_x$, such as :
+This way we can build a discrete cumulative function, referenced as CDF,
+ for $X$, $F_x$, such as :
 \begin{equation}
@@
 
-We then use a normal distribution to generate a number between $0$ and $1$.
-\[
-	f_x = \frac{1}{\sqrt{2 \pi}} e^{\frac{x^2}{2}}
-\]
-Using our discrete cumulative function, in \autoref{eq:cdf}, we can pick an $x_i$.
-The probability density of the normal distribution with mean $0$ and variance $1$ is:
+We then use a bounded uniform distribution, $U\left(0,1\right)$,
+to generate random numbers between $0$ and $1$.
+We picked two pseudo random numbers generator : Mersenne Twister\footnote{
+The Mersenne twister is a pseudorandom number generator developed by 
+Makoto Matsumoto and Takuji Nishimura that is based on a matrix linear 
+recurrence over a finite binary field. It provides for fast generation of 
+very high quality pseudorandom numbers. 
+It has a period of $2^63-1$.
+The source for the C code can be found 
+\href{http://www.math.sci.hiroshima-u.ac.jp/~m-mat/MT/emt64.html}{here}.
+} and Ecuyer\footnote{
+This is the default random number generator in haskell one in haskell.
+ This implementation uses the Portable Combined Generator of L'Ecuyer
+ for 32-bit computers, transliterated by Lennart Augustsson. 
+ It has a period of roughly $2.30584e18$.
+ This implementation claims to be faster than Ecuyer's one.
+ } in order to compare and pick the best one.
+
+Finally using the inverse of the discrete cumulative function, reference as Inverse CDF, 
+we can pick an $x_i$, described in \autoref{eq:invcdf}.
+\begin{equation}
+	\forall y \in \left[0...1 \right], F^{-1}_y = x_i
+	\label{eq:invcdf}
+\end{equation}
+This process gives us a weighted probability pseudo random number generator.
 
@@
 The key requirement is to deliver a production quality software.
-This means that the code has to be well designed, efficient, portable and well tested.
+This means that the code has to be well designed, simple, 
+efficient, portable and well tested.
 
-The key features we would like to implement are:
+The key features we would like to achieve :
 \begin{itemize}
-	\item Implement the generator,
+	\item Implement the weighted probability engine based
+	on a uniform random probability generator,
 	\item Create an User Interface, via Command Line Input,
+	\item Assess the quality of our weighted probability engine,
 	\item Compare various pseudo random number generator,
@@
 \subsection{Design}
-Hence we target the following archictecture, c.f. \autoref{fig:architecture1}.
+We target the following archictecture, c.f. \autoref{fig:architecture1}.
 \begin{figure}[h!]
@@
 	\item[Analytics] The mathematical functions required,
-	\item[Engine] 	The various random numbers generator,
-	\item[CLI] 		The command line input module,
-	\item[Testing] 	The testing module. 
+
+	In this module we have the implementation of the discrete 
+	probability function\footnote{
+	We can take as input incomplete probabilities, i.e. that
+	don't sum up to $1$. We therefore assign the remaining
+	probability to the event we don't select any element.
+	Haskell provides the \emph{Maybe a} type to modelise this.
+	}, the discrete cumulative function, 
+	the inverse discrete cumulative function and the mean and
+	standard deviation functions.
+
+	\item[Random]	The uniform pseudo random numbers generator,
+
+	This module contains an abstraction to a uniform pseudo
+	random number generator with values within $ \left[ 0, 1 \right]$.
+	It can compute a random number or a series of random 
+	number and the statistics related to the distribution of 
+	the random number generated.
+	\item[Engine] 	The weighted probability engine,
+
+	This module includes an abstraction to the weighted 
+	pseudo random numbers generators.
+	It allows computation and statistics on these numbers.
+	It inluce the requested nextNum function.
+	\item[CLI] 		The command line input layer,
+
+	As it is meaningless to look only at one random number at the time.
+	The CLI provides a flexible API to compute $n$ random numbers.
+	We can select any random number we have implemented.
+	We display only the distribution of these random numbers.
+	\item[Testing] 	The testing module,
+
+	This module provides all the automated tests. They are unit 
+	tests at the module level and integration tests at the key
+	features level.
 \end{description}
 
-\subsection{Testing}
+\subsection{UI}
+The UI is a command line input allowing the user to run each feature.
+After building the project, with the following command:
+\begin{verbatim}
+cabal build
+\end{verbatim}
+The binary is located in \emph{./dist/build/MAN-AHL/MAN-AHL}.
+We can run weighted engine or the unform generator
+ as described in \autoref{fig:cli}, with the following command:
+\begin{verbatim}
+time ./dist/build/MAN-AHL/MAN-AHL -run=Weighted -nSims=1000000
+\end{verbatim}
+ The binary has the option \emph{-help}, stating all the default values.
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=1\textwidth]{img/cli.png}
+\caption{Command Line Input}
+\label{fig:cli}
+\end{center}
+\end{figure}
+
+\section{Implementation}
+
+\section{Automated Unit and Integration Testing}
 We need to test each module independtly, i.e. unit testing, and when they 
@@
 
-Due to our limited testing environment, c.f. \autoref{apx:testing.env},
-we limit ourselves to the following tests.
+The testing environment used is described in below\footnote{
+Given that I don't have access to my server, 
+we run the tests on a MacBook Pro 2008 4GB DDR3 Intel Core Duo 2.53GHz.
+It has 250GB harddisk, not SSD. 
+We are using Haskell version 8.2.1 on MacOS. Vim version 8.0.
+}.
 
-\emph{TBC}
+We use heavily a random testing library, i.e. QuickCheck\footnote{
+QuickCheck is a library for random testing of program properties.
+The API is described 
+\href{http://hackage.haskell.org/package/QuickCheck-2.10.0.1/docs/Test-QuickCheck.html}{here}.
+}, to test comprehensively the software.
+Automated pseudo random tests allowed to discover issues and
+test cases that were not included at first.
 
-\subsection{UI}
-The UI is command line input allowing the user to run each feature.
+Our test data is mostly pseudo random: 
+PDF pillars, PDF, CDF and Inverse CDF inputs.
+
+We can run the automated as described in  \autoref{fig:tests} with the command:
+\begin{verbatim}
+time cabal test --show-details=streaming
+\end{verbatim}
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=1\textwidth]{img/tests.png}
+\caption{Automated Testing}
+\label{fig:tests}
+\end{center}
+\end{figure}
+
+The following Test Suites, i.e. lists of tests, compose our test plan split by modules.
+
+\subsection{Test Data}
+
+The key sample used throughout the testing is the generation of PDF pillars.
+We tried to pick a realistic sample.
+
+The pillars can have 1 to 10 pillars. Their summed probability are always less 
+than or equal to 1.  Each probability is within the $[0.01, 1]$ bound.
+
+\subsection{Analytics Testing} 
+These are the unit tests for the Analytics only.
+\begin{description}
+	\item [CDF creation]
+		Given a 1000 pseudo random PDF, we ensure 
+		that the last pillar of the CDF is 1.
+		As the CDF is build incrementally, this gives a good sense that
+		the CDF construction has been correct.
+	\item [CDF and PDF pillars check]
+		Given a 1000 pseudo random PDF, we ensure that
+		the pillars on the x axis of the PDF are the pillars on the y
+		axis of the CDF.
+	\item [PDF Stable]
+		Given a 1000 pseudo random PDF pillars, 
+		we ensure that we get the same PDF given the reverse input.
+	\item [PDF consistency]
+		Given a 1000 pseudo random PDF, 
+		we ensure that the sum of the PDF pillars probabilities are 
+		less than 1. We indeed modelise the non selected element
+		only in the CDF.
+	\item [Inverse CDF valid]
+		Given a 1000 pseudo random PDF,
+		we build the CDF and we ensure that for a random number of
+		x values within 0 and 1 we always recover a x pillars of the PDF.
+	\item [PDF Failure]
+		We test the expecture failure of the PDF construction. 
+		We can't have negative values. We need at least one valid pillar.
+		The pillars with 0 probabilities are discarded.
+		And the sum of the PDF pillars probabilities must be less or
+		equal to one.
+	\item [CDF Failure]
+		 The CDF construction always assume a correct PDF as
+		 input. If it is not the case, it fails if the aggregated 
+		 probabilities are greater than 1.
+		 The test ensure an exception is raised.
+	\item [Inverse CDF Failure]
+		We check that the inverse CDF function raise an
+		exception if the x input is outside the correct bounds, 
+		$\left[0, 1\right]$.
+	\item [Mean and Standard Deviation Failure]
+		These functions raise an exception for empty lists.
+		We test it automatically.
+	\item [PDF and CDF Non Regression]
+		We ensure without randomness that given a set of pillars,
+		we recover the expected CDF and PDF.
+\end{description}
+\subsection{Random Testing}
+
+These are the unit tests for the uniform pseudo random generator.
+
+\begin{description}
+	\item [Mean and Standard Deviation]
+		Given a large number of random number generated for
+		both Ecuyer and Mersenne, i.e. $100000$.
+		We ensure that the mean and the standard deviation 
+		of the distributions are still the same. Run 100 times.
+	\item [Bounds]
+		Test ensuring that the uniform pseudo random generators
+		generate probabilities with the $[0, 1]$ bound.
+		Run $100$ times for $100000$ random numbers.
+	\item [Uniform]
+		Ensure that the ditributions generated are uniform.
+		Run 10 times for $100000$ random numbers.
+	\item [Performance]
+		Ensure that the pseudo random numbers keep at
+		least the same performance.
+		Run 10 times for $100000$ random numbers.
+\end{description}
+
+\subsection{Engine Testing} 
+These are the unit tests for the weighted pseudo random engine.
+All tests are run using the two available uniform pseudo random
+generators. 
+These are like the integration tests as they use most of the library.
+\begin{description}
+	\item [Distribution check]
+		We check that we recover the PDF distribution from
+		a sample of 1000000 at $0.5\%$ precision.
+		We run this for 10 pseudo random PDF.
+	\item [Engine Fail]
+		Ensure that the construction of the engine 
+		handles all the expected failure.
+	\item [Performance]
+		Ensure that the engine keep at least the same performance.
+		Run 10 times for $100000$ random  numbers	
+\end{description}
+
+\subsection{CLI Testing}
+We test that the API produce what is expected.
+\begin{description}
+	\item [Query]
+	We test that given an argument list, we produce the expected
+	Query.
+	\item[Run]
+	We test that for given a Query, we produce the expected Result.
+\end{description}
+
+\section{Qualitative Testing}
+
+\section{Performance Testing}
+
+\section{Extension}
+Here is a list of possible extension we could add.
+\begin{description}
+	\item [Testing]
+	Add some qualitative testing, by displaying the distribution generated 
+	by the random number generators.
+
+	Run the tests on different environments to ensure the portability of 
+	the code.
+	\item [UI] 
+	A nice extension would be to add a Graphic User Interface,
+	using the library 
+	\href{https://hackage.haskell.org/package/threepenny-gui}{threepenny-gui}
+	to create a portable Web application.
+
+	Also we could integrate a plot library to display the distribution of 
+	random numbers.
+	\item[Database]
+	We could add features to store and retrieve the results.
+	\item[Continuous Integration]
+	The fact that we tested only Mac OS, c.f. \autoref{apx:testing.env} is 
+	not production like.
+	We would like to run on various environment, a simple extension would 
+	be to run on Travis and AppVeyor website accessible via GitHub.
+\end{description}
 
@@
 FROM  (
-   SELECT product_id, name FROM product 
-      WHERE available_from >=  (today - 1 month)
+   SELECT product_id, name FROM Product 
+      WHERE available_from <=  (today - 1 month)
 ) p
-INNER JOIN (
-   SELECT product_id, SUM(quantity) nb FROM orders
+LEFT OUTER JOIN (
+   SELECT product_id, SUM(quantity) nb FROM Orders
+      WHERE dispatch_date >= (today - 1 year)
       GROUP BY product_id
-      WHERE dispatch_date <= (today - 1 year)
+      HAVING nb < 10
 ) o
    ON p.product_id = o.product_id
-WHERE 
-   o.nb < 10
 \end{lstlisting}
 
-The key issue here in order to produce a production-like quality is 
-to test the query proposed.
-
-\subsection{Overview}
-We will extend our App by adding a database layer to create and query 
-the tables.
-We extend also our testing layer to create datasets in order to test
-the accuracy and efficiency of our query.
-
-\subsection{Design}
-Hence we target the following archictecture, c.f. \autoref{fig:architecture2}.
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[width=0.8\textwidth]{img/architecture2.png}
-\caption{SQL App Architecture}
-\label{fig:architecture2}
-\end{center}
-\end{figure}
-
-\subsection{Testing}
-We unfortunately lack the production tools to analyse the query execution.
-Without the access to the query plan of execution, we can only on our
-experience and empirical tests to create the best query possible.
-
-Therefore we have simple datasets to test the limiting cases and 
-large datasets to test the performance of our query.
-
-We have access to a limited hardware, c.f. \autoref{apx:testing.env}, 
-therefore the performance are slow.
-
-\subsection{UI}
-We extend the CLI to include the following command :
-\begin{description}
-	\item[TBC] ...
-\end{description}
-
-%-------------------------------------------------------------------------------
-\newpage
-\chapter{Discussion}
-\section{Implementation}
-In order to understand and share the creation process, 
-we share the Git log in \autoref{apx:git.log}. 
-Having a git log allows also rolling back changes, if needed.
-
-We tried to follow a Test Driven Development process as 
-demonstrated by the Git log.
-
-\section{Testing}
-The testing environment is described in \autoref{apx:testing.env}.
-
-\section{Extension}
-Here is a list of possible extension we could add.
-\begin{description}
-	\item [Testing]
-	Add some qualitative testing, by displaying the distribution generated 
-	by the random number generators.
-
-	Run the tests on different environments to ensure the portability of 
-	the code.
-	\item [UI] 
-	A nice extension would be to add a Graphic User Interface,
-	using the library 
-	\href{https://hackage.haskell.org/package/threepenny-gui}{threepenny-gui}
-	to create a portable Web application.
-
-	Also we could integrate a plot library to display the distribution of 
-	random numbers.
-	\item[Database]
-	We could add features to store and retrieve the results.
-	\item[Continuous Integration]
-	The fact that we tested only Mac OS, c.f. \autoref{apx:testing.env} is 
-	not production like.
-	We would like to run on various environment, a simple extension would 
-	be to run on Travis and AppVeyor website accessible via GitHub.
-\end{description}
+Adding indexes to the columns on which we join and maybe query would improve 
+the performance. 
+A query plan of the execution would indicate what is the best design for this 
+database scheme.
 
@@
 \addcontentsline{toc}{chapter}{Appendices}
+
+\chapter{Code} \label{apx:code}
+We provide below the code.
+
+%-------------------------------------------------------------------------------
+\newpage
 \chapter{Installation} \label{apx:installation}
@@
 \end{enumerate}
-
-%-------------------------------------------------------------------------------
-\newpage
-\chapter{Testing Environment} \label{apx:testing.env}
-
-Given that I don't have access to my server this week, 
-we run the test on a MacBook Pro 2008 4GB DDR3 Intel Core Duo 2.53GHz.
-It has 250GB harddisk, not SSD.
-
-We are using Haskell version 8.2.1 on MacOS.
-
-%-------------------------------------------------------------------------------
-\newpage
-\chapter{Haskell Libraries} \label{apx:haskell.libraries}
-
-%-------------------------------------------------------------------------------
-\newpage
-\chapter{Git Log} \label{apx:git.log}
-We provide below the git log, as we are simulating a production environment.
-
-%-------------------------------------------------------------------------------
-\newpage
-\chapter{Code} \label{apx:code}
-We provide below the code.
-
 \end{document}

### 2017-09-01 src/ManAhl/CLI.hs
Improve CLI design

@@ -47,24 +47,20 @@ data Result =
    ResultWeighted (Stats (Maybe Int)) [(Maybe Int, Double)]
   |ResultUniform  (Stats Double) [(Double, Double)]
 
-showList' :: (Show a, Show b) => [(a, b)] -> [String]
-showList' = map (\(x, p) -> show x ++ ";" ++ show p )
+showRes :: Show a => String -> Stats a -> [(a, Double)] -> String
+showRes name (Stats count n) proba = unlines $ [
+      "Result " ++ name ++ " Random Number Engine, " ++ show n ++ " random numbers."
+     ,"Probabilities:"
+     ] ++ showList' proba
+     ++ ["", "Distribution:"]
+     ++ showList' (toList count)
+  where
+    showList' :: (Show a, Show b) => [(a, b)] -> [String]
+    showList' = map (\(x, p) -> show x ++ ";" ++ show p )
 
 instance Show Result where
-  show (ResultWeighted (Stats count n) proba) = unlines $ [
-      "Result Weighted Random Number Engine, " ++ show n ++ " random numbers."
-     ,"Probabilities:"
-     ]
-     ++ showList' proba
-     ++ ["", "Distribution:"]
-     ++ showList' (toList count)
-  show (ResultUniform (Stats count n) proba) = unlines $ [
-      "Result Uniform Random Number Engine, " ++ show n ++ " random numbers."
-     ,"Probabilities:"
-     ]
-     ++ showList' proba
-     ++ ["", "Distribution:"]
-     ++ showList' (toList count)
+  show (ResultWeighted stats proba) = showRes "Weighted" stats proba
+  show (ResultUniform stats proba) = showRes "Uniform" stats proba
 
 -- | Parse the input argument into a query.
 parse :: [String] -> Maybe Query
@@ -109,9 +105,9 @@ run (RunWeightedWith pdfPillars nSims rngT) = do
 -- | Give the CLI help
 help :: [(String, String)]
 help = [
-    ("-help","")
+    ("-help","Produce this help.")
    ,("-pillars=[(1,0.2),(2, 0.3),(3, 0.1),(4, 0.15)]", "PDF Pillars")
-   ,("-nSims=1000000", "Nb of sims")
+   ,("-nSims=1000000", "Number of random number generated")
    ,("-rng=Mersenne", "RNG type: Mersenne or Ecuyer")
    ,("-run=Weighted", "Run type: Weighted or Uniform")
   ]

### 2017-09-03 src/ManAhl/CLI.hs
Refactor the testing

@@ -3,7 +3,7 @@ module ManAhl.CLI(
   parse,
   run,
   help,
-  Query(..),
+  Query(..), Result(..),
   pillarsDefault
 ) where
 

### 2017-09-03 src/ManAhl/Core/Types.hs

@@ -21,6 +21,7 @@ module ManAhl.Core.Types(
   Curve(..)
 ) where
 
+import Control.DeepSeq
 import Control.Monad
 import Control.Monad.State.Strict
 import Control.Monad.Reader
@@ -57,7 +58,7 @@ newtype InvCDF = InvCDF { unICDF :: PieceWiseCurve Double (Maybe Int) }
   deriving (Show, Eq, Curve Double (Maybe Int))
 -- | Distribution
 newtype Distribution a = Distribution { unDist :: PieceWiseCurve a Int }
-  deriving (Show, Eq, Curve a Int)
+  deriving (Show, Eq, Curve a Int, NFData)
 
 class Curve b c a | a -> b, a -> c where
   emptyCurve :: a
@@ -83,35 +84,12 @@ class Curve b c a | a -> b, a -> c where
   -- | O(n) appy a function to each pillar
   cMap :: (c -> c) -> a -> a
 
-instance Curve a b (PieceWiseCurve a b) where
-  emptyCurve = PieceWiseCurve Map.empty
-  nPillars = Map.size . toRaw
-  fromPillars = fromRaw . Map.fromList
-  toPillars = Map.toList . toRaw
-  fromRaw = PieceWiseCurve
-  toRaw = unPWC
-  PieceWiseCurve m !!! x =
-    case x `Map.lookupGE` m of
-      Just r -> r
-      Nothing -> error $ "Fails: " ++ show x
-  addWith f x y c = PieceWiseCurve $ Map.insertWith f x y $ toRaw c
-  add x y c = PieceWiseCurve $ Map.insert x y $ toRaw c
-  cFoldl f x m = Map.foldl f x $ toRaw m
-  cMap = fmap
-
 -- | Class to operate a Distribution
 class Distri a where
   -- | O(log n) add an element
   increaseCount :: a -> Distribution a -> Distribution a
   -- | Range used to compute the statistics
   defaultDist :: Distribution a
-
-instance Distri (Maybe Int) where
-  increaseCount x = addWith (+) x 1
-  defaultDist = emptyCurve
-instance Distri Double where
-  increaseCount x = addWith (+) (fst $ defaultDist !!! x) 1
-  defaultDist = fromPillars $ zip (Prelude.map (/100) [1, 2 .. 100]) [0..]
 
 -- | Weighted Probability Engine Params
 -- contains the PDF, CDF, inverseCDF
[…]

### 2017-09-03 src/Test/ManAhl/CLI.hs

@@ -37,14 +37,14 @@ testRun = TestIO $ do
       q2 = RunUniformWith 1000000 Mersenne
 
   r1' <- run q1
-  let r1 = either (const False) ( \ (WPStats _ _ (Just r)) ->
+  let r1 = either (const False) ( \ (ResultWeighted (Stats _ _ (Just r))) ->
           foldl (\ acc (_, x) ->
             if not acc then False
               else round (x * 100) == 50) True r
           ) r1'
 
   r2' <- run q2
-  let r2 = either (const False) (\ (UniStats _  _ (Just r)) ->
+  let r2 = either (const False) (\ (ResultUniform (Stats _  _ (Just r))) ->
           foldl (\ acc (_, x) ->
             if not acc then False
               else round (x * 100) ==

### 2017-09-03 src/Test/ManAhl/Core/Analytics.hs

@@ -1,3 +1,4 @@
+{-# LANGUAGE ScopedTypeVariables #-}
 -- | Module containing the Analytics unit tests
 module Test.ManAhl.Core.Analytics(
   tests
@@ -40,60 +41,63 @@ genInvCdfQuery = do
 -- Testsuite
 tests :: TestSuite
 tests = [
-    ("CDF Creation",                    propCdfFromPdfComplete)
+    ("InvCDF Creation",                 propInvCdfFromPdfComplete)
    ,("CDF and PDF pillars check",       propCdfPdfPillars)
    ,("PDF stable with reverse Pillars", propPdfStable)
    ,("PDF consistency",                 propPdfConsistency)
    ,("InvCDF valid",                    propInvCdfValid)
    ,("PDF Failure",                     testPdfFail)
-   ,("CDF Failure",                     testCdfFail)
    ,("Inverse CDF Failure",             testInvCdfFail)
    ,("Mean Failure",                    testMeanFail)
    ,("Std Failure",                     testStdFail)
    ,("PDF No regression",               testPDFNoRegression)
-   ,("CDF No regression",               testCDFNoRegression)
+   ,("InvCDF No regression",            testInvCDFNoRegression)
   ]
 
 -- | Ensure that the last pillars of the CDF is 100%
-propCdfFromPdfComplete :: Test
-propCdfFromPdfComplete =
+propInvCdfFromPdfComplete :: Test
+propInvCdfFromPdfComplete =
   TestQC $ run $ \pdf ->
-    let cdf = mkCdf pdf
-        pillarsCdf = Map.toList $ unCDF cdf
+    let iCdf = mkInvCdf $ mkCdf pdf
+        pillarsCdf = toPillars iCdf
      in fst (last pillarsCdf) == 1
 
 -- | Ensure that the PDF and CDF have the correct number of pillars
 propCdfPdfPillars :: Test
 propCdfPdfPillars =
   TestQC $ run $ \pdf ->
-    let cdfPillars = catMaybes $ Map.elems $ unCDF $ mkCdf pdf
-        pdfPillars = Map.keys $ unPDF pdf
-     in (length cdfPillars == length pdfPillars ||
-        length cdfPillars == length pdfPillars + 1)
[…]

### 2017-09-03 src/Test/ManAhl/Core/UniformEngine.hs

@@ -49,7 +49,6 @@ propBounds rngT =
   TestQCRng rngT $ \ rng ->
     Test.runWith 10 $ \ (x :: Int) ->
       foldl (\ acc x -> if not acc then False else  x >= 0 && x <= 1) True $
-        hsDistriUni $
           computeProba Nothing rng (nextNums nRand :: ProbaUniEngine [Double])
 
 -- | Test the distribution of the uniform engine is uniform
@@ -57,12 +56,13 @@ propUniform :: UniformRNGType -> Test
 propUniform rT =
   TestQCRng rT $ \ rng ->
     Test.runWith 10 $ \ (x :: Int) ->
-      let stats = computeStats Nothing rng (allStats nRand :: StatUniEngine Stats)
-       in Map.foldl (\ acc x ->
+      let stats = computeStats Nothing rng (allStats nRand :: StatUniEngine UniStats)
+          (Just proba) = hsProba stats
+       in foldl (\ acc (_, x) ->
           if not acc then False
               else round (x * 100) ==
-                round (100 / fromIntegral (Map.size $ hsDistri stats))) True $
-                  fromJust $ hsProbaUni stats
+                round (100 / fromIntegral (nPillars $ hsDistri stats))) True proba
+
 
 -- | Ensure that the performance of the uniform engine
 -- remain acceptable
@@ -72,7 +72,7 @@ propPerf rT =
     Test.runWith 10 $ monadicIO $
   do
     t <- QC.run $ time $
-            computeStats Nothing rng (allStats 1000000 :: StatUniEngine Stats)
+            computeStats Nothing rng (allStats 1000000 :: StatUniEngine UniStats)
 
     let res = t < 0.4
     unless res $ do

### 2017-09-03 src/Test/ManAhl/Core/WeightedEngine.hs

@@ -8,8 +8,8 @@ import Test.QuickCheck.Monadic as QC
 import Test.ManAhl.QuickCheck as Test
 
 import ManAhl.Core.Types
-import ManAhl.Core.Engine
-import ManAhl.Core.Random
+import ManAhl.Core.WeightedEngine
+import ManAhl.Core.UniformEngine
 import ManAhl.Core.Analytics
 
 import Control.Monad
@@ -36,11 +36,11 @@ propWeightedProba rT =
     Test.runWith 10 $ forAll genPdfPillars $ \ pdfP ->
       let e = case mkEngineParams pdfP of
             Left s -> error s; Right x -> x
-          stats = runStatEngine e rng $ allStats 1000000
-          pdf' = unPDF $ pdf e
-          proba = probaFromCount stats
-       in Map.foldl (\ acc v -> if not acc then False else v <= 0.005 ) True $
-            Map.mapWithKey (\ v p -> abs (proba ! Just v - p)) pdf'
+          stats = computeStats (Just e) rng
+                    (allStats 1000000 :: StatWPEngine WeightedStats)
+          pdf' = pdf e
+          (Just proba) = hsProba stats
+       in pdf' == fromPillars proba
 
 -- | Test that EngineParams fails to build for all
 -- expected cases
@@ -48,10 +48,10 @@ testEngineFail :: Test
 testEngineFail = TestPure $ const $
       negativePro && nullPro && greaterPro && nullPro2
   where
-      negativePro = isLeft $ mkEngineParams [(1, -1)]
-      nullPro = isLeft $ mkEngineParams []
-      nullPro2 = isLeft $ mkEngineParams [(1,0)]
-      greaterPro = isLeft $ mkEngineParams [(1, 0.4), (2, 0.5), (3, 0.4)]
+      negativePro = isLeft $ mkEngineParams $ PdfPillars [(1, -1)]
+      nullPro = isLeft $ mkEngineParams $ PdfPillars []
+      nullPro2 = isLeft $ mkEngineParams $ PdfPillars [(1,0)]
+      greaterPro = isLeft $ mkEngineParams $ PdfPillars [(1, 0.4), (2, 0.5), (3, 0.4)]
 
 -- | Test that the performance of the Engine remain acceptable
 propPerf :: UniformRNGType -> Test
@@ -62,8 +62,7 @@ propPerf rT =
       let e'= mkEngineParams pdfP
           e = case e' of Left s -> error s; Right x -> x
       t <- QC.run $ time $
[…]

### 2017-09-03 src/Test/ManAhl/Run.hs

@@ -9,10 +9,9 @@ import System.Exit (exitFailure)
 import Text.Printf
 import Test.QuickCheck
 
-import ManAhl.Core.Random
 import Test.ManAhl.QuickCheck (runTest)
 import qualified Test.ManAhl.Core.Analytics as Analytics
-import qualified Test.ManAhl.Core.UniformEngine as Uniform
+import qualified Test.ManAhl.Core.UniformEngine as UniformEngine
 import qualified Test.ManAhl.Core.WeightedEngine as WeightedEngine
 import qualified Test.ManAhl.CLI as CLI
 

### 2017-09-03 src/ManAhl/Core/Types.hs
Fix failing tests

@@ -162,7 +162,7 @@ instance Functor (PieceWiseCurve a) where
 
 instance {-# OVERLAPS #-} Eq (PieceWiseCurve (Maybe Int) Double) where
   PieceWiseCurve lhs == PieceWiseCurve rhs =
-    Map.foldl (\acc x -> if not acc then False else x < 0.0001) True $
+    Map.foldl (\acc x -> if not acc then False else x < 0.001) True $
       Map.unionWith (-) lhs rhs
 
 instance {-# OVERLAPS #-} Eq (PieceWiseCurve Double (Maybe Int)) where

### 2017-09-03 src/Test/ManAhl/CLI.hs

@@ -12,8 +12,8 @@ import Control.Monad
 -- | Testsuite
 tests :: TestSuite
 tests = [
-    ("CLI Query", testQuery)
-   ,("CLI Run",   testRun)
+    ("CLI - Query", testQuery)
+   ,("CLI - Run",   testRun)
   ]
 
 -- | Test the creation of a query from the arguments

### 2017-09-03 src/Test/ManAhl/Core/Analytics.hs

@@ -30,6 +30,10 @@ instance Arbitrary PDF where
 instance Arbitrary CDF where
   arbitrary = mkCdf `liftM` arbitrary
 
+-- Instance to create correct PDFs
+instance Arbitrary InvCDF where
+  arbitrary = mkInvCdf `liftM` arbitrary
+
 -- Generatoring input for the inverseCDF testing
 genInvCdfQuery :: Gen (PDF, [Double])
 genInvCdfQuery = do
@@ -40,7 +44,8 @@ genInvCdfQuery = do
 
 -- Testsuite
 tests :: TestSuite
-tests = [
+tests = map (\(x, y) -> ("Analytics - " ++ x, y))
+  [
     ("InvCDF Creation",                 propInvCdfFromPdfComplete)
    ,("CDF and PDF pillars check",       propCdfPdfPillars)
    ,("PDF stable with reverse Pillars", propPdfStable)
@@ -59,8 +64,8 @@ propInvCdfFromPdfComplete :: Test
 propInvCdfFromPdfComplete =
   TestQC $ run $ \pdf ->
     let iCdf = mkInvCdf $ mkCdf pdf
-        pillarsCdf = toPillars iCdf
-     in fst (last pillarsCdf) == 1
+        lastP = fst $ last $ toPillars iCdf
+     in abs ( lastP - 1) <= 0.0001
 
 -- | Ensure that the PDF and CDF have the correct number of pillars
 propCdfPdfPillars :: Test
@@ -87,7 +92,8 @@ propPdfStable =
 propPdfConsistency :: Test
 propPdfConsistency =
   TestQC $ run $ \ (pdf :: PDF) ->
-    cFoldl (\acc x -> x + acc) 0 pdf <= 1
+    let s = cFoldl (\acc x -> x + acc) 0 pdf
+     in abs (s - 1) <= 0.0001
 
 -- | Ensure that the inverseCdf recovers the correct pdf pillars
 propInvCdfValid :: Test

### 2017-09-03 src/Test/ManAhl/Core/UniformEngine.hs

@@ -19,15 +19,16 @@ import ManAhl.Core.Analytics
 
 -- | List of tests
 tests :: TestSuite
-tests = [
+tests = map (\(x, y) -> ("Uniform Engine - " ++ x, y))
+  [
     ("Ecuyer Mean and Std",   propMeanStd Ecuyer)
    ,("Mersenne Mean And Std", propMeanStd Mersenne)
    ,("Ecuyer Bounds",         propBounds Ecuyer)
    ,("Mersenne Bounds",       propBounds Mersenne)
    ,("Mersenne Uniform",      propUniform Mersenne)
    ,("Ecuyer Uniform",        propUniform Ecuyer)
-   ,("Uniform Mersenee Perf", propPerf Mersenne)
-   ,("Uniform Ecuyer Perf",   propPerf Ecuyer)
+   ,("Mersenee Perf",         propPerf Mersenne)
+   ,("Ecuyer Perf",           propPerf Ecuyer)
   ]
 
 -- | Test that the standard deviation and mean of the uniform
@@ -63,7 +64,6 @@ propUniform rT =
               else round (x * 100) ==
                 round (100 / fromIntegral (nPillars $ hsDistri stats))) True proba
 
-
 -- | Ensure that the performance of the uniform engine
 -- remain acceptable
 propPerf :: UniformRNGType -> Test
@@ -72,9 +72,9 @@ propPerf rT =
     Test.runWith 10 $ monadicIO $
   do
     t <- QC.run $ time $
-            computeStats Nothing rng (allStats 1000000 :: StatUniEngine UniStats)
+            computeStats Nothing rng (allStats 100000 :: StatUniEngine UniStats)
 
-    let res = t < 0.4
+    let res = t < 0.45
     unless res $ do
       QC.run $ printf "Time %s: %0.9f sec" (show rT) t
     assert res

### 2017-09-03 src/Test/ManAhl/Core/WeightedEngine.hs

@@ -20,12 +20,13 @@ import Text.Printf (printf)
 
 -- | List of tests related to the engine
 tests :: TestSuite
-tests = [
-    ("Engine distri check - Mersene", propWeightedProba Mersenne)
-   ,("Engine distri check - Ecuyer",  propWeightedProba Ecuyer)
-   ,("Engine fail",                   testEngineFail)
-   ,("Engine Perf - Mersene",         propPerf Mersenne)
-   ,("Engine Perf - Ecuyer",          propPerf Ecuyer)
+tests = map (\(x, y) -> ("Weighted Engine - " ++ x, y))
+  [
+    ("distri check - Mersene", propWeightedProba Mersenne)
+   ,("distri check - Ecuyer",  propWeightedProba Ecuyer)
+   ,("fail",                   testEngineFail)
+   ,("Perf - Mersene",         propPerf Mersenne)
+   ,("Perf - Ecuyer",          propPerf Ecuyer)
   ]
 
 -- | Test that we recover the input probabilities
@@ -51,7 +52,8 @@ testEngineFail = TestPure $ const $
       negativePro = isLeft $ mkEngineParams $ PdfPillars [(1, -1)]
       nullPro = isLeft $ mkEngineParams $ PdfPillars []
       nullPro2 = isLeft $ mkEngineParams $ PdfPillars [(1,0)]
-      greaterPro = isLeft $ mkEngineParams $ PdfPillars [(1, 0.4), (2, 0.5), (3, 0.4)]
+      greaterPro = isLeft $ mkEngineParams $
+                      PdfPillars [(1, 0.4), (2, 0.5), (3, 0.4)]
 
 -- | Test that the performance of the Engine remain acceptable
 propPerf :: UniformRNGType -> Test

### 2017-09-03 src/Test/ManAhl/Run.hs

@@ -24,7 +24,7 @@ main = do
       UniformEngine.tests ++
       WeightedEngine.tests
    ) $ \ (name, test) -> do
-           printf "%-35s:" name
+           printf "%-45s:" name
            runTest test
 
   unless (all (==True) success)

### 2017-09-03 src/ManAhl/CLI.hs
Fix engine params

@@ -59,8 +59,10 @@ showRes name stats proba n = unlines $
     showList' = map (\(x, p) -> show x ++ ";" ++ show p )
 
 instance Show Result where
-  show (ResultWeighted (Stats stats n (Just proba))) = showRes "Weighted" stats proba n
-  show (ResultUniform (Stats stats n (Just proba))) = showRes "Weighted" stats proba n
+  show (ResultWeighted (Stats stats n (Just proba))) =
+    showRes "Weighted" stats proba n
+  show (ResultUniform (Stats stats n (Just proba))) =
+    showRes "Uniform" stats proba n
   show _ = "Error"
 
 -- | Parse the input argument into a query.
@@ -93,14 +95,15 @@ run :: Query -> IO (Either String Result)
 run (RunUniformWith nSims rngT) = do
   rng <- mkUniformRNG rngT
   return $ Right $ ResultUniform $
-    computeStats Nothing rng (allStats nSims :: StatUniEngine UniStats)
+    computeStats UniformEngineParams rng
+      (allStats nSims :: StatUniEngine UniStats)
 run (RunWeightedWith pdfPillars nSims rngT) = do
   rng <- mkUniformRNG rngT
   let p = mkEngineParams pdfPillars
   return $ case p of
     Left s -> Left s
     Right e -> Right $ ResultWeighted $
-      computeStats (Just e) rng (allStats nSims :: StatWPEngine WeightedStats)
+      computeStats e rng (allStats nSims :: StatWPEngine WeightedStats)
 
 -- | Give the CLI help
 help :: [(String, String)]

### 2017-09-03 src/ManAhl/Core/Types.hs

@@ -43,8 +43,7 @@ data UniformRNGType = Ecuyer | Mersenne
 -- | PDF Pillars
 newtype PdfPillars = PdfPillars [(Int, Double)]
   deriving (Show, Eq)
--- | Discrete PieceWise Curve
--- modelised using a TreeMap
+-- | Discrete PieceWise Curve modelised using a TreeMap
 newtype PieceWiseCurve a b = PieceWiseCurve { unPWC :: Map a b }
   deriving Show
 -- | Discrete Probabily Density Function,
@@ -60,6 +59,7 @@ newtype InvCDF = InvCDF { unICDF :: PieceWiseCurve Double (Maybe Int) }
 newtype Distribution a = Distribution { unDist :: PieceWiseCurve a Int }
   deriving (Show, Eq, Curve a Int, NFData)
 
+-- | Operations on a Curve.
 class Curve b c a | a -> b, a -> c where
   emptyCurve :: a
   -- | O(1) Nb of Pillars
@@ -94,11 +94,12 @@ class Distri a where
 -- | Weighted Probability Engine Params
 -- contains the PDF, CDF, inverseCDF
 -- needed to compute the weighted probabilities
-data EngineParams = EngineParams {
+data EngineParams =
+  WeightedEngineParams {
     pdf     :: PDF
    ,cdf     :: CDF
    ,iCdf    :: !InvCDF
-  }
+  } | UniformEngineParams
 
 -- | Statistic of a given Run [a]
 --  hsDistri : represent the distribution of the  elements
@@ -115,19 +116,20 @@ type WeightedStats = Stats (Maybe Int)
 -- | Class to compute probabilities given an engine.
 class Monad a => ProbaEngine a b | a -> b where
   -- | Compute the probabilities
-  computeProba :: Maybe EngineParams -> UniformRNG -> a c -> c
+  computeProba :: EngineParams -> UniformRNG -> a c -> c
   -- | Prepare the next random number
   nextNum :: a b
   -- | Prepare the n next random numbers
   nextNums :: Int -> a [b]
   nextNums n = replicateM n nextNum
 
+-- | Class to compute the statistics given an egine
 class Monad a => StatEngine a b | a -> b where
-
-  computeStats :: Maybe EngineParams -> UniformRNG -> a (Stats b) -> (Stats b)
-
+  -- | Compute the statistics
+  computeStats :: EngineParams -> UniformRNG -> a (Stats b) -> (Stats b)
[…]

### 2017-09-03 src/ManAhl/Core/UniformEngine.hs

@@ -25,8 +25,10 @@ instance RandomGen UniformRNG where
   next (RandomMersenne rng) = let (x, r) = next rng in (x, RandomMersenne r)
   genRange (RandomEcuyer rng)   = genRange rng
   genRange (RandomMersenne rng) = genRange rng
-  split (RandomEcuyer rng)   = let (g1, g2) = split rng in (RandomEcuyer g1, RandomEcuyer g1)
-  split (RandomMersenne rng) = let (g1, g2) = split rng in (RandomMersenne g1, RandomMersenne g2)
+  split (RandomEcuyer rng)   = let (g1, g2) = split rng in
+                                   (RandomEcuyer g1, RandomEcuyer g1)
+  split (RandomMersenne rng) = let (g1, g2) = split rng in
+                                   (RandomMersenne g1, RandomMersenne g2)
 
 -- Create Uniform RNG encapsulating Mersenne or Ecuyer
 mkUniformRNG :: UniformRNGType -> IO UniformRNG

### 2017-09-03 src/ManAhl/Core/WeightedEngine.hs

@@ -25,19 +25,19 @@ mkEngineParams pdfP =
   either
       (\ msg -> Left msg)
       (\ p -> let cdf' = mkCdf p in
-        Right EngineParams {
+        Right WeightedEngineParams {
             pdf = p
            ,cdf = cdf'
            ,iCdf = mkInvCdf cdf'
          }) $ mkPdf pdfP
 
 instance ProbaEngine ProbaWPEngine (Maybe Int) where
-  computeProba (Just p) uniRng e =
+  computeProba p uniRng e =
     flip evalState uniRng $
       runReaderT (unPWPE e) p
 
   nextNum = do
-    EngineParams _ _ iCdf <- ask
+    WeightedEngineParams _ _ iCdf <- ask
     uniRng <- get
     let (!x, !r) = runState (unPUIE nextNum) uniRng
     put r
@@ -45,14 +45,14 @@ instance ProbaEngine ProbaWPEngine (Maybe Int) where
     return y
 
 instance StatEngine StatWPEngine (Maybe Int) where
-  computeStats (Just p) uniRng e = let
+  computeStats p uniRng e = let
       s = flip evalState
         (Stats defaultDist 0 Nothing, uniRng) $
           runReaderT (unSWP e) p
        in s{ hsProba = Just $ probabilities $ hsDistri s }
 
   nextStat = do
-    EngineParams _ _ iCdf <- ask
+    WeightedEngineParams _ _ iCdf <- ask
     (Stats cs n _, uniRng) <- get
     let (!x, !r) = runState (unPUIE nextNum) uniRng
         !y = invCdf iCdf x

### 2017-09-03 src/Test/ManAhl/Core/UniformEngine.hs

@@ -37,7 +37,8 @@ propMeanStd :: UniformRNGType -> Test
 propMeanStd rngT =
   TestQCRng rngT $ \ rng ->
     Test.runWith 10 $ \ (x :: Int) ->
-      let vals = computeProba Nothing rng (nextNums nRand :: ProbaUniEngine [Double])
+      let vals = computeProba UniformEngineParams rng
+                    (nextNums nRand :: ProbaUniEngine [Double])
           m = mean vals
           std = stdDev vals
           x ~= y = abs (x - y) <= 0.04
@@ -50,14 +51,16 @@ propBounds rngT =
   TestQCRng rngT $ \ rng ->
     Test.runWith 10 $ \ (x :: Int) ->
       foldl (\ acc x -> if not acc then False else  x >= 0 && x <= 1) True $
-          computeProba Nothing rng (nextNums nRand :: ProbaUniEngine [Double])
+        computeProba UniformEngineParams rng
+          (nextNums nRand :: ProbaUniEngine [Double])
 
 -- | Test the distribution of the uniform engine is uniform
 propUniform :: UniformRNGType -> Test
 propUniform rT =
   TestQCRng rT $ \ rng ->
     Test.runWith 10 $ \ (x :: Int) ->
-      let stats = computeStats Nothing rng (allStats nRand :: StatUniEngine UniStats)
+      let stats = computeStats UniformEngineParams rng
+                    (allStats nRand :: StatUniEngine UniStats)
           (Just proba) = hsProba stats
        in foldl (\ acc (_, x) ->
           if not acc then False
@@ -72,7 +75,8 @@ propPerf rT =
     Test.runWith 10 $ monadicIO $
   do
     t <- QC.run $ time $
-            computeStats Nothing rng (allStats 100000 :: StatUniEngine UniStats)
+            computeStats UniformEngineParams rng
+              (allStats 100000 :: StatUniEngine UniStats)
 
     let res = t < 0.45
     unless res $ do

### 2017-09-03 src/Test/ManAhl/Core/WeightedEngine.hs

@@ -37,7 +37,7 @@ propWeightedProba rT =
     Test.runWith 10 $ forAll genPdfPillars $ \ pdfP ->
       let e = case mkEngineParams pdfP of
             Left s -> error s; Right x -> x
-          stats = computeStats (Just e) rng
+          stats = computeStats e rng
                     (allStats 1000000 :: StatWPEngine WeightedStats)
           pdf' = pdf e
           (Just proba) = hsProba stats
@@ -64,7 +64,8 @@ propPerf rT =
       let e'= mkEngineParams pdfP
           e = case e' of Left s -> error s; Right x -> x
       t <- QC.run $ time $
-              computeStats (Just e) rng (allStats 100000 :: StatWPEngine WeightedStats)
+              computeStats e rng
+                (allStats 100000 :: StatWPEngine WeightedStats)
       let res = t < 0.4
       unless res $
         QC.run $ printf "Time %s: %0.9f sec" (show rT) t

### 2017-09-03 src/ManAhl/CLI.hs
Fix tests

@@ -109,7 +109,7 @@ run (RunWeightedWith pdfPillars nSims rngT) = do
 help :: [(String, String)]
 help = [
     ("-help","Produce this help.")
-   ,("-pillars=[(1,0.2),(2, 0.3),(3, 0.1),(4, 0.15)]", "PDF Pillars")
+   ,("-pillars='[(1,0.2),(2, 0.3),(3, 0.1),(4, 0.15)]'", "Input the PDF Pillars")
    ,("-nSims=1000000", "Number of random number generated")
    ,("-rng=Mersenne", "RNG type: Mersenne or Ecuyer")
    ,("-run=Weighted", "Run type: Weighted or Uniform")

### 2017-09-03 src/ManAhl/Core/Analytics.hs

@@ -26,8 +26,8 @@ mkPdf (PdfPillars xs)
   | null xs = Left "The pdf pillars are empty."
   | null $ filter (\(_, x) -> x /= 0) xs =
       Left "The pdf pillars contain only zero."
-  | foldl (\ acc (_, x) -> if acc then acc else x < 0) False xs =
-      Left "PDF Pillars contain negative values."
+  | foldl (\ acc (_, x) -> if acc then acc else x < 0 || x > 1) False xs =
+      Left "PDF Pillars contain negative values or greater than 1."
   | foldl (\ acc (_, x) -> acc + x) 0 xs > 1 =
       Left "The sum of PDF probabilities are greater than 1."
   | otherwise = Right $

### 2017-09-03 src/ManAhl/Run.hs

@@ -15,7 +15,7 @@ main :: IO()
 main = do
   args <- getArgs
   let printHelp =
-        mapM_ (\ (x, y) -> printf "%-45s: %s \n" x y) help
+        mapM_ (\ (x, y) -> printf "%-55s: %s \n" x y) help
 
   if "-help" `elem` args
      then printHelp

### 2017-09-03 tex/paper/paper.tex
Update the first sections

@@
 %-------------------------------------------------------------------------------
-\chapter{Algorithm}
+\chapter{Algorithm Exercise}
 \section{Question}
@@
 \section{The Problem}
+\label{sec:problem}
 We interpret the question as the following the mathematical problem. 
@@
 Makoto Matsumoto and Takuji Nishimura that is based on a matrix linear 
-recurrence over a finite binary field. It provides for fast generation of 
-very high quality pseudorandom numbers. 
-It has a period of $2^63-1$.
+recurrence over a finite binary field. 
+It has a period of $2^{63}-1$.
 The source for the C code can be found 
 \href{http://www.math.sci.hiroshima-u.ac.jp/~m-mat/MT/emt64.html}{here}.
-} and Ecuyer\footnote{
+} (This implementation claims to be faster than Ecuyer's one.) and Ecuyer\footnote{
 This is the default random number generator in haskell one in haskell.
  This implementation uses the Portable Combined Generator of L'Ecuyer
- for 32-bit computers, transliterated by Lennart Augustsson. 
+ for 32-bit computers, transliterated in Haskell by Lennart Augustsson. 
  It has a period of roughly $2.30584e18$.
- This implementation claims to be faster than Ecuyer's one.
  } in order to compare and pick the best one.
@@
 \end{equation}
-This process gives us a weighted probability pseudo random number generator.
+This process gives us a weighted probability pseudo random number engine.
 
@@
 \begin{itemize}
-	\item Implement the weighted probability engine based
-	on a uniform random probability generator,
+	\item Implement the weighted probability engine\footnote{
+		The task of an engine is to manage the creation of a serie of
+		pseudo random numbers.} based
+		on a bounded uniform random probability engine,
+	\item Target a $100\%$ testing coverage.
+	\item Assess the quality of our probability engines,
+	\item Assess the performances of our probability engines,
 	\item Create an User Interface, via Command Line Input,
-	\item Assess the quality of our weighted probability engine,
-	\item Compare various pseudo random number generator,
-	\item Target $100\%$ testing coverage.
 	\item Document the work.
@@
 
-	\item[Random]	The uniform pseudo random numbers generator,
+	\item[Uniform Engine] The bounded uniform 
+	pseudo random numbers engine,
 
 	This module contains an abstraction to a uniform pseudo
-	random number generator with values within $ \left[ 0, 1 \right]$.
+	random number generator with values bounded 
+	within $ \left[ 0, 1 \right]$.
 	It can compute a random number or a series of random 
@@
 	the random number generated.
-	\item[Engine] 	The weighted probability engine,
+	\item[Weighted Engine] 	The weighted pseudo random 
+	numbers probability engine,
 
@@
 	It allows computation and statistics on these numbers.
-	It inluce the requested nextNum function.
+	It includes the requested nextNum function.
 	\item[CLI] 		The command line input layer,
@@
 	As it is meaningless to look only at one random number at the time.
-	The CLI provides a flexible API to compute $n$ random numbers.
-	We can select any random number we have implemented.
+	The CLI provides a flexible API to compute
+	statistics on $n$ random numbers.
+	We can select any random number engine we have implemented.
 	We display only the distribution of these random numbers.
@@
 
-\subsection{UI}
+\subsection{User Interface}
 The UI is a command line input allowing the user to run each feature.
@@
 \end{verbatim}
-The binary is located in \emph{./dist/build/MAN-AHL/MAN-AHL}.
-We can run weighted engine or the unform generator
+The binary is then located in \emph{./dist/build/MAN-AHL/MAN-AHL}.
+We can run the weighted or the uniform engine
  as described in \autoref{fig:cli}, with the following command:
@@
 time ./dist/build/MAN-AHL/MAN-AHL -run=Weighted -nSims=1000000
+        -pillars=''
 \end{verbatim}
@@
 
+We use Haskell as implementation language. It is a purely functional language.
+It has a strong type system. It is all about types, they tell the story.
+In this section, we inztroduce the key types used thoughout the application.
+
+\subsection{Analytics Module}
+
+The analytics are mainly destined to weighted probability engine.
+
+We define the \emph{PieceWiseCurve x y} algebraic data type(ADT) to provide an
+abstraction to piecewise curve, as we are working with discrete
+random variable, it is the closest to reality. We picked the tree map data
+structure, \emph{Data.Map} in Haskell, to get efficient lookup ( O(log n) ).
+The \emph{Curve x y a} class\footnote{ad hoc polymorphism} 
+provides the key operations on a 
+\emph{PieceWiseCurve}.
+
+We subsequently define the ADTs to represent all the curves we need
+for our weighted probability engine :
+\begin{itemize}
+	\item The \emph{PDF} ADT modelising the probability mass function,
+	The key are the $x_i$ and the values the $p_i$, we presented in
+	\autoref{sec:problem}.
+	We merge the pillars with similar $x_i$, discard the pillars with zero
+	$p_i$ and ensure that $\sum_i p_i \leq 1$.
+	If needed we a a pillar representing non selected element 
+	as \emph{Nothing}. This way we ensure that the probabilities
+	adds up to 1.
+	\item The \emph{CDF} ADT represents the discrete cumulative
+	curve, presented in \autoref{fig:cdf2}.
+	\item The \emph{InvCDF} ADT represents the inverse CDF curve,
+	as explained in \autoref{eq:invcdf}
+	\item The \emph{Distribution a} ADT models a distribution curve
+	of the random number generated.
+\end{itemize}
+Again, we refer to curve as to piecewise curves or histograms.
+
+This module contains also the basic statistics we are using to 
+analyse the results.
+
+\subsection{Uniform Engine Module}
+
+The \emph{UniformRNG} ADT abstracts a choice of uniform pseudo random 
+number generator, Mersenne Twister and Ecuyer. We could seemlessly
+add new generator, if needs be. We would need to extend the standard
+Haskell \emph{RandomGen} class. 
+They can generate un-bounded pseudo random numbers.
+
+The \emph{ProbaUniEngine} ADT abstracts the computation of a uniform pseudo
+random number generation bounded between 0 and 1.
+It uses the \emph{State} monad to pass on the state of \emph{UniformRNG}
+when we combine multiple computations.
+This engine instanciates the \emph{ProbaEngine} class, which define
+and abstract the role of a probability engine. The latter is to 
+create one or a series of pseudo random numbers.
+
+The \emph{StatUniEngine} ADT abstracts the computation of the statistics
+related to the bounded uniform random numbers generated. 
+In order to be efficient, we compute only the distribution while we 
+are creating pseudo random numbers. 
+There is a post-processing step at the end of the simulation, which 
+computes the remaining relevant statistics.
+It uses the \emph{State} monad to pass on the state of the 
+uniform random number generator and the cumulative statistics.
+This engine instanciates the \emph{StatEngine} class, which role is
+to compute the statistics of a series of random numbers.
+
+\subsection{Weighted Engine Module}
+
+The \emph{ProbaWPEngine} ADT allows to computed weighted pseudo
+random numbers. It order to achieve this, it need to build and keep
+thoughout the computations the \emph{EngineParams} ADT. 
+This latter encapsulates the \emph{PDF}, \emph{CDF} and \emph{InvCDF}
+ADTs. They do not change thoughout the computations and they are kept 
+in memory for efficiency. We pass them thought the computations
+using the \emph{Reader} monad. We also use the \emph{State} monad
+to pass on the state of the bounded uniform engine.
+It also instanciates the \emph{ProbaEngine} class.
+
+The \emph{StatWPEngine} ADT compute the statistic for a weighted
+probabilities run. It also use a monad composed of a \emph{Reader}
+and \emph{State} monads. A post processing step computes
+the remaining metrics. It also instanciates the \emph{StatEngine} class.
+
+\subsection{CLI Module}
+Using the \emph{Query} ADT we modelise a query from the command line
+dynamically. This latter is processed by the \emph{run} function to 
+produce a  \emph{Result} ADT.
+
+In a way, we lose static typing here in order to merge all the types of 
+request and to dispatch the query to the appropriate engine. And we merge
+back the result into the \emph{Result} to provide a single function achieving
+everything we need.
+
+\subsection{Testing Module}
+
 \section{Automated Unit and Integration Testing}
-We need to test each module independtly, i.e. unit testing, and when they 
-are all used together, i.e. integration testing.
+We need to test each module independtly, i.e. unit testing, and all used 
+together, i.e. integration testing.
 
@@
 
-\subsection{Test Data}
+\subsection{Test Data Sample}
 
-The key sample used throughout the testing is the generation of PDF pillars.
-We tried to pick a realistic sample.
-
+The key test data sample used throughout the testing 
+is the generation of PDF pillars.
+We tried to pick a realistic sample :
 The pillars can have 1 to 10 pillars. Their summed probability are always less 
-than or equal to 1.  Each probability is within the $[0.01, 1]$ bound.
+than or equal to 1.  Each probability is within the $]0, 1]$ bound.
 
@@
 		the CDF construction has been correct.
-	\item [CDF and PDF pillars check]
+	\item [InverseCDF, CDF and PDF pillars check]
 		Given a 1000 pseudo random PDF, we ensure that
-		the pillars on the x axis of the PDF are the pillars on the y
-		axis of the CDF.
+		the pillars on the x axis of the PDF and CDF are the pillars on the y
+		axis of the Inverse CDF.
 	\item [PDF Stable]
@@
 		we ensure that the sum of the PDF pillars probabilities are 
-		less than 1. We indeed modelise the non selected element
+		equal to 1. We indeed modelise the non selected element
 		only in the CDF.
@@
 		x values within 0 and 1 we always recover a x pillars of the PDF.
-	\item [PDF Failure]
+	\item [PDF failure]
 		We test the expecture failure of the PDF construction. 
@@
 		The pillars with 0 probabilities are discarded.
-		And the sum of the PDF pillars probabilities must be less or
+		And the sum of the PDF pillars probabilities must be 
 		equal to one.
-	\item [CDF Failure]
-		 The CDF construction always assume a correct PDF as
-		 input. If it is not the case, it fails if the aggregated 
-		 probabilities are greater than 1.
-		 The test ensure an exception is raised.
 	\item [Inverse CDF Failure]
@@
 		We test it automatically.
-	\item [PDF and CDF Non Regression]
+	\item [PDF and Inverse CDF Non Regression]
 		We ensure without randomness that given a set of pillars,
-		we recover the expected CDF and PDF.
+		we recover the expected Inverse CDF and PDF.
 \end{description}
-\subsection{Random Testing}
+\subsection{Uniform Engine Testing}
 
-These are the unit tests for the uniform pseudo random generator.
+These are the unit tests for the bounded uniform pseudo random engine.
 
@@
 		We ensure that the mean and the standard deviation 
-		of the distributions are still the same. Run 100 times.
+		of the distributions are still the same. Run 10 times.
+		We ensure that the uniform random number engines keep
+		the same properties.
 	\item [Bounds]
@@
 		generate probabilities with the $[0, 1]$ bound.
-		Run $100$ times for $100000$ random numbers.
+		Run $10$ times for $100000$ random numbers.
 	\item [Uniform]
-		Ensure that the ditributions generated are uniform.
+		Ensure that the ditributions generated are uniform,
+		by making sure that we match a flat distribution at 0.001
+		precision.
 		Run 10 times for $100000$ random numbers.
@@
 
-\subsection{Engine Testing} 
+\subsection{Weighted Engine Testing} 
 These are the unit tests for the weighted pseudo random engine.
@@
 		We check that we recover the PDF distribution from
-		a sample of 1000000 at $0.5\%$ precision.
+		a sample of 1000000 random numbers at $0.1\%$ precision.
 		We run this for 10 pseudo random PDF.
@@
 
-\section{Extension}
+\section{Possible Extension}
 Here is a list of possible extension we could add.
 \begin{description}
+	\item [Analytics]
+	Further abstract the PDF, CDF, InvCDF to handle all kind of keys.
 	\item [Testing]
-	Add some qualitative testing, by displaying the distribution generated 
-	by the random number generators.
-
-	Run the tests on different environments to ensure the portability of 
+	We could run the tests on different environments to ensure the portability of 
 	the code.
@@
 	random numbers.
-	\item[Database]
-	We could add features to store and retrieve the results.
-	\item[Continuous Integration]
-	The fact that we tested only Mac OS, c.f. \autoref{apx:testing.env} is 
-	not production like.
-	We would like to run on various environment, a simple extension would 
-	be to run on Travis and AppVeyor website accessible via GitHub.
 \end{description}
@@
 \newpage
-\chapter{SQL}
+\chapter{SQL Exercise}
 \section{Question}

### 2017-09-03 src/ManAhl/Core/UniformEngine.hs
perf improvement

@@ -21,13 +21,13 @@ import System.Random.Mersenne.Pure64
 -- | Make UniformRNG instance of RandGen by delegating the
 -- work to the inner RNG
 instance RandomGen UniformRNG where
-  next (RandomEcuyer rng)   = let (x, r) = next rng in (x, RandomEcuyer r)
-  next (RandomMersenne rng) = let (x, r) = next rng in (x, RandomMersenne r)
+  next (RandomEcuyer rng)       = let (x, r) = next rng in (x, RandomEcuyer r)
+  next (RandomMersenne rng)     = let (x, r) = next rng in (x, RandomMersenne r)
   genRange (RandomEcuyer rng)   = genRange rng
   genRange (RandomMersenne rng) = genRange rng
-  split (RandomEcuyer rng)   = let (g1, g2) = split rng in
+  split (RandomEcuyer rng)      = let (g1, g2) = split rng in
                                    (RandomEcuyer g1, RandomEcuyer g1)
-  split (RandomMersenne rng) = let (g1, g2) = split rng in
+  split (RandomMersenne rng)    = let (g1, g2) = split rng in
                                    (RandomMersenne g1, RandomMersenne g2)
 
 -- Create Uniform RNG encapsulating Mersenne or Ecuyer

### 2017-09-03 tex/paper/paper.tex
Update the paper start the metrics

@@
 \usepackage{graphicx}
+\usepackage{subcaption}
 \usepackage{hyperref}
@@
 {\Huge\scshape Fadil Mokhchane \\ 
-\small \href{https://www.linkedin.com/in/fadil/}{LinkedIn} }\par
+\small \href{https://www.linkedin.com/in/fadil/}{CV on LinkedIn} }\par
 \vspace{1cm}
@@
 \vspace*{2\drop}
-{\scshape September 1, 2017}\par
+{\scshape September 3, 2017}\par
 {\scshape \small Version 1.0}\par
@@
 
+%-------------------------------------------------------------------------------
 \section{The Problem}
@@
 
+%-------------------------------------------------------------------------------
 \section{Solution Proposed}
@@
 
+%-------------------------------------------------------------------------------
 \section{Implementation}
@@
 It has a strong type system. It is all about types, they tell the story.
-In this section, we inztroduce the key types used thoughout the application.
+In this section, we introduce the key types used thoughout the application.
+
+\subsection{General Notes}
+We use efficient data structures as appropriate and we modelise the problem using
+the whole power of Haskell. 
+We use \emph{newtype} as much as possible as it allows design at a 
+seemless cost.
+
+Indeed, we use parametric and ad hoc polymorphism as needs be.
+We modelise the exception handling using different techniques, depending on
+the context, let it be \emph{Either a b}, \emph{Maybe a} or \emph{error}.
+
+The aim was to keep the software as simple as possible while targetting a
+good design and performance. 
+The right balance is always difficult to achieve as unfortunately no 
+software is ever perfect.
+
+The code is documented while we believe that a simple and well organised
+code needs less documentation. The complexities are presented in the key
+area of the code. The code is presented in \autoref{apx:code}.
+
+Any constructive feedback is most welcome.
 
@@
 \subsection{Testing Module}
+We modelise a \emph{TestSuite} as a list of \emph{Test}.
+Each \emph{Test} can be of different type: QuickCheck type - 
+using a pseudo random data, 
+an IO type - an action that need to be run, e.g. performance tests, 
+and a Pure kind of test, for pure computation action.
 
-\section{Automated Unit and Integration Testing}
+%-------------------------------------------------------------------------------
+\section{Unit and Integration Testing}
 We need to test each module independtly, i.e. unit testing, and all used 
@@
 than or equal to 1.  Each probability is within the $]0, 1]$ bound.
+
+We felt that the number of pillars was meant to be small. It is unlikely
+the software will be used with a million pillars.
 
@@
 
-\section{Qualitative Testing}
+%-------------------------------------------------------------------------------
+\section{Qualitative Analysis}
+We realise that we maybe be beyond the scope of the initial
+question, which was to implement a \emph{nextNum} function.
+However how to test it efficiently ? It is a very hard question.
 
-\section{Performance Testing}
+It is an important part of Software Engineering and 
+Quantitative Development to understand the 
+meaning of what we are trying to achieve. 
+It allows better modelisation, algoritms and testing. 
+In this section, we will look at the number generated and try
+to find the best parameters for this software.
 
-\section{Possible Extension}
+\subsection{Metrics}
+To assess the quality of a random number engine, we use
+simple statistics. It would have been nice to have time to 
+study further statistical and mathematical papers related 
+to the random numbers generation and probabilities.
+We could have created with more advanced metrics.
+
+There are two keys elements which drive the results :
+the input discrete probability function with $k$ pillars and
+the output discrete probability function deducted from a
+simulation of $n$ random numbers.
+
+Hence we look at different input PDF with various $k$,
+and the output PDF with various $n$. 
+This data gives us intuitions about what are the right
+parameters, $n$ and $k$ to use for our engines.
+
+We also have two random numbers generator, 
+Mersenne and Ecuyer, available. We compare them thoughout.
+
+As our weighted probability engine depends on
+the uniform probability engine. 
+We test first the uniform engine.
+
+The metrics we look at are:
+\begin{itemize}
+	\item the difference between the input and output pdf,
+	\item the standard deviation of these differences,
+	\item the mean of these difference, hopefully close to zero.
+\end{itemize}
+
+\subsection{Uniform Distribution}
+
+The input PDF for a uniform distribution is flat. The probabilities
+should be the same for each bucket.
+
+\begin{figure}[h!]
+    \centering
+    \begin{subfigure}[b]{0.45\textwidth}
+        \includegraphics[width=\textwidth]{img/uni-m-1.png}
+        \caption{A gull}
+        \label{fig:gull}
+    \end{subfigure}
+    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
+      %(or a blank line to force the subfigure onto a new line)
+    \begin{subfigure}[b]{0.45\textwidth}
+        \includegraphics[width=\textwidth]{img/uni-m-1.png}
+        \caption{A tiger}
+        \label{fig:tiger}
+    \end{subfigure}
+
+    \begin{subfigure}[b]{0.45\textwidth}
+        \includegraphics[width=\textwidth]{img/uni-m-1.png}
+        \caption{A gull}
+        \label{fig:gull}
+    \end{subfigure}
+    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
+      %(or a blank line to force the subfigure onto a new line)
+    \begin{subfigure}[b]{0.45\textwidth}
+        \includegraphics[width=\textwidth]{img/uni-m-1.png}
+        \caption{A tiger}
+        \label{fig:tiger}
+    \end{subfigure}
+
+    \begin{subfigure}[b]{0.45\textwidth}
+        \includegraphics[width=\textwidth]{img/uni-m-1.png}
+        \caption{A gull}
+        \label{fig:gull}
+    \end{subfigure}
+    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
+      %(or a blank line to force the subfigure onto a new line)
+    \begin{subfigure}[b]{0.45\textwidth}
+        \includegraphics[width=\textwidth]{img/uni-m-1.png}
+        \caption{A tiger}
+        \label{fig:tiger}
+    \end{subfigure}
+    \caption{Pictures of animals}\label{fig:animals}
+\end{figure}
+
+\subsection{Weighted Distribution}
+
+%-------------------------------------------------------------------------------
+\section{Performance Analysis}
+
+\subsection{Complexity Analysis}
+
+\subsection{Uniform Engine Performance}
+
+\subsection{Weighted Engine Performance}
+
+%-------------------------------------------------------------------------------
+\section{Conclusion}
+
+%-------------------------------------------------------------------------------
+\section{Possible Extensions}
 Here is a list of possible extension we could add.
@@
 	Further abstract the PDF, CDF, InvCDF to handle all kind of keys.
+	\item [Code Design]
+	We wonder if there was a way to avoid the \emph{MultiParamTypeClasses}
+	extension and to achieve a better design. 
+	Unfortunately time didn't allow further explorations.
 	\item [Testing]
@@
 \chapter{Code} \label{apx:code}
-We provide below the code.
+We provide below the code. It is screenshots from 
+\href{https://vim.sourceforge.io/}{Vim} with the 
+\href{https://github.com/begriffs/haskell-vim-now}{haskell-vim-now}.
+extension.
 
@@
 	\item Use cabal to download the require packages :
-\begin{lstlisting}[
-           language=SQL,
-           showspaces=false,
-           basicstyle=\ttfamily,
-           numbers=left,
-           numberstyle=\tiny,
-           commentstyle=\color{gray}
-        ]
-	cabal install TBC
-\end{lstlisting}
+\begin{itemize}
+	\item mersenne-random-pure64
+	\item countainers
+	\item random
+	\item mtl
+	\item QuickCheck
+	\item deepseq
+\end{itemize}
 \end{enumerate}

### 2017-09-04 src/ManAhl/CLI.hs
Modelise the parameters properly and added advanced stats

@@ -4,7 +4,6 @@ module ManAhl.CLI(
   run,
   help,
   Query(..), Result(..),
-  pillarsDefault
 ) where
 
 import ManAhl.Core.Types
@@ -17,10 +16,6 @@ import Data.List
 import Data.Maybe
 import Data.Map (toList)
 
--- | Default pillars if not specified
-pillarsDefault :: PdfPillars
-pillarsDefault = PdfPillars [(1, 0.2), (2, 0.3), (3, 0.1), (4, 0.15)]
-
 -- | Query to Run from the parsed input,
 -- Computing the statistics for :
 -- Either a weighted distribution
@@ -30,11 +25,11 @@ pillarsDefault = PdfPillars [(1, 0.2), (2, 0.3), (3, 0.1), (4, 0.15)]
 -- a selected uniform rng
 data Query =
       RunWeightedWith PdfPillars Int UniformRNGType
-    | RunUniformWith Int UniformRNGType
+    | RunUniformWith [(Double, Double)] Int UniformRNGType
   deriving (Show, Eq)
 instance NFData Query where
   rnf (RunWeightedWith (PdfPillars p) n u) = rnf p `seq` rnf n
-  rnf (RunUniformWith n u) = rnf n
+  rnf (RunUniformWith p n u) = rnf n `seq` rnf p
 
 data Result =
       ResultWeighted WeightedStats
@@ -46,37 +41,38 @@ data RunType = Weighted | Uniform
   deriving (Show, Read)
 
 -- | Helper to display the Results nicely
-showRes :: Show a => String -> Distribution a -> [(a, Double)] -> Int -> String
-showRes name stats proba n = unlines $
+showRes :: Show a => String -> Stats a -> String
+showRes name (Stats dist n (Just proba)
+    (Just diffProba) (Just diffMean) (Just diffStd)) = unlines $
      [
       "Result " ++ name ++ " Random Number Engine, " ++ show n ++ " random numbers."
      ,"Probabilities:"
      ] ++ showList' proba
      ++ ["", "Distribution:"]
-     ++ showList' (toList $ unPWC $ unDist stats)
+     ++ showList' (toPillars dist)
   where
     showList' :: (Show a, Show b) => [(a, b)] -> [String]
     showList' = map (\(x, p) -> show x ++ ";" ++ show p )
 
 instance Show Result where
-  show (ResultWeighted (Stats stats n (Just proba))) =
-    showRes "Weighted" stats proba n
-  show (ResultUniform (Stats stats n (Just proba))) =
[…]

### 2017-09-04 src/ManAhl/Core/Analytics.hs

@@ -1,4 +1,4 @@
-{-# LANGUAGE TupleSections, RecordWildCards, FlexibleInstances #-}
+{-# LANGUAGE TupleSections, RecordWildCards, FlexibleInstances, FlexibleContexts #-}
 -- | Module containing simple analytics
 module ManAhl.Core.Analytics(
   -- * Creation
@@ -7,7 +7,7 @@ module ManAhl.Core.Analytics(
   invCdf,(!!!),
   -- * Statistics
   mean, stdDev,
-  probabilities
+  statistics
 ) where
 
 import Data.Function (on)
@@ -58,12 +58,21 @@ mkInvCdf = fromPillars . Prelude.map (\(x, y) -> (y, x)) . toPillars
 invCdf :: InvCDF -> Double -> Maybe Int
 invCdf (InvCDF m) x = snd $ m !!! x
 
--- | Compute the probabilities from the result distribution
+-- | Compute the statistics from the result distribution
 -- O(n)
-probabilities :: Distribution a -> [(a, Double)]
-probabilities dist
-  = toPillars $ fmap (\ x -> fromIntegral x / fromIntegral n) $ unDist dist
-    where n = cFoldl (\acc x -> acc + x) 0 dist
+statistics :: (Ord a, Curve a Double b) => b -> Stats a -> Stats a
+statistics inputPdf s@(Stats dist n _ _ _ _)
+  = s{
+     hsProba = Just $ toPillars resPdf
+     ,hsDiffProba = Just diffP
+     ,hsDiffMean = Just $ mean diffs
+     ,hsDiffStd = Just $ stdDev diffs
+     }
+  where
+    diffs = snd $ unzip diffP
+    resPdf = fmap (\ x -> fromIntegral x / fromIntegral n) $ unDist dist
+    diffP = Map.toList $ Map.unionWith (-) (toRaw inputPdf) $ toRaw resPdf
+
 
 -- | Compute the mean for a non empty list
 -- O(n)

### 2017-09-04 src/ManAhl/Core/Types.hs

@@ -15,7 +15,7 @@ module ManAhl.Core.Types(
   Distribution(..),
   UniformRNGType(..),
   UniformRNG(..),
-  EngineParams(..),
+  WEngineParams(..), UEngineParams(..),
   Stats(..), UniStats, WeightedStats,
   Distri(..),
   Curve(..)
@@ -94,12 +94,19 @@ class Distri a where
 -- | Weighted Probability Engine Params
 -- contains the PDF, CDF, inverseCDF
 -- needed to compute the weighted probabilities
-data EngineParams =
-  WeightedEngineParams {
+data WEngineParams =
+  WEngineParams {
     pdf     :: PDF
    ,cdf     :: CDF
    ,iCdf    :: !InvCDF
-  } | UniformEngineParams
+  }
+
+-- | Uniform Probability Engine Params
+-- Used to pick the buckets, the probabilities are flat
+newtype UEngineParams =
+  UEngineParams {
+    uepPdf  :: PieceWiseCurve Double Double
+  }
 
 -- | Statistic of a given Run [a]
 --  hsDistri : represent the distribution of the  elements
@@ -107,16 +114,19 @@ data EngineParams =
 data Stats a =
   Stats {
     hsDistri      :: !(Distribution a)
-   ,hsTotalCount  :: !Int
+   ,hsCount       :: !Int
    ,hsProba       :: Maybe [(a, Double)]
+   ,hsDiffProba   :: Maybe [(a, Double)]
+   ,hsDiffMean    :: Maybe Double
+   ,hsDiffStd     :: Maybe Double
   }
 type UniStats = Stats Double
 type WeightedStats = Stats (Maybe Int)
 
 -- | Class to compute probabilities given an engine.
-class Monad a => ProbaEngine a b | a -> b where
+class Monad a => ProbaEngine a b c | a -> b, a -> c where
   -- | Compute the probabilities
-  computeProba :: EngineParams -> UniformRNG -> a c -> c
+  computeProba :: c -> UniformRNG -> a d -> d
   -- | Prepare the next random number
   nextNum :: a b
   -- | Prepare the n next random numbers
@@ -124,9 +134,9 @@ class Monad a => ProbaEngine a b | a -> b where
   nextNums n = replicateM n nextNum
 
 -- | Class to compute the statistics given an egine
-class Monad a => StatEngine a b | a -> b where
+class Monad a => StatEngine a b c | a -> b, a -> c where
[…]

### 2017-09-04 src/ManAhl/Core/UniformEngine.hs

@@ -2,6 +2,8 @@
 module ManAhl.Core.UniformEngine(
   -- * Creation
   mkUniformRNG,
+  mkUPEngineParams,
+  pillarsUDefault,
   -- * Engines
   ProbaUniEngine(),
   StatUniEngine()
@@ -30,29 +32,41 @@ instance RandomGen UniformRNG where
   split (RandomMersenne rng)    = let (g1, g2) = split rng in
                                    (RandomMersenne g1, RandomMersenne g2)
 
+pillarsUDefault :: [(Double, Double)]
+pillarsUDefault = map (\ x-> (x/100, 1/50)) [0,2..100]
+
 -- Create Uniform RNG encapsulating Mersenne or Ecuyer
 mkUniformRNG :: UniformRNGType -> IO UniformRNG
 mkUniformRNG Ecuyer   = return . RandomEcuyer =<< newStdGen
 mkUniformRNG Mersenne = return . RandomMersenne =<< newPureMT
 
-instance ProbaEngine ProbaUniEngine Double where
+mkUPEngineParams :: [(Double, Double)] -> Either String UEngineParams
+mkUPEngineParams pdfP
+  | null pdfP = Left "The pdf pillars are empty."
+  | any (\(_, x) -> abs( x - snd (head pdfP)) > 0.0001) pdfP =
+        Left "All the pdf probabilities must be equal, as it is uniform"
+  | abs (foldl (\ acc (_, x) -> acc + x) 0 pdfP - 1 ) < 0.0001 =
+        Left "The sum of PDF probabilities are different than 1."
+  | otherwise = Right $ UEngineParams $ fromPillars pdfP
+
+instance ProbaEngine ProbaUniEngine Double UEngineParams where
   computeProba _ r e = evalState (unPUIE e) r
 
   nextNum = state $! randomR (0, 1)
 
-instance StatEngine StatUniEngine Double where
-  computeStats _ r e = let
-      s = evalState (unSUE e) (Stats defaultDist 0 Nothing, r)
-   in s{ hsProba = Just $ probabilities $ hsDistri s }
+instance StatEngine StatUniEngine Double UEngineParams where
+  computeStats p r e = let
+      d = fromRaw $ Map.map (const 0::Double -> Int) $ toRaw $ uepPdf p
+   in statistics (uepPdf p) $
+     evalState (unSUE e) (Stats d 0 Nothing Nothing Nothing Nothing, r)
 
   nextStat = do
-    (Stats cs n _, uniRng) <- get
[…]

### 2017-09-04 src/ManAhl/Core/WeightedEngine.hs

@@ -2,7 +2,8 @@
 -- | The weighted proba engine
 module ManAhl.Core.WeightedEngine(
   -- * Creation
-  mkEngineParams,
+  mkWPEngineParams,
+  pillarsWDefault,
   -- * Engines
   ProbaWPEngine(),
   StatWPEngine()
@@ -17,51 +18,54 @@ import Control.Monad.State.Strict
 import Control.Monad.Reader
 import qualified Data.Map as Map
 
+-- | Default pillars if not specified
+pillarsWDefault :: PdfPillars
+pillarsWDefault = PdfPillars [(1, 0.2), (2, 0.3), (3, 0.1), (4, 0.15)]
+
 -- | Create a weighted probability engine parameters
 -- The creation can fail if the pdf pillars are incorrect.
 --
-mkEngineParams :: PdfPillars -> Either String EngineParams
-mkEngineParams pdfP =
+mkWPEngineParams :: PdfPillars -> Either String WEngineParams
+mkWPEngineParams pdfP =
   either
       (\ msg -> Left msg)
       (\ p -> let cdf' = mkCdf p in
-        Right WeightedEngineParams {
+        Right WEngineParams {
             pdf = p
            ,cdf = cdf'
            ,iCdf = mkInvCdf cdf'
          }) $ mkPdf pdfP
 
-instance ProbaEngine ProbaWPEngine (Maybe Int) where
+instance ProbaEngine ProbaWPEngine (Maybe Int) WEngineParams where
   computeProba p uniRng e =
     flip evalState uniRng $
       runReaderT (unPWPE e) p
 
   nextNum = do
-    WeightedEngineParams _ _ iCdf <- ask
+    WEngineParams _ _ iCdf <- ask
     uniRng <- get
     let (!x, !r) = runState (unPUIE nextNum) uniRng
     put r
     let !y = invCdf iCdf x
     return y
 
-instance StatEngine StatWPEngine (Maybe Int) where
-  computeStats p uniRng e = let
-      s = flip evalState
-        (Stats defaultDist 0 Nothing, uniRng) $
-          runReaderT (unSWP e) p
-       in s{ hsProba = Just $ probabilities $ hsDistri s }
+instance StatEngine StatWPEngine (Maybe Int) WEngineParams where
+  computeStats p uniRng e =
+    statistics (pdf p) $
+        flip evalState
+          (Stats defaultDist 0 Nothing Nothing Nothing Nothing, uniRng) $
[…]

### 2017-09-04 src/Test/ManAhl/CLI.hs

@@ -5,6 +5,8 @@ module Test.ManAhl.CLI(
 
 import ManAhl.CLI
 import ManAhl.Core.Types
+import ManAhl.Core.WeightedEngine
+import ManAhl.Core.UniformEngine
 import Test.ManAhl.QuickCheck hiding (run)
 
 import Control.Monad
@@ -20,35 +22,37 @@ tests = [
 testQuery :: Test
 testQuery = TestPure $ const $ t1 && t2 && t3 && t4 && t5
   where
-      t1 = parse [] == Just (RunWeightedWith pillarsDefault 1000000 Mersenne)
+      t1 = parse [] == Just (RunWeightedWith pillarsWDefault 1000000 Mersenne)
       t2 = parse ["-rng=Ecuyer"] ==
-                Just (RunWeightedWith pillarsDefault 1000000 Ecuyer)
+                Just (RunWeightedWith pillarsWDefault 1000000 Ecuyer)
       t3 = parse ["-rng=Ecuyer","-nSims=1"] ==
-                Just (RunWeightedWith pillarsDefault 1 Ecuyer)
+                Just (RunWeightedWith pillarsWDefault 1 Ecuyer)
       t4 = parse ["-rng=Ecuyer","-nSims=1","-pillars=[(1,0),(2,1)]"] ==
                 Just (RunWeightedWith (PdfPillars [(1, 0), (2, 1)]) 1 Ecuyer)
       t5 = parse ["-rng=Ecuyer","-nSims=1","-run=Uniform"] ==
-                Just (RunUniformWith 1 Ecuyer)
+                Just (RunUniformWith pillarsUDefault 1 Ecuyer)
 
 -- | Test a run for a given query
 testRun :: Test
 testRun = TestIO $ do
   let q1 = RunWeightedWith (PdfPillars [(1, 0.5), (2, 0.5)]) 1000000 Mersenne
-      q2 = RunUniformWith 1000000 Mersenne
+      q2 = RunUniformWith pillarsUDefault 1000000 Mersenne
 
   r1' <- run q1
-  let r1 = either (const False) ( \ (ResultWeighted (Stats _ _ (Just r))) ->
-          foldl (\ acc (_, x) ->
-            if not acc then False
-              else round (x * 100) == 50) True r
-          ) r1'
+  let r1 = either (const False) (
+          \ (ResultWeighted (Stats _ _ (Just r) _ _ _)) ->
+            foldl (\ acc (_, x) ->
+              if not acc then False
[…]

### 2017-09-04 src/Test/ManAhl/Core/UniformEngine.hs

@@ -37,7 +37,7 @@ propMeanStd :: UniformRNGType -> Test
 propMeanStd rngT =
   TestQCRng rngT $ \ rng ->
     Test.runWith 10 $ \ (x :: Int) ->
-      let vals = computeProba UniformEngineParams rng
+      let vals = computeProba (UEngineParams $ fromPillars pillarsUDefault) rng
                     (nextNums nRand :: ProbaUniEngine [Double])
           m = mean vals
           std = stdDev vals
@@ -51,7 +51,7 @@ propBounds rngT =
   TestQCRng rngT $ \ rng ->
     Test.runWith 10 $ \ (x :: Int) ->
       foldl (\ acc x -> if not acc then False else  x >= 0 && x <= 1) True $
-        computeProba UniformEngineParams rng
+        computeProba (UEngineParams $ fromPillars pillarsUDefault) rng
           (nextNums nRand :: ProbaUniEngine [Double])
 
 -- | Test the distribution of the uniform engine is uniform
@@ -59,7 +59,7 @@ propUniform :: UniformRNGType -> Test
 propUniform rT =
   TestQCRng rT $ \ rng ->
     Test.runWith 10 $ \ (x :: Int) ->
-      let stats = computeStats UniformEngineParams rng
+      let stats = computeStats (UEngineParams $ fromPillars pillarsUDefault) rng
                     (allStats nRand :: StatUniEngine UniStats)
           (Just proba) = hsProba stats
        in foldl (\ acc (_, x) ->
@@ -75,7 +75,7 @@ propPerf rT =
     Test.runWith 10 $ monadicIO $
   do
     t <- QC.run $ time $
-            computeStats UniformEngineParams rng
+          computeStats (UEngineParams $ fromPillars pillarsUDefault) rng
               (allStats 100000 :: StatUniEngine UniStats)
 
     let res = t < 0.45

### 2017-09-04 src/Test/ManAhl/Core/WeightedEngine.hs

@@ -35,7 +35,7 @@ propWeightedProba :: UniformRNGType -> Test
 propWeightedProba rT =
   TestQCRng rT $ \ rng ->
     Test.runWith 10 $ forAll genPdfPillars $ \ pdfP ->
-      let e = case mkEngineParams pdfP of
+      let e = case mkWPEngineParams pdfP of
             Left s -> error s; Right x -> x
           stats = computeStats e rng
                     (allStats 1000000 :: StatWPEngine WeightedStats)
@@ -49,10 +49,10 @@ testEngineFail :: Test
 testEngineFail = TestPure $ const $
       negativePro && nullPro && greaterPro && nullPro2
   where
-      negativePro = isLeft $ mkEngineParams $ PdfPillars [(1, -1)]
-      nullPro = isLeft $ mkEngineParams $ PdfPillars []
-      nullPro2 = isLeft $ mkEngineParams $ PdfPillars [(1,0)]
-      greaterPro = isLeft $ mkEngineParams $
+      negativePro = isLeft $ mkWPEngineParams $ PdfPillars [(1, -1)]
+      nullPro = isLeft $ mkWPEngineParams $ PdfPillars []
+      nullPro2 = isLeft $ mkWPEngineParams $ PdfPillars [(1,0)]
+      greaterPro = isLeft $ mkWPEngineParams $
                       PdfPillars [(1, 0.4), (2, 0.5), (3, 0.4)]
 
 -- | Test that the performance of the Engine remain acceptable
@@ -61,7 +61,7 @@ propPerf rT =
   TestQCRng rT $ \ rng ->
     Test.runWith 10 $ forAll genPdfPillars $ \ pdfP -> monadicIO $
     do
-      let e'= mkEngineParams pdfP
+      let e'= mkWPEngineParams pdfP
           e = case e' of Left s -> error s; Right x -> x
       t <- QC.run $ time $
               computeStats e rng

### 2017-09-04 src/ManAhl/CLI.hs
fix tests

@@ -14,10 +14,7 @@ import ManAhl.Core.WeightedEngine
 import Control.DeepSeq
 import Data.List
 import Data.Maybe
-import Data.Map (toList)
-
--- | Query to Run from the parsed input,
--- Computing the statistics for :
+import Data.Map (toList) -- | Query to Run from the parsed input, -- Computing the statistics for :
 -- Either a weighted distribution
 -- computed from the pillars for nSims and a selected uniform rng
 -- can be specified as well.
@@ -50,6 +47,10 @@ showRes name (Stats dist n (Just proba)
      ] ++ showList' proba
      ++ ["", "Distribution:"]
      ++ showList' (toPillars dist)
+     ++ ["", "Diff res and input PDFs:"]
+     ++ showList' diffProba
+     ++ ["", "Mean of the PDF Diffs: " ++ show diffMean]
+     ++ ["", "StdDev of the PDF Diffs: " ++ show diffStd]
   where
     showList' :: (Show a, Show b) => [(a, b)] -> [String]
     showList' = map (\(x, p) -> show x ++ ";" ++ show p )

### 2017-09-04 src/ManAhl/Core/Types.hs

@@ -17,7 +17,6 @@ module ManAhl.Core.Types(
   UniformRNG(..),
   WEngineParams(..), UEngineParams(..),
   Stats(..), UniStats, WeightedStats,
-  Distri(..),
   Curve(..)
 ) where
 
@@ -83,13 +82,6 @@ class Curve b c a | a -> b, a -> c where
   cFoldl :: (d -> c -> d) -> d -> a -> d
   -- | O(n) appy a function to each pillar
   cMap :: (c -> c) -> a -> a
-
--- | Class to operate a Distribution
-class Distri a where
-  -- | O(log n) add an element
-  increaseCount :: a -> Distribution a -> Distribution a
-  -- | Range used to compute the statistics
-  defaultDist :: Distribution a
 
 -- | Weighted Probability Engine Params
 -- contains the PDF, CDF, inverseCDF
@@ -203,13 +195,6 @@ instance Curve a b (PieceWiseCurve a b) where
   add x y c = PieceWiseCurve $ Map.insert x y $ toRaw c
   cFoldl f x m = Map.foldl f x $ toRaw m
   cMap = fmap
-
-instance Distri (Maybe Int) where
-  increaseCount x = addWith (+) x 1
-  defaultDist = emptyCurve
-instance Distri Double where
-  increaseCount x = addWith (+) (fst $ defaultDist !!! x) 1
-  defaultDist = fromPillars $ zip (Prelude.map (/100) [1, 2 .. 100]) [0..]
 
 instance NFData a => NFData (Stats a) where
   rnf (Stats d t p dP dM dS) = rnf d `seq` rnf t `seq` rnf p

### 2017-09-04 src/ManAhl/Core/UniformEngine.hs

@@ -33,7 +33,7 @@ instance RandomGen UniformRNG where
                                    (RandomMersenne g1, RandomMersenne g2)
 
 pillarsUDefault :: [(Double, Double)]
-pillarsUDefault = map (\ x-> (x/100, 1/50)) [0,2..100]
+pillarsUDefault = tail $ map (\ x-> (x/100, 1/50)) [0,2..100]
 
 -- Create Uniform RNG encapsulating Mersenne or Ecuyer
 mkUniformRNG :: UniformRNGType -> IO UniformRNG
@@ -45,7 +45,7 @@ mkUPEngineParams pdfP
   | null pdfP = Left "The pdf pillars are empty."
   | any (\(_, x) -> abs( x - snd (head pdfP)) > 0.0001) pdfP =
         Left "All the pdf probabilities must be equal, as it is uniform"
-  | abs (foldl (\ acc (_, x) -> acc + x) 0 pdfP - 1 ) < 0.0001 =
+  | abs (foldl (\ acc (_, x) -> acc + x) 0 pdfP - 1 ) > 0.0001 =
         Left "The sum of PDF probabilities are different than 1."
   | otherwise = Right $ UEngineParams $ fromPillars pdfP
 
@@ -64,7 +64,7 @@ instance StatEngine StatUniEngine Double UEngineParams where
     (stats, uniRng) <- get
     let (!x, !r) = runState (unPUIE nextNum) uniRng
         !stats' = stats {
-            hsDistri = increaseCount x $ hsDistri stats
+            hsDistri = addWith (+) (fst $ (hsDistri stats) !!! x) 1 $ hsDistri stats
            ,hsCount  = hsCount stats + 1
           }
     put (stats', r)

### 2017-09-04 src/ManAhl/Core/WeightedEngine.hs

@@ -53,7 +53,7 @@ instance StatEngine StatWPEngine (Maybe Int) WEngineParams where
   computeStats p uniRng e =
     statistics (pdf p) $
         flip evalState
-          (Stats defaultDist 0 Nothing Nothing Nothing Nothing, uniRng) $
+          (Stats emptyCurve 0 Nothing Nothing Nothing Nothing, uniRng) $
             runReaderT (unSWP e) p
 
   nextStat = do
@@ -63,7 +63,7 @@ instance StatEngine StatWPEngine (Maybe Int) WEngineParams where
         !y = invCdf iCdf x
 
         !stats' = stats {
-            hsDistri = increaseCount y $ hsDistri stats
+            hsDistri = addWith (+) y 1  $ hsDistri stats
            ,hsCount  = hsCount stats + 1
           }
     put (stats', r)

### 2017-09-04 src/Test/ManAhl/Core/UniformEngine.hs

@@ -61,11 +61,9 @@ propUniform rT =
     Test.runWith 10 $ \ (x :: Int) ->
       let stats = computeStats (UEngineParams $ fromPillars pillarsUDefault) rng
                     (allStats nRand :: StatUniEngine UniStats)
-          (Just proba) = hsProba stats
+          (Just diffProba) = hsDiffProba stats
        in foldl (\ acc (_, x) ->
-          if not acc then False
-              else round (x * 100) ==
-                round (100 / fromIntegral (nPillars $ hsDistri stats))) True proba
+         if not acc then False else x < 0.001) True diffProba
 
 -- | Ensure that the performance of the uniform engine
 -- remain acceptable

### 2017-09-04 src/ManAhl/Core/UniformEngine.hs
Add checks

@@ -43,6 +43,10 @@ mkUniformRNG Mersenne = return . RandomMersenne =<< newPureMT
 mkUPEngineParams :: [(Double, Double)] -> Either String UEngineParams
 mkUPEngineParams pdfP
   | null pdfP = Left "The pdf pillars are empty."
+  | foldl (\ acc (x, _) -> if acc then acc else x < 0 || x > 1) False pdfP =
+      Left "PDF Pillars contain negative values or greater than 1."
+  | foldl (\ acc (_, x) -> if acc then acc else x < 0 || x > 1) False pdfP =
+      Left "PDF Pillars contain negative values or greater than 1."
   | any (\(_, x) -> abs( x - snd (head pdfP)) > 0.0001) pdfP =
         Left "All the pdf probabilities must be equal, as it is uniform"
   | abs (foldl (\ acc (_, x) -> acc + x) 0 pdfP - 1 ) > 0.0001 =

### 2017-09-04 src/ManAhl/Core/UniformEngine.hs
optimise uniform engine

@@ -33,7 +33,7 @@ instance RandomGen UniformRNG where
                                    (RandomMersenne g1, RandomMersenne g2)
 
 pillarsUDefault :: [(Double, Double)]
-pillarsUDefault = tail $ map (\ x-> (x/100, 1/50)) [0,2..100]
+pillarsUDefault = map (\ x-> (x/100, 1/50)) [2,4..100]
 
 -- Create Uniform RNG encapsulating Mersenne or Ecuyer
 mkUniformRNG :: UniformRNGType -> IO UniformRNG

### 2017-09-04 src/Test/ManAhl/Core/UniformEngine.hs
Fix test, revert the accuracy to what it was

@@ -60,10 +60,10 @@ propUniform rT =
   TestQCRng rT $ \ rng ->
     Test.runWith 10 $ \ (x :: Int) ->
       let stats = computeStats (UEngineParams $ fromPillars pillarsUDefault) rng
-                    (allStats nRand :: StatUniEngine UniStats)
+                    (allStats 100000 :: StatUniEngine UniStats)
           (Just diffProba) = hsDiffProba stats
        in foldl (\ acc (_, x) ->
-         if not acc then False else x < 0.001) True diffProba
+         if not acc then False else x < 0.01) True diffProba
 
 -- | Ensure that the performance of the uniform engine
 -- remain acceptable

### 2017-09-04 src/ManAhl/CLI.hs
Add hi and low to diff stats

@@ -40,7 +40,8 @@ data RunType = Weighted | Uniform
 -- | Helper to display the Results nicely
 showRes :: Show a => String -> Stats a -> String
 showRes name (Stats dist n (Just proba)
-    (Just diffProba) (Just diffMean) (Just diffStd)) = unlines $
+    (Just diffProba) (Just diffMean) (Just diffStd)
+    (Just diffHi) (Just diffLow) ) = unlines $
      [
       "Result " ++ name ++ " Random Number Engine, " ++ show n ++ " random numbers."
      ,"Probabilities:"
@@ -51,6 +52,8 @@ showRes name (Stats dist n (Just proba)
      ++ showList' diffProba
      ++ ["", "Mean of the PDF Diffs: " ++ show diffMean]
      ++ ["", "StdDev of the PDF Diffs: " ++ show diffStd]
+     ++ ["", "Highest of the PDF Diffs: " ++ show diffHi]
+     ++ ["", "Lowest of the PDF Diffs: " ++ show diffLow]
   where
     showList' :: (Show a, Show b) => [(a, b)] -> [String]
     showList' = map (\(x, p) -> show x ++ ";" ++ show p )

### 2017-09-04 src/ManAhl/Core/Analytics.hs

@@ -61,12 +61,14 @@ invCdf (InvCDF m) x = snd $ m !!! x
 -- | Compute the statistics from the result distribution
 -- O(n)
 statistics :: (Ord a, Curve a Double b) => b -> Stats a -> Stats a
-statistics inputPdf s@(Stats dist n _ _ _ _)
+statistics inputPdf s@(Stats dist n _ _ _ _ _ _)
   = s{
      hsProba = Just $ toPillars resPdf
      ,hsDiffProba = Just diffP
      ,hsDiffMean = Just $ mean diffs
      ,hsDiffStd = Just $ stdDev diffs
+     ,hsDiffHi = Just $ maximum diffs
+     ,hsDiffLow = Just $ minimum diffs
      }
   where
     diffs = snd $ unzip diffP

### 2017-09-04 src/ManAhl/Core/Types.hs

@@ -111,6 +111,8 @@ data Stats a =
    ,hsDiffProba   :: Maybe [(a, Double)]
    ,hsDiffMean    :: Maybe Double
    ,hsDiffStd     :: Maybe Double
+   ,hsDiffHi      :: Maybe Double
+   ,hsDiffLow     :: Maybe Double
   }
 type UniStats = Stats Double
 type WeightedStats = Stats (Maybe Int)
@@ -197,7 +199,8 @@ instance Curve a b (PieceWiseCurve a b) where
   cMap = fmap
 
 instance NFData a => NFData (Stats a) where
-  rnf (Stats d t p dP dM dS) = rnf d `seq` rnf t `seq` rnf p
+  rnf (Stats d t p dP dM dS dH dL) = rnf d `seq` rnf t `seq` rnf p
                                 `seq` rnf dP `seq` rnf dM `seq` rnf dS
+                                  `seq` rnf dH `seq` rnf dL
 instance (NFData a, NFData b) => NFData (PieceWiseCurve a b) where
   rnf (PieceWiseCurve c) = rnf c

### 2017-09-04 src/ManAhl/Core/UniformEngine.hs

@@ -62,7 +62,8 @@ instance StatEngine StatUniEngine Double UEngineParams where
   computeStats p r e = let
       d = fromRaw $ Map.map (const 0::Double -> Int) $ toRaw $ uepPdf p
    in statistics (uepPdf p) $
-     evalState (unSUE e) (Stats d 0 Nothing Nothing Nothing Nothing, r)
+     evalState (unSUE e)
+        (Stats d 0 Nothing Nothing Nothing Nothing Nothing Nothing, r)
 
   nextStat = do
     (stats, uniRng) <- get

### 2017-09-04 src/ManAhl/Core/WeightedEngine.hs

@@ -53,8 +53,9 @@ instance StatEngine StatWPEngine (Maybe Int) WEngineParams where
   computeStats p uniRng e =
     statistics (pdf p) $
         flip evalState
-          (Stats emptyCurve 0 Nothing Nothing Nothing Nothing, uniRng) $
-            runReaderT (unSWP e) p
+          (Stats emptyCurve 0 Nothing Nothing Nothing Nothing
+              Nothing Nothing, uniRng) $
+                runReaderT (unSWP e) p
 
   nextStat = do
     WEngineParams _ _ iCdf <- ask

### 2017-09-04 src/Test/ManAhl/CLI.hs

@@ -40,7 +40,7 @@ testRun = TestIO $ do
 
   r1' <- run q1
   let r1 = either (const False) (
-          \ (ResultWeighted (Stats _ _ (Just r) _ _ _)) ->
+          \ (ResultWeighted (Stats _ _ (Just r) _ _ _ _  _)) ->
             foldl (\ acc (_, x) ->
               if not acc then False
                 else round (x * 100) == 50) True r
@@ -48,7 +48,7 @@ testRun = TestIO $ do
 
   r2' <- run q2
   let r2 = either (const False) (
-          \ (ResultUniform (Stats _  _ (Just r) _ _ _)) ->
+          \ (ResultUniform (Stats _  _ (Just r) _ _ _ _ _)) ->
             foldl (\ acc (_, x) ->
               if not acc then False
                 else round (x * 100) ==

### 2017-09-04 src/ManAhl/CLI.hs
Add new tests engine params and statistics

@@ -50,10 +50,10 @@ showRes name (Stats dist n (Just proba)
      ++ showList' (toPillars dist)
      ++ ["", "Diff res and input PDFs:"]
      ++ showList' diffProba
-     ++ ["", "Mean of the PDF Diffs: " ++ show diffMean]
-     ++ ["", "StdDev of the PDF Diffs: " ++ show diffStd]
-     ++ ["", "Highest of the PDF Diffs: " ++ show diffHi]
-     ++ ["", "Lowest of the PDF Diffs: " ++ show diffLow]
+     ++ ["", "Mean of the PDF Diffs; " ++ show diffMean]
+     ++ ["StdDev of the PDF Diffs; " ++ show diffStd]
+     ++ ["Highest of the PDF Diffs; " ++ show diffHi]
+     ++ ["Lowest of the PDF Diffs; " ++ show diffLow]
   where
     showList' :: (Show a, Show b) => [(a, b)] -> [String]
     showList' = map (\(x, p) -> show x ++ ";" ++ show p )

### 2017-09-04 src/ManAhl/Core/UniformEngine.hs

@@ -33,7 +33,7 @@ instance RandomGen UniformRNG where
                                    (RandomMersenne g1, RandomMersenne g2)
 
 pillarsUDefault :: [(Double, Double)]
-pillarsUDefault = map (\ x-> (x/100, 1/50)) [2,4..100]
+pillarsUDefault = map (\ x-> (x/100, 1/5)) [20,40..100]
 
 -- Create Uniform RNG encapsulating Mersenne or Ecuyer
 mkUniformRNG :: UniformRNGType -> IO UniformRNG
@@ -43,6 +43,8 @@ mkUniformRNG Mersenne = return . RandomMersenne =<< newPureMT
 mkUPEngineParams :: [(Double, Double)] -> Either String UEngineParams
 mkUPEngineParams pdfP
   | null pdfP = Left "The pdf pillars are empty."
+  | null $ filter (\(_, x) -> x /= 0) pdfP =
+      Left "The pdf pillars contain only zero."
   | foldl (\ acc (x, _) -> if acc then acc else x < 0 || x > 1) False pdfP =
       Left "PDF Pillars contain negative values or greater than 1."
   | foldl (\ acc (_, x) -> if acc then acc else x < 0 || x > 1) False pdfP =
@@ -51,7 +53,8 @@ mkUPEngineParams pdfP
         Left "All the pdf probabilities must be equal, as it is uniform"
   | abs (foldl (\ acc (_, x) -> acc + x) 0 pdfP - 1 ) > 0.0001 =
         Left "The sum of PDF probabilities are different than 1."
-  | otherwise = Right $ UEngineParams $ fromPillars pdfP
+  | otherwise = Right $ UEngineParams $ fromPillars $
+        filter (\(_, x) -> x /= 0) pdfP
 
 instance ProbaEngine ProbaUniEngine Double UEngineParams where
   computeProba _ r e = evalState (unPUIE e) r

### 2017-09-04 src/Test/ManAhl/Core/Analytics.hs

@@ -57,6 +57,7 @@ tests = map (\(x, y) -> ("Analytics - " ++ x, y))
    ,("Std Failure",                     testStdFail)
    ,("PDF No regression",               testPDFNoRegression)
    ,("InvCDF No regression",            testInvCDFNoRegression)
+   ,("Statistics No regression",        testStatistics)
   ]
 
 -- | Ensure that the last pillars of the CDF is 100%
@@ -157,4 +158,21 @@ testInvCDFNoRegression =
               Right pdf ->
                 mkInvCdf (mkCdf pdf) ==
                   fromPillars [(0.3, Just 1), (0.7, Just 2), (1, Just 3)]
+
+-- | Test the statistics
+testStatistics:: Test
+testStatistics =
+  TestPure $ const $
+    let
+      dist = fromPillars [(Just 1, 10), (Just 2, 10), (Just 3, 80)]
+        :: Distribution (Maybe Int)
+      stats = Stats dist 100 Nothing Nothing
+                  Nothing Nothing Nothing Nothing
+      Stats d n (Just pb) (Just p) (Just m) (Just s) (Just h) (Just l) =
+           statistics pdf stats
+      pdf = fromPillars [(Just 1, 0.11), (Just 2, 0.1), (Just 3, 0.8)] :: PDF
+      x ~= y = abs (x - y) < 0.001
+      diff = fromPillars [(Just 1, 0.01), (Just 2, 0), (Just 3, 0)] :: PDF
+   in m ~= (0.01/3) && h ~= 0.01 && l ~= 0 && s ~= 0.0057
+        && fromPillars pb == pdf && fromPillars p == diff
 

### 2017-09-04 src/Test/ManAhl/Core/UniformEngine.hs

@@ -9,6 +9,7 @@ import Test.QuickCheck.Monadic as QC
 import Test.ManAhl.QuickCheck as Test
 
 import Control.Monad
+import Data.Either
 import qualified Data.Map as Map
 import Data.Maybe
 import Text.Printf (printf)
@@ -29,6 +30,7 @@ tests = map (\(x, y) -> ("Uniform Engine - " ++ x, y))
    ,("Ecuyer Uniform",        propUniform Ecuyer)
    ,("Mersenee Perf",         propPerf Mersenne)
    ,("Ecuyer Perf",           propPerf Ecuyer)
+   ,("fail",                  testEngineFail)
   ]
 
 -- | Test that the standard deviation and mean of the uniform
@@ -60,10 +62,9 @@ propUniform rT =
   TestQCRng rT $ \ rng ->
     Test.runWith 10 $ \ (x :: Int) ->
       let stats = computeStats (UEngineParams $ fromPillars pillarsUDefault) rng
-                    (allStats 100000 :: StatUniEngine UniStats)
-          (Just diffProba) = hsDiffProba stats
-       in foldl (\ acc (_, x) ->
-         if not acc then False else x < 0.01) True diffProba
+                    (allStats 1000000 :: StatUniEngine UniStats)
+          (Just std) = hsDiffStd stats
+       in std < 0.001
 
 -- | Ensure that the performance of the uniform engine
 -- remain acceptable
@@ -80,3 +81,15 @@ propPerf rT =
     unless res $ do
       QC.run $ printf "Time %s: %0.9f sec" (show rT) t
     assert res
+
+-- | Test that EngineParams fails to build for all
+-- expected cases
+testEngineFail :: Test
+testEngineFail = TestPure $ const $
+      negativePro && nullPro && greaterPro && nullPro2
+  where
+      negativePro = isLeft $ mkUPEngineParams [(1, -1)]
+      nullPro = isLeft $ mkUPEngineParams  [(1,0.5), (2,0.3), (3,0.2)]
+      nullPro2 = isLeft $ mkUPEngineParams [(1,0)]
+      greaterPro = isLeft $ mkUPEngineParams $
+                      [(1, 0.4), (2, 0.5), (3, 0.4)]

### 2017-09-04 src/Test/ManAhl/Core/WeightedEngine.hs

@@ -39,9 +39,8 @@ propWeightedProba rT =
             Left s -> error s; Right x -> x
           stats = computeStats e rng
                     (allStats 1000000 :: StatWPEngine WeightedStats)
-          pdf' = pdf e
-          (Just proba) = hsProba stats
-       in pdf' == fromPillars proba
+          (Just std) = hsDiffStd stats
+       in std < 0.001
 
 -- | Test that EngineParams fails to build for all
 -- expected cases

### 2017-09-04 tex/paper/paper.tex
Near final version of the paper

@@
 \listoffigures
-%\listoftables
+\listoftables
+\vfill
 \newpage
@@
 We interpret the question as the following the mathematical problem. 
-We define a $X$ as a discrete random variable. 
+We define $X$ as a discrete random variable. 
 As input, we have a $k$ values, $x_i$, with their associated probabilities, $p_i$.
@@
 } (This implementation claims to be faster than Ecuyer's one.) and Ecuyer\footnote{
-This is the default random number generator in haskell one in haskell.
+This is the default random number generator in haskell.
  This implementation uses the Portable Combined Generator of L'Ecuyer
@@
 	}, the discrete cumulative function, 
-	the inverse discrete cumulative function and the mean and
+	the inverse discrete cumulative function, the mean and
 	standard deviation functions.
@@
 time ./dist/build/MAN-AHL/MAN-AHL -run=Weighted -nSims=1000000
-        -pillars=''
+        -pillars='[(1, 0.5), (2, 0.5)]'
 \end{verbatim}
@@
 
-The aim was to keep the software as simple as possible while targetting a
+The aim was to keep the software as simple as possible while targeting a
 good design and performance. 
@@
 code needs less documentation. The complexities are presented in the key
-area of the code. The code is presented in \autoref{apx:code}.
+area of the code.
 
@@
 	$p_i$ and ensure that $\sum_i p_i \leq 1$.
-	If needed we a a pillar representing non selected element 
+	If needed we add a pillar representing non selected element 
 	as \emph{Nothing}. This way we ensure that the probabilities
@@
 In a way, we lose static typing here in order to merge all the types of 
-request and to dispatch the query to the appropriate engine. And we merge
+requests and to dispatch the query to the appropriate engine. And we merge
 back the result into the \emph{Result} to provide a single function achieving
@@
 The following Test Suites, i.e. lists of tests, compose our test plan split by modules.
+There is more on the testing in \autoref{sec:quality}. We expand on what is a correct 
+metric for this problem.
 
@@
 		generate probabilities with the $[0, 1]$ bound.
-		Run $10$ times for $100000$ random numbers.
+		Run $10$ times for $1000000$ random numbers.
 	\item [Uniform]
@@
 		by making sure that we match a flat distribution at 0.001
-		precision.
+		precision on the standard deviation of the difference
+		between the PDFs.
 		Run 10 times for $100000$ random numbers.
@@
 		We check that we recover the PDF distribution from
-		a sample of 1000000 random numbers at $0.1\%$ precision.
+		a sample of 1000000 random numbers at $0.1\%$ precision
+		on the standard deviation of the differences with the 
+		generated PDF.
 		We run this for 10 pseudo random PDF.
@@
 \section{Qualitative Analysis}
+\label{sec:quality}
 We realise that we maybe be beyond the scope of the initial
@@
 However how to test it efficiently ? It is a very hard question.
+This led us to look at the distribution of the results to ensure
+the quality of the numbers generated.
 
-It is an important part of Software Engineering and 
-Quantitative Development to understand the 
-meaning of what we are trying to achieve. 
-It allows better modelisation, algoritms and testing. 
 In this section, we will look at the number generated and try
@@
 To assess the quality of a random number engine, we use
-simple statistics. It would have been nice to have time to 
-study further statistical and mathematical papers related 
-to the random numbers generation and probabilities.
-We could have created with more advanced metrics.
+simple statistics.
 
-There are two keys elements which drive the results :
+There are two keys elements that drive the results :
 the input discrete probability function with $k$ pillars and
@@
 
-We also have two random numbers generator, 
+We also have two random numbers generators, 
 Mersenne and Ecuyer, available. We compare them thoughout.
@@
 As our weighted probability engine depends on
-the uniform probability engine. 
-We test first the uniform engine.
+the uniform probability engine, we test first the uniform engine.
 
@@
 	\item the standard deviation of these differences,
-	\item the mean of these difference, hopefully close to zero.
+	\item the mean of these differences, hopefully close to zero,
+	\item and the highest and lowest differences.
 \end{itemize}
@@
 
-\begin{figure}[h!]
-    \centering
-    \begin{subfigure}[b]{0.45\textwidth}
-        \includegraphics[width=\textwidth]{img/uni-m-1.png}
-        \caption{A gull}
-        \label{fig:gull}
-    \end{subfigure}
-    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
-      %(or a blank line to force the subfigure onto a new line)
-    \begin{subfigure}[b]{0.45\textwidth}
-        \includegraphics[width=\textwidth]{img/uni-m-1.png}
-        \caption{A tiger}
-        \label{fig:tiger}
-    \end{subfigure}
+\autoref{tab:uni.test} presents several runs for various number of random
+numbers for each random number generators, which can be use in
+the bounded uniform probability engine.
+% Table generated by Excel2LaTeX from sheet 'Sheet5'
+\begin{table}[htbp!]
+  \centering \tiny
+    \begin{tabular}{r|rrrrrr}
+    \multicolumn{1}{r}{} & \multicolumn{2}{c}{1000000} & \multicolumn{2}{c}{100000} & \multicolumn{2}{c}{10000} \\
+    \multicolumn{1}{r}{} & Mersenne & Ecuyer & Mersenne & Ecuyer & Mersenne & Ecuyer \\
+\cmidrule{2-7}    Mean  & 5.55E-19 & 4.16E-19 & 4.86E-19 & 2.78E-19 & 5.55E-19 & 4.16E-19 \\
+    StdDev  & 1.08E-04 & 1.27E-04 & 4.42E-04 & 4.80E-04 & 1.47E-03 & 1.29E-03 \\
+    Highest  & 1.89E-04 & 2.89E-04 & 9.90E-04 & 1.01E-03 & 3.80E-03 & 2.50E-03 \\
+    Lowest  & -2.91E-04 & -2.93E-04 & -1.56E-03 & -1.25E-03 & -3.10E-03 & -2.60E-03 \\
+    \end{tabular}%
+  \caption{Uniform Distribution Test}
+  \label{tab:uni.test}%
+\end{table}%
 
-    \begin{subfigure}[b]{0.45\textwidth}
-        \includegraphics[width=\textwidth]{img/uni-m-1.png}
-        \caption{A gull}
-        \label{fig:gull}
-    \end{subfigure}
-    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
-      %(or a blank line to force the subfigure onto a new line)
-    \begin{subfigure}[b]{0.45\textwidth}
-        \includegraphics[width=\textwidth]{img/uni-m-1.png}
-        \caption{A tiger}
-        \label{fig:tiger}
-    \end{subfigure}
+The best standard deviation we achieve is of the order of $e-4$.
+The mean is very close to zero with both generators and the results 
+are very similar.
+Hence setting $n$ to 1000000 for more accurate testing, 
+i.e. of the order of $e-4$, is recommanded.
 
-    \begin{subfigure}[b]{0.45\textwidth}
-        \includegraphics[width=\textwidth]{img/uni-m-1.png}
-        \caption{A gull}
-        \label{fig:gull}
-    \end{subfigure}
-    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
-      %(or a blank line to force the subfigure onto a new line)
-    \begin{subfigure}[b]{0.45\textwidth}
-        \includegraphics[width=\textwidth]{img/uni-m-1.png}
-        \caption{A tiger}
-        \label{fig:tiger}
-    \end{subfigure}
-    \caption{Pictures of animals}\label{fig:animals}
-\end{figure}
+We tried various $k$, less than 100 to remain realistic. It has no impact on the
+results as expected.
 
 \subsection{Weighted Distribution}
+
+Therefore we can't expect to achieve better accuracy with the
+weighted probability engine as it relies on the bounded uniform engine.
+
+We present in \autoref{tab:w.test}, the result of multiple runs with various $n$.
+% Table generated by Excel2LaTeX from sheet 'Sheet5'
+\begin{table}[htbp!]
+  \centering \tiny
+    \begin{tabular}{r|rrrrrr}
+    \multicolumn{1}{r}{} & \multicolumn{2}{c}{1000000} & \multicolumn{2}{c}{100000} & \multicolumn{2}{c}{10000} \\
+    \multicolumn{1}{r}{} & Mersenne & Ecuyer & Mersenne & Ecuyer & Mersenne & Ecuyer \\
+\cmidrule{2-7}    Mean  & -3.73E-18 & -3.36E-18 & -3.45E-18 & -3.96E-18 & -3.38E-18 & -3.26E-18 \\
+    StdDev  & 1.71E-04 & 1.49E-04 & 5.14E-04 & 4.61E-04 & 1.79E-03 & 1.91E-03 \\
+    Highest  & 7.88E-04 & 2.70E-04 & 1.13E-03 & 8.00E-04 & 5.20E-03 & 5.50E-03 \\
+    Lowest  & -2.99E-04 & -3.61E-04 & -1.34E-03 & -1.25E-03 & -5.10E-03 & -5.52E-03 \\
+    \end{tabular}%
+  \caption{Weighted Distribution Test}
+  \label{tab:w.test}%
+\end{table}%
+The result are very close to the precision of the uniform engine. 
+We therefore recommand the same setting as before for $n$ and $k$.
 
@@
 \subsection{Complexity Analysis}
+We commented some of the code with the complexities.
+The computation of the weighted distribution for $n$ random number generated, 
+i.e. the function \emph{allStats}, with a PDF of $k$ pillars, is :
+\[
+	O(n . log (k) . rng )
+\]
+where $rng$ is the complexity of the raw random number generator.
 
 \subsection{Uniform Engine Performance}
+\autoref{tab:uni.perf} presents the result of many runs with various $n$ and
+the heap that was allocated during the run and the time taken.
+\begin{table}[htbp!]
+  \centering \tiny
+    \begin{tabular}{r|rrrrrr}
+    \multicolumn{1}{r}{} & \multicolumn{2}{c}{1000000} & \multicolumn{2}{c}{100000} & \multicolumn{2}{c}{10000} \\
+    \multicolumn{1}{r}{} & Mersenne & Ecuyer & Mersenne & Ecuyer & Mersenne & Ecuyer \\
+\cmidrule{2-7}    Heap  & 2,724,561,112 & 3,360,007,920 & 274,635,272 & 338,190,648 & 29,602,472 & 35,953,944 \\
+    Time  & 3.576 & 3.707 & 0.347 & 0.373 & 0.041 & 0.041 \\
+    \end{tabular}%
+  \caption{Uniform Engine Performance}
+  \label{tab:uni.perf}%
+\end{table}%
+Most of the heap allocation and the time is consumed by the underlying 
+random number generator, the various engines adds only minor overhead, 
+as shown on the profiling results, c.f. \autoref{fig:perf1} and \autoref{fig:perf2}.
+We can see that the time and space are linear with respect to $n$. 
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=1\textwidth]{img/prof1.png}
+\caption{Performance Profiling 1}
+\label{fig:perf1}
+\end{center}
+\end{figure}
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=1\textwidth]{img/prof2.png}
+\caption{Performance Profiling 2}
+\label{fig:perf2}
+\end{center}
+\end{figure}
+%\begin{figure}[h!]
+%\begin{center}
+%\includegraphics[width=1\textwidth]{img/prof3.png}
+%\caption{Performance Profiling 3}
+%\label{fig:perf3}
+%\end{center}
+%\end{figure}
+We can conclude that the complexity of the inner random number generators
+are $O(1)$ in time and $O(n)$ in space. Indeed the function \emph{allStats} for the
+\emph{StatUniEngine} does not store the number generated, 
+just the distribution of these.
+
+We notice that Ecuyer take much more space, therefore our default setting
+is set to Mersenne.
 
@@
 
-%-------------------------------------------------------------------------------
-\section{Conclusion}
+\autoref{tab:w.perf} presents similar results for the \emph{StatWPEngine}, 
+i.e. the statistic weighted probability engine.
+\begin{table}[htbp!]
+  \centering \tiny
+    \begin{tabular}{r|rrrrrr}
+    \multicolumn{1}{r}{} & \multicolumn{2}{c}{1000000} & \multicolumn{2}{c}{100000} & \multicolumn{2}{c}{10000} \\
+    \multicolumn{1}{r}{} & Mersenne & Ecuyer & Mersenne & Ecuyer & Mersenne & Ecuyer \\
+\cmidrule{2-7}    Heap  & 2,777,630,784 & 3,419,213,784 & 281,175,032 & 344,423,280 & 30,695,560 & 37,067,344 \\
+    Time  & 3.612 & 3.81  & 0.357 & 0.379 & 0.038 & 0.043 \\
+    \end{tabular}%
+  \caption{Weighted Engine Performance}
+  \label{tab:w.perf}%
+\end{table}%
+The results shows that there is little overhead for the weighted probabilities
+engines. The results are very similar to \autoref{tab:uni.perf}.
+This conforts us in the computation of our complexities.
 
@@
 	Further abstract the PDF, CDF, InvCDF to handle all kind of keys.
-	\item [Code Design]
-	We wonder if there was a way to avoid the \emph{MultiParamTypeClasses}
-	extension and to achieve a better design. 
-	Unfortunately time didn't allow further explorations.
 	\item [Testing]
@@
 
-%-------------------------------------------------------------------------------
-\newpage
-\appendix
-\addcontentsline{toc}{chapter}{Appendices}
-
-\chapter{Code} \label{apx:code}
-We provide below the code. It is screenshots from 
-\href{https://vim.sourceforge.io/}{Vim} with the 
-\href{https://github.com/begriffs/haskell-vim-now}{haskell-vim-now}.
-extension.
-
-%-------------------------------------------------------------------------------
-\newpage
-\chapter{Installation} \label{apx:installation}
-
-Here are the steps to install the App.
-\begin{enumerate}
-	\item Download Haskell via this \href{https://www.haskell.org/platform/}{link}.
-	\item Install following the instructions given by the installer.
-	\item Use cabal to download the require packages :
-\begin{itemize}
-	\item mersenne-random-pure64
-	\item countainers
-	\item random
-	\item mtl
-	\item QuickCheck
-	\item deepseq
-\end{itemize}
-\end{enumerate}
 \end{document}

### 2017-09-04 src/ManAhl/Core/Analytics.hs
comment

@@ -58,8 +58,7 @@ mkInvCdf = fromPillars . Prelude.map (\(x, y) -> (y, x)) . toPillars
 invCdf :: InvCDF -> Double -> Maybe Int
 invCdf (InvCDF m) x = snd $ m !!! x
 
--- | Compute the statistics from the result distribution
--- O(n)
+-- | Compute the statistics from the result distribution and original PDF
 statistics :: (Ord a, Curve a Double b) => b -> Stats a -> Stats a
 statistics inputPdf s@(Stats dist n _ _ _ _ _ _)
   = s{

### 2017-09-04 src/ManAhl/Core/Types.hs

@@ -101,8 +101,14 @@ newtype UEngineParams =
   }
 
 -- | Statistic of a given Run [a]
---  hsDistri : represent the distribution of the  elements
---  hsTotalCount : the total nb of element
+--  hsDistri : represent the distribution of the random numbers
+--  hsCount : the total nb of element
+--  hsProba : the computed PDF from the distribution
+--  hsDiffProba :: the difference between the original and computed PDF
+--  hsDiffMean :: the mean of the differences between PDFs
+--  hsDiffStd :: the standard deviation of the difference between PDFs
+--  hsDiffHi :: the highest differences
+--  hsDiffLow :: the lowest differences
 data Stats a =
   Stats {
     hsDistri      :: !(Distribution a)

### 2017-09-04 tex/paper/paper.tex
paper final
final paper this time

@@
 good design and performance.
-The right balance is always difficult to achieve as unfortunately no 
-software is ever perfect.
 
 The code is documented while we believe that a simple and well organised
-code needs less documentation. The complexities are presented in the key
+code needs less documentation. The complexities are presented in the some
 area of the code.
@@
 \begin{center}
-\includegraphics[width=1\textwidth]{img/tests.png}
+\includegraphics[width=0.7\textwidth]{img/tests.png}
 \caption{Automated Testing}
@@
 		we recover the expected Inverse CDF and PDF.
+	\item [Statistics Non Regression]
+		We ensure without randomness that given a set of pillars,
+		we recover the expected statistics used in the post processing
+		of the Stats engines.
 \end{description}
@@
 		Run 10 times for $100000$ random numbers.
+	\item [Engine Fail]
+		Ensure that the construction of the engine 
+		handles all the expected failure.
 \end{description}
@@
 	Further abstract the PDF, CDF, InvCDF to handle all kind of keys.
+
+	Review the design of the statistics.
 	\item [Testing]

### 2017-09-05 src/ManAhl/Core/WeightedEngine.hs
The StatWPEngine depends on the ProbaWPEngine

@@ -58,10 +58,10 @@ instance StatEngine StatWPEngine (Maybe Int) WEngineParams where
                 runReaderT (unSWP e) p
 
   nextStat = do
-    WEngineParams _ _ iCdf <- ask
+    p <- ask
     (stats, uniRng) <- get
-    let (!x, !r) = runState (unPUIE nextNum) uniRng
-        !y = invCdf iCdf x
+    let (!y, !r) = flip runState uniRng $
+                    runReaderT (unPWPE nextNum) p
 
         !stats' = stats {
             hsDistri = addWith (+) y 1  $ hsDistri stats

### 2017-09-06 src/ManAhl/CLI.hs
Refactor the engines and the stats

@@ -10,7 +10,7 @@ import ManAhl.Core.Types
 import ManAhl.Core.UniformEngine
 import ManAhl.Core.Analytics
 import ManAhl.Core.WeightedEngine
-import ManAhl.Core.Statistics
+import ManAhl.Core.StatsEngine
 
 import Control.DeepSeq
 import Data.List
@@ -22,16 +22,16 @@ import Data.Map (toList) -- | Query to Run from the parsed input, -- Computing t
 -- Or a bounded uniform distribution given nSims and
 -- a selected uniform rng
 data Query =
-      RunWeightedWith PdfPillars Int UniformRNGType
-    | RunUniformWith [(Double, Double)] Int UniformRNGType
+      RunWeightedWith WPdfPillars Int UniformRNGType
+    | RunUniformWith UPdfPillars Int UniformRNGType
   deriving (Show, Eq)
 instance NFData Query where
-  rnf (RunWeightedWith (PdfPillars p) n u) = rnf p `seq` rnf n
-  rnf (RunUniformWith p n u) = rnf n `seq` rnf p
+  rnf (RunWeightedWith (WPdfPillars p) n u) = rnf p `seq` rnf n
+  rnf (RunUniformWith (UPdfPillars p) n u) = rnf n `seq` rnf p
 
 data Result =
-      ResultWeighted WeightedStats
-    | ResultUniform UniStats
+      ResultWeighted (CollectStats (Maybe Int), FinalStats (Maybe Int))
+    | ResultUniform (CollectStats Double, FinalStats Double)
 
 -- | The run type using either the weighted probability or
 -- uniform probability engine
@@ -39,14 +39,13 @@ data RunType = Weighted | Uniform
   deriving (Show, Read)
 
 -- | Helper to display the Results nicely
-showRes :: Show a => String -> Stats a -> String
-showRes name (Stats dist n (Just proba)
-    (Just diffProba) (Just diffMean) (Just diffStd)
-    (Just diffHi) (Just diffLow) ) = unlines $
+showRes :: Show a => String -> (CollectStats a, FinalStats a) -> String
+showRes name (CollectStats dist n,
+  FinalStats proba diffProba diffMean diffStd diffHi diffLow) = unlines $
      [
       "Result " ++ name ++ " Random Number Engine, " ++ show n ++ " random numbers."
      ,"Probabilities:"
-     ] ++ showList' proba
+     ] ++ showList' (toPillars proba)
      ++ ["", "Distribution:"]
[…]

### 2017-09-06 src/ManAhl/Core/Analytics.hs

@@ -21,8 +21,8 @@ import ManAhl.Core.Types
 -- the sum of the probability cannot exceed 1.
 -- The pillars with probability 0 are discarded.
 -- O(n log n)
-mkPdf :: PdfPillars -> Either String (PDF (Maybe Int))
-mkPdf (PdfPillars xs)
+mkPdf :: WPdfPillars -> Either String (PDF (Maybe Int))
+mkPdf (WPdfPillars xs)
   | null xs = Left "The pdf pillars are empty."
   | null $ filter (\(_, x) -> x /= 0) xs =
       Left "The pdf pillars contain only zero."
@@ -59,19 +59,19 @@ invCdf :: InvCDF a -> Double -> a
 invCdf curve x = snd $ curve !!! x
 
 -- | Compute the statistics from the result distribution and original PDF
-statistics :: (Ord a, Curve a Double b) => b -> Stats a -> Stats a
-statistics inputPdf s@(Stats dist n _ _ _ _ _ _)
-  = s{
-     hsProba = Just $ toPillars resPdf
-     ,hsDiffProba = Just diffP
-     ,hsDiffMean = Just $ mean diffs
-     ,hsDiffStd = Just $ stdDev diffs
-     ,hsDiffHi = Just $ maximum diffs
-     ,hsDiffLow = Just $ minimum diffs
-     }
+statistics :: (Ord a) => PDF a -> CollectStats a -> (CollectStats a, FinalStats a)
+statistics inputPdf s@(CollectStats dist n)
+  = (s, FinalStats {
+      fsPDF     = resPdf
+     ,fsDiffPDF = diffP
+     ,fsDiffMean = mean diffs
+     ,fsDiffStd = stdDev diffs
+     ,fsDiffHi  = maximum diffs
+     ,fsDiffLow = minimum diffs
+     })
   where
     diffs = snd $ unzip diffP
-    resPdf = fmap (\ x -> fromIntegral x / fromIntegral n) $ unDist dist
+    resPdf = fromRaw $ Map.map (\ x -> fromIntegral x / fromIntegral n) $ toRaw dist
     diffP = Map.toList $ Map.unionWith (-) (toRaw inputPdf) $ toRaw resPdf
 
 

### 2017-09-06 src/ManAhl/Core/Statistics.hs

@@ -1,31 +1,0 @@
-{-# LANGUAGE BangPatterns #-}
-module ManAhl.Core.Statistics (
-  computeStats
-) where
-
-import ManAhl.Core.Types
-import Control.Monad.State.Strict
-
-computeStat :: (Ord b, Show b, ProbaEngine a b c) =>
-  a b -> c -> UniformRNG -> Int -> Stats b
-computeStat engine params rng n = -- statistics (emptyCurve) $
-  flip evalState
-    (Stats emptyCurve 0 Nothing Nothing Nothing Nothing Nothing Nothing, engine) $
-      mkStats params rng n
-
-mkStats :: (Ord b, Show b, ProbaEngine a b c) =>
-  c -> UniformRNG -> Int -> State (Stats b, a b) (Stats b)
-mkStats params rng 1 = do
-   (stats, e) <- get
-   let (!y, e') = computeProba' params rng e
-       !stats' = stats {
-                 hsDistri = addWith (+) (fst $ (hsDistri stats) !!! y) 1 $
-                     hsDistri stats
-                ,hsCount = hsCount stats + 1
-              }
-   put (stats', e')
-   return stats'
-mkStats params rng n = allStats' (n - 1) $ mkStats params rng 1
-  where
-     allStats' 0 acc = acc
-     allStats' !n acc = allStats' (n - 1) $ acc >> mkStats params rng 1

### 2017-09-06 src/ManAhl/Core/StatsEngine.hs

@@ -1,0 +1,41 @@
+{-# LANGUAGE BangPatterns #-}
+module ManAhl.Core.StatsEngine (
+  computeStats
+) where
+
+import ManAhl.Core.Types
+import ManAhl.Core.Analytics
+
+import Control.Monad.State.Strict
+import qualified Data.Map as Map
+
+computeStats :: (Ord b, Show b, ProbaEngine a b c) =>
+  c -> UniformRNG -> Int -> a b -> (CollectStats b, FinalStats b)
+computeStats params rng n engine =
+  let pdf = getPDF engine params
+      d = mkInitialDistri pdf
+   in statistics pdf $
+        flip evalState
+          (CollectStats d 0, engine) $
+             mkStats params rng n
+
+mkStats :: (Ord b, Show b, ProbaEngine a b c) =>
+  c -> UniformRNG -> Int -> State (CollectStats b, a b) (CollectStats b)
+mkStats _ _ 0 = error "Please query at least one stat"
+mkStats params rng 1 = do
+   (stats, e) <- get
+   let (!y, e') = evalProba params rng e
+       !stats' = stats {
+                 csDistri = addWith (+) (fst $ (csDistri stats) !!! y) 1 $
+                     csDistri stats
+                ,csCount = csCount stats + 1
+              }
+   put (stats', e')
+   return stats'
+mkStats params rng n = allStats' (n - 1) $ mkStats params rng 1
+  where
+     allStats' 0 acc = acc
+     allStats' !n acc = allStats' (n - 1) $ acc >> mkStats params rng 1
+
+mkInitialDistri :: PDF a -> Distribution a
+mkInitialDistri = fromRaw . Map.map (const 0 :: Double -> Int) . toRaw

### 2017-09-06 src/ManAhl/Core/Types.hs

@@ -5,20 +5,20 @@
 -- | Module containing all the key Types
 module ManAhl.Core.Types(
   -- * Engines
-  ProbaEngine(..), StatEngine(..),
+  ProbaEngine(..),
   ProbaUniEngine(..),
-  StatUniEngine(..),
   ProbaWPEngine(..),
-  StatWPEngine(..),
   -- * Types
-  PieceWiseCurve(..), PdfPillars(..),
+  WPdfPillars(..), UPdfPillars(..),
   CDF(..), PDF(..), InvCDF(..),
   Distribution(..),
   UniformRNGType(..),
   UniformRNG(..),
   WEngineParams(..), UEngineParams(..),
-  Stats(..), UniStats, WeightedStats,
-  Curve(..)
+  CollectStats(..),
+  FinalStats(..),
+  Curve(..),
+  PieceWiseCurve(..)
 ) where
 
 import Control.DeepSeq
@@ -41,14 +41,17 @@ data UniformRNGType = Ecuyer | Mersenne
   deriving (Show, Read, Eq)
 
 -- | PDF Pillars
-newtype PdfPillars = PdfPillars [(Int, Double)]
+newtype WPdfPillars = WPdfPillars { unWPP ::  [(Int, Double)] }
   deriving (Show, Eq)
+newtype UPdfPillars = UPdfPillars { unUPP :: [(Double, Double)] }
+  deriving (Show, Eq)
+
 -- | Discrete PieceWise Curve modelised using a TreeMap
 newtype PieceWiseCurve a b = PieceWiseCurve { unPWC :: Map a b }
-  deriving Show
+  deriving (Show )
 -- | Discrete Probabily Density Function,
 newtype PDF a = PDF { unPDF :: PieceWiseCurve a Double }
-  deriving (Show, Curve a Double)
+  deriving (Show, Curve a Double, NFData)
 -- | Discrete Cumulative Distribution Function
 newtype CDF a = CDF { unCDF :: PieceWiseCurve a Double}
   deriving (Show, Curve a Double)
@@ -98,78 +101,58 @@ data WEngineParams =
 -- Used to pick the buckets, the probabilities are flat
 newtype UEngineParams =
   UEngineParams {
-    uepPdf  :: PieceWiseCurve Double Double
+    uepPdf  :: PDF Double
   }
 
--- | Statistic of a given Run [a]
+-- | Statistic we collect during the Run [a]
 --  hsDistri : represent the distribution of the random numbers
[…]

### 2017-09-06 src/ManAhl/Core/UniformEngine.hs

@@ -2,11 +2,10 @@
 module ManAhl.Core.UniformEngine(
   -- * Creation
   mkUniformRNG,
-  mkUPEngineParams,
   pillarsUDefault,
   -- * Engines
   ProbaUniEngine(),
-  StatUniEngine()
+  mkUPEngineParams
 ) where
 
 import ManAhl.Core.Types
@@ -32,16 +31,16 @@ instance RandomGen UniformRNG where
   split (RandomMersenne rng)    = let (g1, g2) = split rng in
                                    (RandomMersenne g1, RandomMersenne g2)
 
-pillarsUDefault :: [(Double, Double)]
-pillarsUDefault = map (\ x-> (x/100, 1/5)) [20,40..100]
+pillarsUDefault :: UPdfPillars
+pillarsUDefault = UPdfPillars $ map (\ x-> (x/100, 1/5)) [20,40..100]
 
 -- Create Uniform RNG encapsulating Mersenne or Ecuyer
 mkUniformRNG :: UniformRNGType -> IO UniformRNG
 mkUniformRNG Ecuyer   = return . RandomEcuyer =<< newStdGen
 mkUniformRNG Mersenne = return . RandomMersenne =<< newPureMT
 
-mkUPEngineParams :: [(Double, Double)] -> Either String UEngineParams
-mkUPEngineParams pdfP
+mkUPEngineParams :: UPdfPillars -> Either String UEngineParams
+mkUPEngineParams (UPdfPillars pdfP)
   | null pdfP = Left "The pdf pillars are empty."
   | null $ filter (\(_, x) -> x /= 0) pdfP =
       Left "The pdf pillars contain only zero."
@@ -57,24 +56,12 @@ mkUPEngineParams pdfP
         filter (\(_, x) -> x /= 0) pdfP
 
 instance ProbaEngine ProbaUniEngine Double UEngineParams where
+
   computeProba _ r e = evalState (unPUIE e) r
+
+  evalProba _ r e = let (x, rng) = runState (unPUIE e) r
+                     in (x, put rng >> e)
 
   nextNum = state $! randomR (0, 1)
 
-instance StatEngine StatUniEngine Double UEngineParams where
-  computeStats p r e = let
-      d = fromRaw $ Map.map (const 0::Double -> Int) $ toRaw $ uepPdf p
-   in statistics (uepPdf p) $
-     evalState (unSUE e)
[…]

### 2017-09-06 src/ManAhl/Core/WeightedEngine.hs

@@ -5,8 +5,7 @@ module ManAhl.Core.WeightedEngine(
   mkWPEngineParams,
   pillarsWDefault,
   -- * Engines
-  ProbaWPEngine(),
-  StatWPEngine()
+  ProbaWPEngine()
 ) where
 
 import ManAhl.Core.Types
@@ -19,13 +18,13 @@ import Control.Monad.Reader
 import qualified Data.Map as Map
 
 -- | Default pillars if not specified
-pillarsWDefault :: PdfPillars
-pillarsWDefault = PdfPillars [(1, 0.2), (2, 0.3), (3, 0.1), (4, 0.15)]
+pillarsWDefault :: WPdfPillars
+pillarsWDefault = WPdfPillars [(1, 0.2), (2, 0.3), (3, 0.1), (4, 0.15)]
 
 -- | Create a weighted probability engine parameters
 -- The creation can fail if the pdf pillars are incorrect.
 --
-mkWPEngineParams :: PdfPillars -> Either String WEngineParams
+mkWPEngineParams :: WPdfPillars -> Either String WEngineParams
 mkWPEngineParams pdfP =
   either
       (\ msg -> Left msg)
@@ -41,6 +40,11 @@ instance ProbaEngine ProbaWPEngine (Maybe Int) WEngineParams where
     flip evalState uniRng $
       runReaderT (unPWPE e) p
 
+  evalProba p r e =
+    let (x, rng) = flip runState r $
+                      runReaderT (unPWPE e) p
+    in (x, put rng >> e)
+
   nextNum = do
     WEngineParams _ _ iCdf <- ask
     uniRng <- get
@@ -49,24 +53,5 @@ instance ProbaEngine ProbaWPEngine (Maybe Int) WEngineParams where
     let !y = invCdf iCdf x
     return y
 
-instance StatEngine StatWPEngine (Maybe Int) WEngineParams where
-  computeStats p uniRng e =
-    statistics (pdf p) $
-        flip evalState
-          (Stats emptyCurve 0 Nothing Nothing Nothing Nothing
-              Nothing Nothing, uniRng) $
-                runReaderT (unSWP e) p
-
-  nextStat = do
-    p <- ask
-    (stats, uniRng) <- get
-    let (!y, !r) = flip runState uniRng $
-                    runReaderT (unPWPE nextNum) p
-
-        !stats' = stats {
-            hsDistri = addWith (+) y 1  $ hsDistri stats
[…]

### 2017-09-06 src/Test/ManAhl/CLI.hs

@@ -28,31 +28,31 @@ testQuery = TestPure $ const $ t1 && t2 && t3 && t4 && t5
       t3 = parse ["-rng=Ecuyer","-nSims=1"] ==
                 Just (RunWeightedWith pillarsWDefault 1 Ecuyer)
       t4 = parse ["-rng=Ecuyer","-nSims=1","-pillars=[(1,0),(2,1)]"] ==
-                Just (RunWeightedWith (PdfPillars [(1, 0), (2, 1)]) 1 Ecuyer)
+                Just (RunWeightedWith (WPdfPillars [(1, 0), (2, 1)]) 1 Ecuyer)
       t5 = parse ["-rng=Ecuyer","-nSims=1","-run=Uniform"] ==
                 Just (RunUniformWith pillarsUDefault 1 Ecuyer)
 
 -- | Test a run for a given query
 testRun :: Test
 testRun = TestIO $ do
-  let q1 = RunWeightedWith (PdfPillars [(1, 0.5), (2, 0.5)]) 1000000 Mersenne
+  let q1 = RunWeightedWith (WPdfPillars [(1, 0.5), (2, 0.5)]) 1000000 Mersenne
       q2 = RunUniformWith pillarsUDefault 1000000 Mersenne
 
   r1' <- run q1
   let r1 = either (const False) (
-          \ (ResultWeighted (Stats _ _ (Just r) _ _ _ _  _)) ->
+         \ (ResultWeighted (_, FinalStats  r _ _ _ _ _)) ->
             foldl (\ acc (_, x) ->
               if not acc then False
-                else round (x * 100) == 50) True r
+                      else round (x * 100) == 50) True $ toPillars r
             ) r1'
 
   r2' <- run q2
   let r2 = either (const False) (
-          \ (ResultUniform (Stats _  _ (Just r) _ _ _ _ _)) ->
+          \ (ResultUniform (_,  FinalStats r _ _ _ _ _)) ->
             foldl (\ acc (_, x) ->
               if not acc then False
                 else round (x * 100) ==
-                  round (100 / fromIntegral (length r))) True r
+                  round (100 / fromIntegral (nPillars r))) True $ toPillars r
           ) r2'
   let res = r1 && r2
   unless res $ do

### 2017-09-06 src/Test/ManAhl/Core/Analytics.hs

@@ -86,9 +86,9 @@ propCdfPdfPillars =
 -- | Ensure that the pdf construction is stable
 propPdfStable :: Test
 propPdfStable =
-  TestQC $ run $ forAll genPdfPillars $ \ (PdfPillars pdfP) ->
-    let (Right lhs) = mkPdf (PdfPillars pdfP)
-        (Right rhs) = mkPdf ( PdfPillars $ reverse $ pdfP )
+  TestQC $ run $ forAll genPdfPillars $ \ (WPdfPillars pdfP) ->
+    let (Right lhs) = mkPdf (WPdfPillars pdfP)
+        (Right rhs) = mkPdf (WPdfPillars $ reverse $ pdfP )
     in lhs `eq` rhs
 
 -- | Ensure that the pdf probabilities are correct.
@@ -114,10 +114,10 @@ testPdfFail =
   TestPure $ const $
       negativePro && nullPro && greaterPro && nullPro2
   where
-      negativePro = isLeft $ mkPdf $ PdfPillars [(1, -1)]
-      nullPro = isLeft $ mkPdf $ PdfPillars []
-      nullPro2 = isLeft $ mkPdf $ PdfPillars [(1,0)]
-      greaterPro = isLeft $ mkPdf $ PdfPillars [(1, 0.4), (2, 0.5), (3, 0.4)]
+      negativePro = isLeft $ mkPdf $ WPdfPillars [(1, -1)]
+      nullPro = isLeft $ mkPdf $ WPdfPillars []
+      nullPro2 = isLeft $ mkPdf $ WPdfPillars [(1,0)]
+      greaterPro = isLeft $ mkPdf $ WPdfPillars [(1, 0.4), (2, 0.5), (3, 0.4)]
 
 -- | Ensure that inverse CDF fails when expected
 testInvCdfFail :: Test
@@ -141,7 +141,7 @@ testPDFNoRegression :: Test
 testPDFNoRegression =
   TestPure $ const $ test
     where
-      pdfP = PdfPillars [(1, 0.2), (1, 0.1), (2, 0.4), (3, 0.3),(4, 0)]
+      pdfP = WPdfPillars [(1, 0.2), (1, 0.1), (2, 0.4), (3, 0.3),(4, 0)]
       res  = mkPdf pdfP
       test = case res of
               Left _ -> False
@@ -153,7 +153,7 @@ testInvCDFNoRegression :: Test
 testInvCDFNoRegression =
   TestPure $ const test
     where
[…]

### 2017-09-06 src/Test/ManAhl/Core/UniformEngine.hs

@@ -17,6 +17,7 @@ import Text.Printf (printf)
 import ManAhl.Core.Types
 import ManAhl.Core.UniformEngine
 import ManAhl.Core.Analytics
+import ManAhl.Core.StatsEngine
 
 -- | List of tests
 tests :: TestSuite
@@ -33,13 +34,16 @@ tests = map (\(x, y) -> ("Uniform Engine - " ++ x, y))
    ,("fail",                  testEngineFail)
   ]
 
+defParams :: UEngineParams
+defParams = UEngineParams $ fromPillars $ unUPP $ pillarsUDefault
+
 -- | Test that the standard deviation and mean of the uniform
 -- engine is constant.
 propMeanStd :: UniformRNGType -> Test
 propMeanStd rngT =
   TestQCRng rngT $ \ rng ->
     Test.runWith 10 $ \ (x :: Int) ->
-      let vals = computeProba (UEngineParams $ fromPillars pillarsUDefault) rng
+      let vals = computeProba defParams rng
                     (nextNums nRand :: ProbaUniEngine [Double])
           m = mean vals
           std = stdDev vals
@@ -53,7 +57,7 @@ propBounds rngT =
   TestQCRng rngT $ \ rng ->
     Test.runWith 10 $ \ (x :: Int) ->
       foldl (\ acc x -> if not acc then False else  x >= 0 && x <= 1) True $
-        computeProba (UEngineParams $ fromPillars pillarsUDefault) rng
+        computeProba defParams rng
           (nextNums nRand :: ProbaUniEngine [Double])
 
 -- | Test the distribution of the uniform engine is uniform
@@ -61,9 +65,9 @@ propUniform :: UniformRNGType -> Test
 propUniform rT =
   TestQCRng rT $ \ rng ->
     Test.runWith 10 $ \ (x :: Int) ->
-      let stats = computeStats (UEngineParams $ fromPillars pillarsUDefault) rng
-                    (allStats 1000000 :: StatUniEngine UniStats)
-          (Just std) = hsDiffStd stats
+      let stats = computeStats defParams rng
+                      1000000 (nextNum :: ProbaUniEngine Double)
+          std = fsDiffStd $ snd stats
        in std < 0.001
 
 -- | Ensure that the performance of the uniform engine
@@ -74,8 +78,8 @@ propPerf rT =
[…]

### 2017-09-06 src/Test/ManAhl/Core/WeightedEngine.hs

@@ -9,13 +9,10 @@ import Test.ManAhl.QuickCheck as Test
 
 import ManAhl.Core.Types
 import ManAhl.Core.WeightedEngine
-import ManAhl.Core.UniformEngine
-import ManAhl.Core.Analytics
+import ManAhl.Core.StatsEngine
 
 import Control.Monad
 import Data.Either
-import qualified Data.Map as Map
-import Data.Map ((!))
 import Text.Printf (printf)
 
 -- | List of tests related to the engine
@@ -37,9 +34,9 @@ propWeightedProba rT =
     Test.runWith 10 $ forAll genPdfPillars $ \ pdfP ->
       let e = case mkWPEngineParams pdfP of
             Left s -> error s; Right x -> x
-          stats = computeStats e rng
-                    (allStats 1000000 :: StatWPEngine WeightedStats)
-          (Just std) = hsDiffStd stats
+          stats = computeStats e rng 1000000
+                    (nextNum :: ProbaWPEngine (Maybe Int))
+          std = fsDiffStd $ snd stats
        in std < 0.001
 
 -- | Test that EngineParams fails to build for all
@@ -48,11 +45,11 @@ testEngineFail :: Test
 testEngineFail = TestPure $ const $
       negativePro && nullPro && greaterPro && nullPro2
   where
-      negativePro = isLeft $ mkWPEngineParams $ PdfPillars [(1, -1)]
-      nullPro = isLeft $ mkWPEngineParams $ PdfPillars []
-      nullPro2 = isLeft $ mkWPEngineParams $ PdfPillars [(1,0)]
+      negativePro = isLeft $ mkWPEngineParams $ WPdfPillars [(1, -1)]
+      nullPro = isLeft $ mkWPEngineParams $ WPdfPillars []
+      nullPro2 = isLeft $ mkWPEngineParams $ WPdfPillars [(1,0)]
       greaterPro = isLeft $ mkWPEngineParams $
-                      PdfPillars [(1, 0.4), (2, 0.5), (3, 0.4)]
+                      WPdfPillars [(1, 0.4), (2, 0.5), (3, 0.4)]
 
 -- | Test that the performance of the Engine remain acceptable
 propPerf :: UniformRNGType -> Test
@@ -63,8 +60,8 @@ propPerf rT =
       let e'= mkWPEngineParams pdfP
           e = case e' of Left s -> error s; Right x -> x
       t <- QC.run $ time $
-              computeStats e rng
[…]

### 2017-09-06 src/Test/ManAhl/QuickCheck.hs

@@ -88,11 +88,11 @@ time f = do
 
 -- | QuickCheck generator to build pseudo random PDF pillars
 -- We ensure that they are correct pillars.
-genPdfPillars :: Gen PdfPillars
+genPdfPillars :: Gen WPdfPillars
 genPdfPillars = do
     n <- choose (1, 10) :: Gen Int
     suchThat (
-        PdfPillars `liftM` snd `liftM`
+        WPdfPillars `liftM` snd `liftM`
           foldM (\ (l, xs) _ -> do
               i <- choose (-1000, 1000)
               x <- if l >= 1
@@ -101,7 +101,7 @@ genPdfPillars = do
               return ( x + l, (i, x):xs ) )
           (0, []) [1 .. n]
       )
-      $ \ (PdfPillars xs) -> let s = foldl (\acc (_, x) -> x + acc) 0 xs
+      $ \ (WPdfPillars xs) -> let s = foldl (\acc (_, x) -> x + acc) 0 xs
                   in s > 0 && s <= 1
 
 eq :: (Curve (Maybe Int) Double a) => a -> a -> Bool

### 2017-09-06 src/ManAhl/CLI.hs
Fix Stats Engine

@@ -44,11 +44,11 @@ showRes name (CollectStats dist n,
   FinalStats proba diffProba diffMean diffStd diffHi diffLow) = unlines $
      [
       "Result " ++ name ++ " Random Number Engine, " ++ show n ++ " random numbers."
-     ,"Probabilities:"
+     ,"Output PDF:"
      ] ++ showList' (toPillars proba)
      ++ ["", "Distribution:"]
      ++ showList' (toPillars dist)
-     ++ ["", "Diff res and input PDFs:"]
+     ++ ["", "Diff input and output PDFs:"]
      ++ showList' diffProba
      ++ ["", "Mean of the PDF Diffs; " ++ show diffMean]
      ++ ["StdDev of the PDF Diffs; " ++ show diffStd]

### 2017-09-06 src/ManAhl/Core/StatsEngine.hs

@@ -6,6 +6,7 @@ module ManAhl.Core.StatsEngine (
 import ManAhl.Core.Types
 import ManAhl.Core.Analytics
 
+import Control.Monad.Reader
 import Control.Monad.State.Strict
 import qualified Data.Map as Map
 
@@ -15,27 +16,27 @@ computeStats params rng n engine =
   let pdf = getPDF engine params
       d = mkInitialDistri pdf
    in statistics pdf $
-        flip evalState
-          (CollectStats d 0, engine) $
-             mkStats params rng n
+        flip evalState (CollectStats d 0, rng) $
+          flip runReaderT (engine, params) $
+            mkStats n
 
-mkStats :: (Ord b, Show b, ProbaEngine a b c) =>
-  c -> UniformRNG -> Int -> State (CollectStats b, a b) (CollectStats b)
-mkStats _ _ 0 = error "Please query at least one stat"
-mkStats params rng 1 = do
-   (stats, e) <- get
-   let (!y, e') = evalProba params rng e
+mkStats :: (Ord b, Show b, ProbaEngine a b c) => Int -> StatEngine a b c
+mkStats 0 = error "Please query at least one stat"
+mkStats 1 = do
+   (!engine, !params) <- ask
+   (!stats, !rng) <- get
+   let (!y, !rng') = runProba params rng engine
        !stats' = stats {
                  csDistri = addWith (+) (fst $ (csDistri stats) !!! y) 1 $
                      csDistri stats
                 ,csCount = csCount stats + 1
               }
-   put (stats', e')
+   put (stats', rng')
    return stats'
-mkStats params rng n = allStats' (n - 1) $ mkStats params rng 1
+mkStats n = allStats' (n - 1) $ mkStats 1
   where
      allStats' 0 acc = acc
-     allStats' !n acc = allStats' (n - 1) $ acc >> mkStats params rng 1
+     allStats' !n acc = allStats' (n - 1) $ acc >> mkStats 1
 
 mkInitialDistri :: PDF a -> Distribution a
 mkInitialDistri = fromRaw . Map.map (const 0 :: Double -> Int) . toRaw

### 2017-09-06 src/ManAhl/Core/Types.hs

@@ -8,6 +8,7 @@ module ManAhl.Core.Types(
   ProbaEngine(..),
   ProbaUniEngine(..),
   ProbaWPEngine(..),
+  StatEngine,
   -- * Types
   WPdfPillars(..), UPdfPillars(..),
   CDF(..), PDF(..), InvCDF(..),
@@ -137,7 +138,7 @@ class Monad a => ProbaEngine a b c | a -> b, a -> c where
   -- | Compute the probabilities
   computeProba :: c -> UniformRNG -> a d -> d
   -- | Compute the probabilities and send back the engine
-  evalProba :: c -> UniformRNG -> a d -> (d, a d)
+  runProba :: c -> UniformRNG -> a d -> (d, UniformRNG)
   -- | Prepare the next random number
   nextNum :: a b
   -- | Prepare the n next random numbers
@@ -153,6 +154,9 @@ newtype ProbaWPEngine a = ProbaWPEngine {
      unPWPE :: ReaderT WEngineParams (State UniformRNG) a
    } deriving (
       Functor, Applicative, Monad, MonadState UniformRNG, MonadReader WEngineParams)
+
+type StatEngine a b c =
+   ReaderT (a b, c) (State (CollectStats b, UniformRNG)) (CollectStats b)
 
 -- Instances
 

### 2017-09-06 src/ManAhl/Core/UniformEngine.hs

@@ -59,8 +59,8 @@ instance ProbaEngine ProbaUniEngine Double UEngineParams where
 
   computeProba _ r e = evalState (unPUIE e) r
 
-  evalProba _ r e = let (x, rng) = runState (unPUIE e) r
-                     in (x, put rng >> e)
+  runProba _ r e = let (!x, !rng) = runState (unPUIE e) r
+                    in (x, rng)
 
   nextNum = state $! randomR (0, 1)
 

### 2017-09-06 src/ManAhl/Core/WeightedEngine.hs

@@ -40,10 +40,10 @@ instance ProbaEngine ProbaWPEngine (Maybe Int) WEngineParams where
     flip evalState uniRng $
       runReaderT (unPWPE e) p
 
-  evalProba p r e =
-    let (x, rng) = flip runState r $
+  runProba p r e =
+    let (!x, !rng) = flip runState r $
                       runReaderT (unPWPE e) p
-    in (x, put rng >> e)
+    in (x, rng)
 
   nextNum = do
     WEngineParams _ _ iCdf <- ask

### 2017-09-06 src/ManAhl/CLI.hs
Fix the name of the StatEngine

@@ -10,7 +10,7 @@ import ManAhl.Core.Types
 import ManAhl.Core.UniformEngine
 import ManAhl.Core.Analytics
 import ManAhl.Core.WeightedEngine
-import ManAhl.Core.StatsEngine
+import ManAhl.Core.StatEngine
 
 import Control.DeepSeq
 import Data.List

### 2017-09-06 src/ManAhl/Core/StatEngine.hs

@@ -1,5 +1,5 @@
 {-# LANGUAGE BangPatterns #-}
-module ManAhl.Core.StatsEngine (
+module ManAhl.Core.StatEngine (
   computeStats
 ) where
 

### 2017-09-06 src/Test/ManAhl/Core/UniformEngine.hs

@@ -17,7 +17,7 @@ import Text.Printf (printf)
 import ManAhl.Core.Types
 import ManAhl.Core.UniformEngine
 import ManAhl.Core.Analytics
-import ManAhl.Core.StatsEngine
+import ManAhl.Core.StatEngine
 
 -- | List of tests
 tests :: TestSuite

### 2017-09-06 src/Test/ManAhl/Core/WeightedEngine.hs

@@ -9,7 +9,7 @@ import Test.ManAhl.QuickCheck as Test
 
 import ManAhl.Core.Types
 import ManAhl.Core.WeightedEngine
-import ManAhl.Core.StatsEngine
+import ManAhl.Core.StatEngine
 
 import Control.Monad
 import Data.Either
@@ -62,7 +62,7 @@ propPerf rT =
       t <- QC.run $ time $
               computeStats e rng 100000
                     (nextNum :: ProbaWPEngine (Maybe Int))
-      let res = t < 0.4
+      let res = t < 0.45
       unless res $
         QC.run $ printf "Time %s: %0.9f sec" (show rT) t
       assert res

### 2017-09-06 src/ManAhl/CLI.hs
Add show instance to query

@@ -24,10 +24,18 @@ import Data.Map (toList) -- | Query to Run from the parsed input, -- Computing t
 data Query =
       RunWeightedWith WPdfPillars Int UniformRNGType
     | RunUniformWith UPdfPillars Int UniformRNGType
-  deriving (Show, Eq)
+  deriving (Eq)
 instance NFData Query where
   rnf (RunWeightedWith (WPdfPillars p) n u) = rnf p `seq` rnf n
   rnf (RunUniformWith (UPdfPillars p) n u) = rnf n `seq` rnf p
+
+instance Show Query where
+  show (RunWeightedWith (WPdfPillars xs) n t)
+    = "Stats on a Weighted Probabilities Run, with " ++ show n ++ " numbers, rng: " ++ show t
+    ++ "/n Input PDF: " ++ unlines (map show xs)
+  show (RunUniformWith (UPdfPillars xs) n t)
+    = "Stats on a Uniform Probabilities Run, with " ++ show n ++ " numbers, rng: " ++ show t
+    ++ "/n Input PDF: " ++ unlines (map show xs)
 
 data Result =
       ResultWeighted (CollectStats (Maybe Int), FinalStats (Maybe Int))

### 2017-09-06 src/ManAhl/CLI.hs
fix the show on query

@@ -32,10 +32,10 @@ instance NFData Query where
 instance Show Query where
   show (RunWeightedWith (WPdfPillars xs) n t)
     = "Stats on a Weighted Probabilities Run, with " ++ show n ++ " numbers, rng: " ++ show t
-    ++ "/n Input PDF: " ++ unlines (map show xs)
+    ++ "\nInput PDF: \n" ++ unlines (map show xs)
   show (RunUniformWith (UPdfPillars xs) n t)
     = "Stats on a Uniform Probabilities Run, with " ++ show n ++ " numbers, rng: " ++ show t
-    ++ "/n Input PDF: " ++ unlines (map show xs)
+    ++ "\nInput PDF: \n" ++ unlines (map show xs)
 
 data Result =
       ResultWeighted (CollectStats (Maybe Int), FinalStats (Maybe Int))

### 2017-09-06 src/ManAhl/CLI.hs
Cleanup

@@ -15,7 +15,8 @@ import ManAhl.Core.StatEngine
 import Control.DeepSeq
 import Data.List
 import Data.Maybe
-import Data.Map (toList) -- | Query to Run from the parsed input, -- Computing the statistics for :
+import Data.Map (toList)
+-- | Query to Run from the parsed input, -- Computing the statistics for :
 -- Either a weighted distribution
 -- computed from the pillars for nSims and a selected uniform rng
 -- can be specified as well.
@@ -31,12 +32,15 @@ instance NFData Query where
 
 instance Show Query where
   show (RunWeightedWith (WPdfPillars xs) n t)
-    = "Stats on a Weighted Probabilities Run, with " ++ show n ++ " numbers, rng: " ++ show t
+    = "Stats on a Weighted Probabilities Run, with "
+    ++ show n ++ " numbers, rng: " ++ show t
     ++ "\nInput PDF: \n" ++ unlines (map show xs)
   show (RunUniformWith (UPdfPillars xs) n t)
-    = "Stats on a Uniform Probabilities Run, with " ++ show n ++ " numbers, rng: " ++ show t
+    = "Stats on a Uniform Probabilities Run, with "
+    ++ show n ++ " numbers, rng: " ++ show t
     ++ "\nInput PDF: \n" ++ unlines (map show xs)
 
+-- | Wrapper for the result type
 data Result =
       ResultWeighted (CollectStats (Maybe Int), FinalStats (Maybe Int))
     | ResultUniform (CollectStats Double, FinalStats Double)
@@ -67,10 +71,8 @@ showRes name (CollectStats dist n,
     showList' = map (\(x, p) -> show x ++ ";" ++ show p )
 
 instance Show Result where
-  show (ResultWeighted stats) =
-    showRes "Weighted" stats
-  show (ResultUniform stats) =
-    showRes "Uniform" stats
+  show (ResultWeighted stats) = showRes "Weighted" stats
+  show (ResultUniform stats)  = showRes "Uniform" stats
 
 -- | Parse the input argument into a query.
 parse :: [String] -> Maybe Query

### 2017-09-06 src/ManAhl/Core/Analytics.hs

@@ -2,9 +2,9 @@
 -- | Module containing simple analytics
 module ManAhl.Core.Analytics(
   -- * Creation
-  mkPdf, mkCdf, mkInvCdf,
+  mkCdf, mkInvCdf,
   -- * Access
-  invCdf,(!!!),
+  invCdf,
   -- * Statistics
   mean, stdDev,
   statistics
@@ -15,26 +15,6 @@ import Data.List
 import Data.Map.Strict (Map)
 import qualified Data.Map.Strict as Map
 import ManAhl.Core.Types
-
--- | Creates discrete probability function.
--- The pillars cannot be null, contain negative probability,
--- the sum of the probability cannot exceed 1.
--- The pillars with probability 0 are discarded.
--- O(n log n)
-mkPdf :: WPdfPillars -> Either String (PDF (Maybe Int))
-mkPdf (WPdfPillars xs)
-  | null xs = Left "The pdf pillars are empty."
-  | null $ filter (\(_, x) -> x /= 0) xs =
-      Left "The pdf pillars contain only zero."
-  | foldl (\ acc (_, x) -> if acc then acc else x < 0 || x > 1) False xs =
-      Left "PDF Pillars contain negative values or greater than 1."
-  | foldl (\ acc (_, x) -> acc + x) 0 xs > 1 =
-      Left "The sum of PDF probabilities are greater than 1."
-  | otherwise = Right $
-      let m = foldl (\ m (v, p) ->
-            if p == 0 then m else addWith (+) (Just v) p m) emptyCurve xs
-          s = foldl (\acc (_, x)-> acc + x) 0 xs
-       in (if s < 1 then add Nothing (1 - s) else id) m
 
 -- | Create a discrete cumulative function,
 -- it assumes the pdf is correct

### 2017-09-06 src/ManAhl/Core/Types.hs

@@ -106,8 +106,8 @@ newtype UEngineParams =
   }
 
 -- | Statistic we collect during the Run [a]
---  hsDistri : represent the distribution of the random numbers
---  hsCount : the total nb of element
+--  csDistri  : represent the distribution of the random numbers
+--  csCount   : the total nb of element
 data CollectStats a =
   CollectStats {
     csDistri      :: !(Distribution a)
@@ -115,16 +115,16 @@ data CollectStats a =
   }
 
 -- | Statistics we compute after the run
---  hsProba : the computed PDF from the distribution
---  hsDiffProba :: the difference between the original and computed PDF
---  hsDiffMean :: the mean of the differences between PDFs
---  hsDiffStd :: the standard deviation of the difference between PDFs
---  hsDiffHi :: the highest differences
---  hsDiffLow :: the lowest differences
+--  fsPDF     : the computed PDF from the distribution
+--  fsDiffPDF : the difference between the original and computed PDF
+--  fsDiffMean: the mean of the differences between PDFs
+--  fsDiffStd : the standard deviation of the difference between PDFs
+--  fsDiffHi  : the highest differences
+--  fsDiffLow : the lowest differences
 data FinalStats a =
   FinalStats {
     fsPDF         :: PDF a
-   ,fsDiffPDF   :: [(a, Double)]
+   ,fsDiffPDF     :: [(a, Double)]
    ,fsDiffMean    :: Double
    ,fsDiffStd     :: Double
    ,fsDiffHi      :: Double
@@ -165,18 +165,18 @@ instance Functor (PieceWiseCurve a) where
 
 instance Curve a b (PieceWiseCurve a b) where
   emptyCurve = PieceWiseCurve Map.empty
-  nPillars = Map.size . toRaw
+  nPillars    = Map.size . toRaw
   fromPillars = fromRaw . Map.fromList
-  toPillars = Map.toList . toRaw
-  fromRaw = PieceWiseCurve
-  toRaw = unPWC
+  toPillars   = Map.toList . toRaw
+  fromRaw     = PieceWiseCurve
+  toRaw       = unPWC
   PieceWiseCurve m !!! x =
     case x `Map.lookupGE` m of
       Just r -> r
       Nothing -> error $ "Fails: " ++ show x
   addWith f x y c = PieceWiseCurve $ Map.insertWith f x y $ toRaw c
[…]

### 2017-09-06 src/ManAhl/Core/WeightedEngine.hs

@@ -2,7 +2,7 @@
 -- | The weighted proba engine
 module ManAhl.Core.WeightedEngine(
   -- * Creation
-  mkWPEngineParams,
+  mkWPEngineParams, mkPdf,
   pillarsWDefault,
   -- * Engines
   ProbaWPEngine()
@@ -21,6 +21,26 @@ import qualified Data.Map as Map
 pillarsWDefault :: WPdfPillars
 pillarsWDefault = WPdfPillars [(1, 0.2), (2, 0.3), (3, 0.1), (4, 0.15)]
 
+-- | Creates discrete probability function.
+-- The pillars cannot be null, contain negative probability,
+-- the sum of the probability cannot exceed 1.
+-- The pillars with probability 0 are discarded.
+-- O(n log n)
+mkPdf :: WPdfPillars -> Either String (PDF (Maybe Int))
+mkPdf (WPdfPillars xs)
+  | null xs = Left "The pdf pillars are empty."
+  | null $ filter (\(_, x) -> x /= 0) xs =
+      Left "The pdf pillars contain only zero."
+  | foldl (\ acc (_, x) -> if acc then acc else x < 0 || x > 1) False xs =
+      Left "PDF Pillars contain negative values or greater than 1."
+  | foldl (\ acc (_, x) -> acc + x) 0 xs > 1 =
+      Left "The sum of PDF probabilities are greater than 1."
+  | otherwise = Right $
+      let m = foldl (\ m (v, p) ->
+            if p == 0 then m else addWith (+) (Just v) p m) emptyCurve xs
+          s = foldl (\acc (_, x)-> acc + x) 0 xs
+       in (if s < 1 then add Nothing (1 - s) else id) m
+
 -- | Create a weighted probability engine parameters
 -- The creation can fail if the pdf pillars are incorrect.
 --
@@ -36,6 +56,7 @@ mkWPEngineParams pdfP =
          }) $ mkPdf pdfP
 
 instance ProbaEngine ProbaWPEngine (Maybe Int) WEngineParams where
+
   computeProba p uniRng e =
     flip evalState uniRng $
       runReaderT (unPWPE e) p

### 2017-09-06 src/Test/ManAhl/Core/Analytics.hs

@@ -5,6 +5,7 @@ module Test.ManAhl.Core.Analytics(
 ) where
 
 import ManAhl.Core.Analytics
+import ManAhl.Core.WeightedEngine
 import ManAhl.Core.Types
 
 import Control.Exception

### 2017-09-06 src/ManAhl/Core/Types.hs
Rename mkPdf to mkWPdf

@@ -137,7 +137,7 @@ class Monad a => ProbaEngine a b c | a -> b, a -> c where
   getPDF :: a b -> c -> PDF b
   -- | Compute the probabilities
   computeProba :: c -> UniformRNG -> a d -> d
-  -- | Compute the probabilities and send back the engine
+  -- | Compute the probabilities and send back the rng
   runProba :: c -> UniformRNG -> a d -> (d, UniformRNG)
   -- | Prepare the next random number
   nextNum :: a b

### 2017-09-06 src/ManAhl/Core/WeightedEngine.hs

@@ -2,7 +2,7 @@
 -- | The weighted proba engine
 module ManAhl.Core.WeightedEngine(
   -- * Creation
-  mkWPEngineParams, mkPdf,
+  mkWPEngineParams, mkWPdf,
   pillarsWDefault,
   -- * Engines
   ProbaWPEngine()
@@ -26,8 +26,8 @@ pillarsWDefault = WPdfPillars [(1, 0.2), (2, 0.3), (3, 0.1), (4, 0.15)]
 -- the sum of the probability cannot exceed 1.
 -- The pillars with probability 0 are discarded.
 -- O(n log n)
-mkPdf :: WPdfPillars -> Either String (PDF (Maybe Int))
-mkPdf (WPdfPillars xs)
+mkWPdf :: WPdfPillars -> Either String (PDF (Maybe Int))
+mkWPdf (WPdfPillars xs)
   | null xs = Left "The pdf pillars are empty."
   | null $ filter (\(_, x) -> x /= 0) xs =
       Left "The pdf pillars contain only zero."
@@ -53,7 +53,7 @@ mkWPEngineParams pdfP =
             pdf = p
            ,cdf = cdf'
            ,iCdf = mkInvCdf cdf'
-         }) $ mkPdf pdfP
+         }) $ mkWPdf pdfP
 
 instance ProbaEngine ProbaWPEngine (Maybe Int) WEngineParams where
 

### 2017-09-06 src/Test/ManAhl/Core/Analytics.hs

@@ -22,7 +22,7 @@ import Test.ManAhl.QuickCheck
 instance Arbitrary (PDF (Maybe Int)) where
   arbitrary = do
       pillars <- genPdfPillars
-      let pdf = mkPdf pillars
+      let pdf = mkWPdf pillars
       return $ case pdf of
         Left s -> error $ "Generation failed " ++ s
         Right p -> p
@@ -88,8 +88,8 @@ propCdfPdfPillars =
 propPdfStable :: Test
 propPdfStable =
   TestQC $ run $ forAll genPdfPillars $ \ (WPdfPillars pdfP) ->
-    let (Right lhs) = mkPdf (WPdfPillars pdfP)
-        (Right rhs) = mkPdf (WPdfPillars $ reverse $ pdfP )
+    let (Right lhs) = mkWPdf (WPdfPillars pdfP)
+        (Right rhs) = mkWPdf (WPdfPillars $ reverse $ pdfP )
     in lhs `eq` rhs
 
 -- | Ensure that the pdf probabilities are correct.
@@ -115,10 +115,10 @@ testPdfFail =
   TestPure $ const $
       negativePro && nullPro && greaterPro && nullPro2
   where
-      negativePro = isLeft $ mkPdf $ WPdfPillars [(1, -1)]
-      nullPro = isLeft $ mkPdf $ WPdfPillars []
-      nullPro2 = isLeft $ mkPdf $ WPdfPillars [(1,0)]
-      greaterPro = isLeft $ mkPdf $ WPdfPillars [(1, 0.4), (2, 0.5), (3, 0.4)]
+      negativePro = isLeft $ mkWPdf $ WPdfPillars [(1, -1)]
+      nullPro = isLeft $ mkWPdf $ WPdfPillars []
+      nullPro2 = isLeft $ mkWPdf $ WPdfPillars [(1,0)]
+      greaterPro = isLeft $ mkWPdf $ WPdfPillars [(1, 0.4), (2, 0.5), (3, 0.4)]
 
 -- | Ensure that inverse CDF fails when expected
 testInvCdfFail :: Test
@@ -143,7 +143,7 @@ testPDFNoRegression =
   TestPure $ const $ test
     where
       pdfP = WPdfPillars [(1, 0.2), (1, 0.1), (2, 0.4), (3, 0.3),(4, 0)]
-      res  = mkPdf pdfP
+      res  = mkWPdf pdfP
       test = case res of
               Left _ -> False
               Right p ->
[…]

### 2017-09-06 tex/paper/paper.tex
Fix paper typo
version 1.1

@@
 \vspace*{2\drop}
-{\scshape September 3, 2017}\par
-{\scshape \small Version 1.0}\par
+{\scshape September 6, 2017}\par
+{\scshape \small Version 1.1}\par
 \endgroup}
@@
 \phantomsection
+\vfill
+
+\begin{table}[h!]
+  \centering
+  \caption{Table of Changes}
+%  \label{tab:table1}
+  \begin{tabular}{lll p{6.cm}}
+    \toprule
+    V. & Author & Date & Change\\
+    \midrule
+    1.0 & Fadil M. & 3/09/2017 & 
+    	Initial version. \\
+    1.1 & Fadil M. & 6/09/2017 & 
+    	Simplified and generalised the design of the code. 
+    	C.f. \autoref{apx:code}
+
+    	- Added the Statistics engine module in \autoref{ssec:design}
+
+    	- Updated implementation notes: \autoref{ssec:uniform.impl}
+    	 and \autoref{ssec:weighted.impl}, 
+    	added \autoref{ssec:stats.impl} to reflect the new design.
+
+    	- Updated the performances, \autoref{sec:perf}, to be clearer.
+
+    	- Updated the extensions, \autoref{sec:ext}.
+
+    	- Added \autoref{apx:code} with the code to facilitate sharing.
+    	\\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+\newpage
 \listoffigures
@@
 \subsection{Design}
+\label{ssec:design}
 We target the following archictecture, c.f. \autoref{fig:architecture1}.
@@
 \begin{center}
-\includegraphics[width=0.8\textwidth]{img/architecture1.png}
+\includegraphics[width=0.9\textwidth]{img/architecture1.png}
 \caption{Algorithm App Architecture}
@@
 	It can compute a random number or a series of random 
-	number and the statistics related to the distribution of 
-	the random number generated.
+	number.
+
 	\item[Weighted Engine] 	The weighted pseudo random 
@@
 	It includes the requested nextNum function.
+	\item[Statistics Engine] The various statistical metrics
+	introduced in \autoref{sec:quality}.
+
+	It computes the statistics metrics for a series of 
+	random numbers produced by the weighted or
+	uniform engine.
 	\item[CLI] 		The command line input layer,
@@
 \subsection{Uniform Engine Module}
-
+\label{ssec:uniform.impl}
 The \emph{UniformRNG} ADT abstracts a choice of uniform pseudo random 
@@
 
-The \emph{StatUniEngine} ADT abstracts the computation of the statistics
-related to the bounded uniform random numbers generated. 
-In order to be efficient, we compute only the distribution while we 
-are creating pseudo random numbers. 
-There is a post-processing step at the end of the simulation, which 
-computes the remaining relevant statistics.
-It uses the \emph{State} monad to pass on the state of the 
-uniform random number generator and the cumulative statistics.
-This engine instanciates the \emph{StatEngine} class, which role is
-to compute the statistics of a series of random numbers.
-
 \subsection{Weighted Engine Module}
-
+\label{ssec:weighted.impl}
 The \emph{ProbaWPEngine} ADT allows to computed weighted pseudo
@@
 
-The \emph{StatWPEngine} ADT compute the statistic for a weighted
-probabilities run. It also use a monad composed of a \emph{Reader}
-and \emph{State} monads. A post processing step computes
-the remaining metrics. It also instanciates the \emph{StatEngine} class.
+\subsection{Statistics Engine Module}
+\label{ssec:stats.impl}
+This \emph{StatEngine} type role is
+to compute the statistics of a series of random numbers generated
+by either the \emph{ProbaUniEngine} or the \emph{ProbaWPEngine}.
+
+In order to be efficient, we compute only the distribution while we 
+are creating pseudo random numbers. 
+There is a post-processing step at the end of the simulation, which 
+computes the remaining relevant statistics.
+It uses the \emph{State} monad to pass on the state of the 
+uniform random number generator and the cumulative statistics.
+It also use a monad composed of a \emph{Reader} which
+pass one the engine used and the engine parameters.
 
@@
 and a Pure kind of test, for pure computation action.
+
+%-------------------------------------------------------------------------------
+\section{Qualitative Analysis}
+\label{sec:quality}
+We realise that we maybe be beyond the scope of the initial
+question, which was to implement a \emph{nextNum} function.
+However how to test it efficiently ? It is a very hard question.
+This led us to look at the distribution of the results to ensure
+the quality of the numbers generated.
+
+In this section, we will look at the number generated and try
+to find the best parameters for this software.
+
+\subsection{Metrics}
+To assess the quality of a random number engine, we use
+simple statistics.
+
+There are two keys elements that drive the results :
+the input discrete probability function with $k$ pillars and
+the output discrete probability function deducted from a
+simulation of $n$ random numbers.
+
+Hence we look at different input PDF with various $k$,
+and the output PDF with various $n$. 
+This data gives us intuitions about what are the right
+parameters, $n$ and $k$ to use for our engines.
+
+We also have two random numbers generators, 
+Mersenne and Ecuyer, available. We compare them thoughout.
+
+As our weighted probability engine depends on
+the uniform probability engine, we test first the uniform engine.
+
+The metrics we look at are:
+\begin{itemize}
+	\item the difference between the input and output pdf,
+	\item the standard deviation of these differences,
+	\item the mean of these differences, hopefully close to zero,
+	\item and the highest and lowest differences.
+\end{itemize}
+
+\subsection{Uniform Distribution}
+
+The input PDF for a uniform distribution is flat. The probabilities
+should be the same for each bucket.
+
+\autoref{tab:uni.test} presents several runs for various number of random
+numbers for each random number generators, which can be use in
+the bounded uniform probability engine.
+% Table generated by Excel2LaTeX from sheet 'Sheet5'
+\begin{table}[htbp!]
+  \centering \tiny
+    \begin{tabular}{r|rrrrrr}
+    \multicolumn{1}{r}{} & \multicolumn{2}{c}{1000000} & \multicolumn{2}{c}{100000} & \multicolumn{2}{c}{10000} \\
+    \multicolumn{1}{r}{} & Mersenne & Ecuyer & Mersenne & Ecuyer & Mersenne & Ecuyer \\
+\cmidrule{2-7}    Mean  & 5.55E-19 & 4.16E-19 & 4.86E-19 & 2.78E-19 & 5.55E-19 & 4.16E-19 \\
+    StdDev  & 1.08E-04 & 1.27E-04 & 4.42E-04 & 4.80E-04 & 1.47E-03 & 1.29E-03 \\
+    Highest  & 1.89E-04 & 2.89E-04 & 9.90E-04 & 1.01E-03 & 3.80E-03 & 2.50E-03 \\
+    Lowest  & -2.91E-04 & -2.93E-04 & -1.56E-03 & -1.25E-03 & -3.10E-03 & -2.60E-03 \\
+    \end{tabular}%
+  \caption{Uniform Distribution Test}
+  \label{tab:uni.test}%
+\end{table}%
+
+The best standard deviation we achieve is of the order of $e-4$.
+The mean is very close to zero with both generators and the results 
+are very similar.
+Hence setting $n$ to 1000000 for more accurate testing, 
+i.e. of the order of $e-4$, is recommanded.
+
+We tried various $k$, less than 100 to remain realistic. It has no impact on the
+results as expected.
+
+\subsection{Weighted Distribution}
+
+Therefore we can't expect to achieve better accuracy with the
+weighted probability engine as it relies on the bounded uniform engine.
+
+We present in \autoref{tab:w.test}, the result of multiple runs with various $n$.
+% Table generated by Excel2LaTeX from sheet 'Sheet5'
+\begin{table}[htbp!]
+  \centering \tiny
+    \begin{tabular}{r|rrrrrr}
+    \multicolumn{1}{r}{} & \multicolumn{2}{c}{1000000} & \multicolumn{2}{c}{100000} & \multicolumn{2}{c}{10000} \\
+    \multicolumn{1}{r}{} & Mersenne & Ecuyer & Mersenne & Ecuyer & Mersenne & Ecuyer \\
+\cmidrule{2-7}    Mean  & -3.73E-18 & -3.36E-18 & -3.45E-18 & -3.96E-18 & -3.38E-18 & -3.26E-18 \\
+    StdDev  & 1.71E-04 & 1.49E-04 & 5.14E-04 & 4.61E-04 & 1.79E-03 & 1.91E-03 \\
+    Highest  & 7.88E-04 & 2.70E-04 & 1.13E-03 & 8.00E-04 & 5.20E-03 & 5.50E-03 \\
+    Lowest  & -2.99E-04 & -3.61E-04 & -1.34E-03 & -1.25E-03 & -5.10E-03 & -5.52E-03 \\
+    \end{tabular}%
+  \caption{Weighted Distribution Test}
+  \label{tab:w.test}%
+\end{table}%
+The result are very close to the precision of the uniform engine. 
+We therefore recommand the same setting as before for $n$ and $k$.
 
@@
 %-------------------------------------------------------------------------------
-\section{Qualitative Analysis}
-\label{sec:quality}
-We realise that we maybe be beyond the scope of the initial
-question, which was to implement a \emph{nextNum} function.
-However how to test it efficiently ? It is a very hard question.
-This led us to look at the distribution of the results to ensure
-the quality of the numbers generated.
-
-In this section, we will look at the number generated and try
-to find the best parameters for this software.
-
-\subsection{Metrics}
-To assess the quality of a random number engine, we use
-simple statistics.
-
-There are two keys elements that drive the results :
-the input discrete probability function with $k$ pillars and
-the output discrete probability function deducted from a
-simulation of $n$ random numbers.
-
-Hence we look at different input PDF with various $k$,
-and the output PDF with various $n$. 
-This data gives us intuitions about what are the right
-parameters, $n$ and $k$ to use for our engines.
-
-We also have two random numbers generators, 
-Mersenne and Ecuyer, available. We compare them thoughout.
-
-As our weighted probability engine depends on
-the uniform probability engine, we test first the uniform engine.
-
-The metrics we look at are:
-\begin{itemize}
-	\item the difference between the input and output pdf,
-	\item the standard deviation of these differences,
-	\item the mean of these differences, hopefully close to zero,
-	\item and the highest and lowest differences.
-\end{itemize}
-
-\subsection{Uniform Distribution}
-
-The input PDF for a uniform distribution is flat. The probabilities
-should be the same for each bucket.
-
-\autoref{tab:uni.test} presents several runs for various number of random
-numbers for each random number generators, which can be use in
-the bounded uniform probability engine.
-% Table generated by Excel2LaTeX from sheet 'Sheet5'
-\begin{table}[htbp!]
-  \centering \tiny
-    \begin{tabular}{r|rrrrrr}
-    \multicolumn{1}{r}{} & \multicolumn{2}{c}{1000000} & \multicolumn{2}{c}{100000} & \multicolumn{2}{c}{10000} \\
-    \multicolumn{1}{r}{} & Mersenne & Ecuyer & Mersenne & Ecuyer & Mersenne & Ecuyer \\
-\cmidrule{2-7}    Mean  & 5.55E-19 & 4.16E-19 & 4.86E-19 & 2.78E-19 & 5.55E-19 & 4.16E-19 \\
-    StdDev  & 1.08E-04 & 1.27E-04 & 4.42E-04 & 4.80E-04 & 1.47E-03 & 1.29E-03 \\
-    Highest  & 1.89E-04 & 2.89E-04 & 9.90E-04 & 1.01E-03 & 3.80E-03 & 2.50E-03 \\
-    Lowest  & -2.91E-04 & -2.93E-04 & -1.56E-03 & -1.25E-03 & -3.10E-03 & -2.60E-03 \\
-    \end{tabular}%
-  \caption{Uniform Distribution Test}
-  \label{tab:uni.test}%
-\end{table}%
-
-The best standard deviation we achieve is of the order of $e-4$.
-The mean is very close to zero with both generators and the results 
-are very similar.
-Hence setting $n$ to 1000000 for more accurate testing, 
-i.e. of the order of $e-4$, is recommanded.
-
-We tried various $k$, less than 100 to remain realistic. It has no impact on the
-results as expected.
-
-\subsection{Weighted Distribution}
-
-Therefore we can't expect to achieve better accuracy with the
-weighted probability engine as it relies on the bounded uniform engine.
-
-We present in \autoref{tab:w.test}, the result of multiple runs with various $n$.
-% Table generated by Excel2LaTeX from sheet 'Sheet5'
-\begin{table}[htbp!]
-  \centering \tiny
-    \begin{tabular}{r|rrrrrr}
-    \multicolumn{1}{r}{} & \multicolumn{2}{c}{1000000} & \multicolumn{2}{c}{100000} & \multicolumn{2}{c}{10000} \\
-    \multicolumn{1}{r}{} & Mersenne & Ecuyer & Mersenne & Ecuyer & Mersenne & Ecuyer \\
-\cmidrule{2-7}    Mean  & -3.73E-18 & -3.36E-18 & -3.45E-18 & -3.96E-18 & -3.38E-18 & -3.26E-18 \\
-    StdDev  & 1.71E-04 & 1.49E-04 & 5.14E-04 & 4.61E-04 & 1.79E-03 & 1.91E-03 \\
-    Highest  & 7.88E-04 & 2.70E-04 & 1.13E-03 & 8.00E-04 & 5.20E-03 & 5.50E-03 \\
-    Lowest  & -2.99E-04 & -3.61E-04 & -1.34E-03 & -1.25E-03 & -5.10E-03 & -5.52E-03 \\
-    \end{tabular}%
-  \caption{Weighted Distribution Test}
-  \label{tab:w.test}%
-\end{table}%
-The result are very close to the precision of the uniform engine. 
-We therefore recommand the same setting as before for $n$ and $k$.
-
-%-------------------------------------------------------------------------------
 \section{Performance Analysis}
+\label{sec:perf}
 
@@
 \subsection{Uniform Engine Performance}
-\autoref{tab:uni.perf} presents the result of many runs with various $n$ and
-the heap that was allocated during the run and the time taken.
+\autoref{tab:uni.perf} and \autoref{fig:perf.uni} 
+ present the result of many runs with various $n$ and
+the heap (in bytes) that was allocated during the run and the time taken.
+\begin{figure}[h!]
+\centering
+    \begin{subfigure}[b]{0.47\textwidth}
+        \includegraphics[width=\textwidth]{img/perf-heap-uni.png}
+        \caption{Heap (bytes)}
+        \label{fig:perf.heap.uni}
+    \end{subfigure}
+    ~ 
+    \begin{subfigure}[b]{0.47\textwidth}
+        \includegraphics[width=\textwidth]{img/perf-time-uni.png}
+        \caption{Time (s)}
+        \label{fig:perf.time.uni}
+    \end{subfigure}
+\caption{Performance Uniform Engine}
+\label{fig:perf.uni}
+\end{figure}
 \begin{table}[htbp!]
@@
 \end{table}%
+
 Most of the heap allocation and the time is consumed by the underlying 
 random number generator, the various engines adds only minor overhead, 
-as shown on the profiling results, c.f. \autoref{fig:perf1} and \autoref{fig:perf2}.
+as shown on the profiling results, c.f. the file \emph{Run.prof} in the code.
 We can see that the time and space are linear with respect to $n$.
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[width=1\textwidth]{img/prof1.png}
-\caption{Performance Profiling 1}
-\label{fig:perf1}
-\end{center}
-\end{figure}
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[width=1\textwidth]{img/prof2.png}
-\caption{Performance Profiling 2}
-\label{fig:perf2}
-\end{center}
-\end{figure}
-%\begin{figure}[h!]
-%\begin{center}
-%\includegraphics[width=1\textwidth]{img/prof3.png}
-%\caption{Performance Profiling 3}
-%\label{fig:perf3}
-%\end{center}
-%\end{figure}
+
 We can conclude that the complexity of the inner random number generators
@@
 i.e. the statistic weighted probability engine.
+\begin{figure}[h!]
+\centering
+    \begin{subfigure}[b]{0.47\textwidth}
+        \includegraphics[width=\textwidth]{img/perf-heap-w.png}
+        \caption{Heap (bytes)}
+    \end{subfigure}
+    ~ 
+    \begin{subfigure}[b]{0.47\textwidth}
+        \includegraphics[width=\textwidth]{img/perf-time-w.png}
+        \caption{Time (s)}
+    \end{subfigure}
+\caption{Performance Weighted Engine}
+\label{fig:perf.w}
+\end{figure}
 \begin{table}[htbp!]
@@
 \section{Possible Extensions}
+\label{sec:ext}
 Here is a list of possible extension we could add.
 \begin{description}
-	\item [Analytics]
-	Further abstract the PDF, CDF, InvCDF to handle all kind of keys.
-
-	Review the design of the statistics.
 	\item [Testing]
@@
 
+%-------------------------------------------------------------------------------
+\newpage
+\appendix
+\addcontentsline{toc}{chapter}{Appendices}
+
+\chapter{Code} \label{apx:code}
+We provide below the code. We use Vim with the extension 
+\href{https://github.com/begriffs/haskell-vim-now}{haskell-vim-now}
 \end{document}

### 2017-09-06 src/Test/ManAhl/Core/Analytics.hs
Tidy the code

@@ -172,9 +172,11 @@ testStatistics =
       stats = CollectStats dist 100
       (CollectStats d n, FinalStats pb p m s h l) =
            statistics pdf stats
-      pdf = fromPillars [(Just 1, 0.11), (Just 2, 0.1), (Just 3, 0.8)] :: PDF (Maybe Int)
+      pdf = fromPillars [(Just 1, 0.11), (Just 2, 0.1), (Just 3, 0.8)]
+        :: PDF (Maybe Int)
       x ~= y = abs (x - y) < 0.001
-      diff = fromPillars [(Just 1, 0.01), (Just 2, 0), (Just 3, 0)] :: PDF (Maybe Int)
+      diff = fromPillars [(Just 1, 0.01), (Just 2, 0), (Just 3, 0)]
+        :: PDF (Maybe Int)
    in m ~= (0.01/3) && h ~= 0.01 && l ~= 0 && s ~= 0.0057
         && pb `eq` pdf && fromPillars p `eq` diff
 

### 2017-09-06 src/Test/ManAhl/Core/UniformEngine.hs

@@ -93,6 +93,8 @@ testEngineFail = TestPure $ const $
       negativePro && nullPro && greaterPro && nullPro2
   where
       negativePro = isLeft $ mkUPEngineParams $ UPdfPillars [(1, -1)]
-      nullPro = isLeft $ mkUPEngineParams $ UPdfPillars [(1,0.5), (2,0.3), (3,0.2)]
+      nullPro = isLeft $ mkUPEngineParams $
+          UPdfPillars [(1,0.5), (2,0.3), (3,0.2)]
       nullPro2 = isLeft $ mkUPEngineParams $ UPdfPillars [(1,0)]
-      greaterPro = isLeft $ mkUPEngineParams $ UPdfPillars [(1, 0.4), (2, 0.5), (3, 0.4)]
+      greaterPro = isLeft $ mkUPEngineParams $
+          UPdfPillars [(1, 0.4), (2, 0.5), (3, 0.4)]

### 2017-09-06 tex/paper/paper.tex
final paper v1.1

@@
 the whole power of Haskell. 
+The types are key, c.f. the code at \autoref{fig:core.types1}, \autoref{fig:core.types2}
+and \autoref{fig:core.types3}.
+
 We use \emph{newtype} as much as possible as it allows design at a 
@@
 
+The relevant code is in \autoref{fig:core.analytics}.
 \subsection{Uniform Engine Module}
@@
 
+The relevant code is in \autoref{fig:core.u}.
 \subsection{Weighted Engine Module}
@@
 
+The relevant code is in \autoref{fig:core.we}.
 \subsection{Statistics Engine Module}
@@
 
+The relevant code is in \autoref{fig:core.se}.
 \subsection{CLI Module}
@@
 
+The relevant code is in \autoref{fig:core.cli1} and \autoref{fig:core.cli2}.
 \subsection{Testing Module}
@@
 
+The relevant code is in \autoref{fig:test.qc1} and \autoref{fig:test.qc2}.
 %-------------------------------------------------------------------------------
@@
 \end{description}
+The relevant code is available in \autoref{fig:test.a1}, \autoref{fig:test.a2}
+and \autoref{fig:test.a3}.
+
 \subsection{Uniform Engine Testing}
@@
 \end{description}
-
+The relevant code is in \autoref{fig:test.u1} and \autoref{fig:test.u2}.
 \subsection{Weighted Engine Testing} 
@@
 \end{description}	
-
+The relevant code is in \autoref{fig:test.w}.
 \subsection{CLI Testing}
@@
 \end{description}
-
+The relevant code is in \autoref{fig:test.cli}.
 %-------------------------------------------------------------------------------
@@
 	the code.
+
+	We could also automate the performance testing.
 	\item [UI] 
@@
 We provide below the code. We use Vim with the extension 
-\href{https://github.com/begriffs/haskell-vim-now}{haskell-vim-now}
+\href{https://github.com/begriffs/haskell-vim-now}{haskell-vim-now}.
+\begin{figure}[h!]
+\centering
+\includegraphics[width=1\textwidth]{img/code-run.png}
+\caption{Code: ManAhl.Run}
+\label{fig:core.run}
+\end{figure}
+\begin{figure}[h!]
+\centering
+\includegraphics[width=1\textwidth]{img/code-types-1.png}
+\caption{Code: ManAhl.Core.Types - page 1}
+\label{fig:core.types1}
+\end{figure}
+\begin{figure}[h!]
+\centering
+\includegraphics[width=1\textwidth]{img/code-types-2.png}
+\caption{Code: ManAhl.Core.Types - page 2}
+\label{fig:core.types2}
+\end{figure}
+\begin{figure}[h!]
+\centering
+\includegraphics[width=1\textwidth]{img/code-types-3.png}
+\caption{Code: ManAhl.Core.Types - page 3}
+\label{fig:core.types3}
+\end{figure}
+\begin{figure}[h!]
+\centering
+\includegraphics[width=1\textwidth]{img/code-ue.png}
+\caption{Code: ManAhl.Core.UniformEngine}
+\label{fig:core.u}
+\end{figure}
+\begin{figure}[h!]
+\centering
+\includegraphics[width=1\textwidth]{img/code-we.png}
+\caption{Code: ManAhl.Core.WeightedEngine}
+\label{fig:core.we}
+\end{figure}
+\begin{figure}[h!]
+\centering
+\includegraphics[width=1\textwidth]{img/code-se.png}
+\caption{Code: ManAhl.Core.StatEngine}
+\label{fig:core.se}
+\end{figure}
+\begin{figure}[h!]
+\centering
+\includegraphics[width=1\textwidth]{img/code-analytics.png}
+\caption{Code: ManAhl.Core.Analytics}
+\label{fig:core.analytics}
+\end{figure}
+\begin{figure}[h!]
+\centering
+\includegraphics[width=1\textwidth]{img/code-cli-1.png}
+\caption{Code: ManAhl.CLI - page 1}
+\label{fig:core.cli1}
+\end{figure}
+\begin{figure}[h!]
+\centering
+\includegraphics[width=1\textwidth]{img/code-cli-2.png}
+\caption{Code: ManAhl.CLI - page 2}
+\label{fig:core.cli2}
+\end{figure}
+\begin{figure}[h!]
+\centering
+\includegraphics[width=1\textwidth]{img/code-test-run.png}
+\caption{Code: Test.ManAhl.Run}
+\label{fig:test.run}
+\end{figure}
+\begin{figure}[h!]
+\centering
+\includegraphics[width=1\textwidth]{img/code-test-quickcheck-1.png}
+\caption{Code: Test.ManAhl.QuickCheck - page 1}
+\label{fig:test.qc1}
+\end{figure}
+\begin{figure}[h!]
+\centering
+\includegraphics[width=1\textwidth]{img/code-test-quickcheck-2.png}
+\caption{Code: Test.ManAhl.QuickCheck - page 2}
+\label{fig:test.qc2}
+\end{figure}
+\begin{figure}[h!]
+\centering
+\includegraphics[width=1\textwidth]{img/code-test-uni-1.png}
+\caption{Code: Test.ManAhl.Core.UniformEngine - page 1}
+\label{fig:test.u1}
+\end{figure}
+\begin{figure}[h!]
+\centering
+\includegraphics[width=1\textwidth]{img/code-test-uni-2.png}
+\caption{Code: Test.ManAhl.Core.UniformEngine - page 2}
+\label{fig:test.u2}
+\end{figure}
+\begin{figure}[h!]
+\centering
+\includegraphics[width=1\textwidth]{img/code-test-w.png}
+\caption{Code: Test.ManAhl.Core.WeightedEngine }
+\label{fig:test.w}
+\end{figure}
+\begin{figure}[h!]
+\centering
+\includegraphics[width=1\textwidth]{img/code-test-analytics-1.png}
+\caption{Code: Test.ManAhl.Core.Analytics - page 1}
+\label{fig:test.a1}
+\end{figure}
+\begin{figure}[h!]
+\centering
+\includegraphics[width=1\textwidth]{img/code-test-analytics-2.png}
+\caption{Code: Test.ManAhl.Core.Analytics - page 2}
+\label{fig:test.a2}
+\end{figure}
+\begin{figure}[h!]
+\centering
+\includegraphics[width=1\textwidth]{img/code-test-analytics-3.png}
+\caption{Code: Test.ManAhl.Core.Analytics - page 3}
+\label{fig:test.a3}
+\end{figure}
+\begin{figure}[h!]
+\centering
+\includegraphics[width=1\textwidth]{img/code-test-cli.png}
+\caption{Code: Test.ManAhl.CLI}
+\label{fig:test.cli}
+\end{figure}
 \end{document}
